### 2014-02-05 latex/dgci2014/article.tex
repo init

\documentclass{llncs}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{tikz}        % standard LaTeX graphics tool
\usepackage{subfigure}                                 % authors: subfigures
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}   % authors: last version of algorithm display
\usepackage{todonotes}

%\title{A Subquadratic and Separable Algorithm for Chamfer Norm
  %Distance Transformation \thanks{This work has been mainly funded
  %  by  ANR-11-BS02-009 and  ANR-11-IDEX-0007-02 PALSE/2013/21 research grants.}}

\title{Generic Separable Algorithms for Distance Transformation: A
  Subquadratic Approach for Path Based Norms\thanks{This work has been
    mainly funded by ANR-11-BS02-009 and ANR-11-IDEX-0007-02
    PALSE/2013/21 research grants.}}

\author{David Coeurjolly\inst{1}}

 \institute{ CNRS,  LIRIS, UMR5205, F-69621, France\\
   \email{david.coeurjolly@liris.cnrs.fr}
}
\graphicspath{{./Figs/}}
\input{macros}
\begin{document}
\maketitle

\begin{abstract}
In many applications, separable algorithms have demonstrated their
efficiency to perform high performance volumetric computations, such
as distance transformation or medial axis extraction. In the
literature, several authors have discussed about the conditions on the
metric to be considered in a separable approach.  In this article, we
present generic separable algorithms to efficiently compute Voronoi
maps and distance transformations for a large class of
metrics. Focusing to path based norms (chamfer masks, neighborhood
sequences, ...), we detail a subquadratic algorithm to compute such
volumetric transformations. More precisely, we describe a
$O(N\log^2(m))$ algorithm in dimension 2 for shapes with $N$ grid
points and for example a chamfer mask of size $m$.

\keywords{Digital Geometry, Distance Transformation, Chamfer Norms}
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Since early works on digital geometry, distance transformation plays
an important role in many applications
\cite{Rosenfeld1966,Rosenfeld1968}. Given a finite input shape
$X\subset \Z^n$, the distance transformation labels each point in $X$
with the distance to the closest point in $\Z^n \setminus X$. Since
such characterization is parametrized by a distance function, many
works have been done to address this distance transformation problem
with a trade-off between algorithmic performances and the
\emph{accuracy} of the digital distance function with respect to the
Euclidean one.  Hence, authors have considered distances based on
chamfer masks
\cite{Rosenfeld1968,borgefors,Thiel_IWCIA7,fouard:ivc:2005} or
sequences of chamfer masks
\cite{ROSEN_66,mukherjee,Nagy05,Strand2008,DBLP:conf/dgci/NormandSE13};
the vector displacement based Euclidean distance
\cite{danielson,ragnemalm,MULL_92,Cuisenaire1999_268}; the Voronoi
diagram based Euclidean distance
\cite{BreuEtAl95,GotLin95,Guan,maurer_pami} or the square of the
Euclidean distance \cite{SaitTori:94,Hirata,roerdnik}.

\paragraph{Contributions} In this article,

\section{Preliminaries}
\label{sec:preliminaries}

Let us first present some definitions.
\begin{definition}[Metrics and Metric Space]
  \label{def:distance}
  A metric is a map $d$ from $E$ to a sub-group $F$ of $\R$ such that
  $\forall a,b,c\in E$,
  \begin{align}
    (\text{non-negative})\quad & d(a,b)\geq 0\\
    (\text{identity of indiscernibles}) \quad&  d(a,b)= 0
    \Leftrightarrow a=b\\
    (\text{symmetry})\quad &  d(a,b)=d(b,a)\\
    (\text{triangular inequality})\quad &   d(a,c) \leq d(a,b) + d(b,c)
  \end{align}
$(E, F, d)$ is called a metric space.
\end{definition}
If property $(4)$ is omitted, we are defining a distance function
instead of a metric. Note that in the following, we will only consider
metric spaces with properties $(1-4)$. Furthermore, we may have to
consider  metrics induced by a vector space norm:
\begin{definition}[Norm and metric induced by a norm]
  \label{def:distance}
  Given a vector space EV, a norm is a map $g$ from  $EV$ to a sub-group
  $F$ of $\R$ such that $\forall \vec{x},\vec{y}\in EV$,
  \begin{align}
    (\text{non-negative})\quad & g(\vec{x})\geq 0\\
    (\text{identity of indiscernibles}) \quad&  g(\vec{x})= 0
    \Leftrightarrow \vec{x}=\vec{0}\\
    (\text{triangular inequality})\quad &   g(\vec{x}+\vec{y}) \leq
    g(\vec{x}) + g(\vec{y})\\
    (\text{homogeneity})\quad &  \forall \lambda\in\R, \quad
    g(\lambda\cdot\vec{x}) = |\lambda|\cdot g(\lambda\cdot\vec{x})
  \end{align}
$d(a,b) \EqDef g(b-a)$ is the metric induced by the
  norm $g$.
\end{definition}
Note that the above definition can be extended from vector spaces to
\emph{modules} on a commutative ring ($\Z^n$ being a module on $\Z$
but not a vector space) \cite{Thiel_hdr}.

From the literature, path-based approaches (Chamfer masks, (weighted)
neighborhood sequences...)  aim at defining metrics induced by norms
in metric spaces $(\Z^n, \Z , d)$.  Note that (weighed, with $w_i\geq 0$) $L_p$ norms inducing
metrics
\begin{equation}
    d_{\ell_p} (a,b) = \left ( \sum_{i=0}^n w_i|a_i-b_i |^p \right )^{\frac{1}{p}}\,
  \end{equation}
characterize metric spaces $(\Z^n, \R , d_{\ell_p})$. However,  note that
$(\Z^n,\Z, \lfloor d_{\ell_p}) \rfloor)$ is a metric space.

\section{Separable Distance Transformation}
\label{sec:separ-dist-transf}

\subsection{A First Generic Adapter}
\label{sec:first-gener-adapt}

In

\subsection{Subquadratic Algorithm in Dimension 2}
\label{sec:subq-algor-dimens}

\subsection{Subquadratic Algorithms in Higher Dimension}
\label{sec:subq-algor-high}

\section{Experimental Analysis}
\label{sec:exper-analys}

\subsection{Implementation details}
\label{sec:impl-deta}

\subsection{Voronoi Maps in dimension 2}
\label{sec:impl-2D}

\section{Discussion}
\label{sec:discussion}

\bibliographystyle{splncs}
\bibliography{library,mybiblio,dtbib}
\end{document}

### 2014-02-05 src/statDistances.cpp

@@ -1,0 +1,60 @@
+//
+//  statDistances.cpp
+//  ChamferSubQuad
+//
+//  Created by David Coeurjolly on 22/12/2013.
+//
+//
+
+#include <DGtal/base/Common.h>
+#include <DGtal/helpers/StdDefs.h>
+#include <DGtal/geometry/volumes/distance/ChamferNorm2D.h>
+#include <DGtal/arithmetic/IntegerComputer.h>
+#include <stdio.h>
+
+using namespace DGtal;
+
+template< typename Mask, typename Point>
+double bruteForceDT( Mask &avec, const Point &p, const Point &q)
+{
+  double maxdot=0;
+  typename Mask::Vector d = q-p;
+  
+  for(typename Mask::ConstIterator it = avec.begin(), itend = avec.end();
+      it != itend; ++it)
+    if (( (*it)[0]*d[0] + (*it)[1]*d[1]) > maxdot)
+      maxdot = (*it)[0]*d[0] + (*it)[1]*d[1];
+  return maxdot;
+}
+
+int main(int argc, char **argv)
+{
+  double accum = 0.0;
+  
+  for(unsigned int N = 3 ; N < 10000; N++)
+  {
+    ChamferNorm2D<Z2i::Space> mask(N);
+    trace.info() << mask<<std::endl;
+    Z2i::Point origin(0,0), p;
+    trace.beginBlock("10000 distances");
+    for(unsigned int k = 0; k < 10000 ; k++)
+    {
+      p[0] = rand();
+      p[1] = rand();
+      accum += mask(origin,p);
+    }
+    double duration = trace.endBlock();
+    trace.beginBlock("10000 distances (brute)");
+    for(unsigned int k = 0; k < 10000 ; k++)
+    {
+      p[0] = rand();
+      p[1] = rand();
+      accum += bruteForceDT(mask,origin,p);
+    }
+    double duration2 = trace.endBlock();
+    std::cout <<N<<" "<<duration<<" "<<duration2<<std::endl;
+  }
+  trace.info() << accum<<std::endl;
+  
+  return 0;
+}

### 2014-02-05 src/statVoronoi.cpp

@@ -1,0 +1,100 @@
+//
+//  statVoronoi.cpp
+//  ChamferSubQuad
+//
+//  Created by David Coeurjolly on 30/01/2014.
+//
+//
+
+#include <DGtal/base/Common.h>
+#include <DGtal/helpers/StdDefs.h>
+#include <DGtal/geometry/volumes/distance/ChamferNorm2D.h>
+#include <DGtal/geometry/volumes/distance/VoronoiMap.h>
+#include <DGtal/arithmetic/IntegerComputer.h>
+#include <stdio.h>
+#include <DGtal/io/boards/Board2D.h>
+#include <DGtal/io/colormaps/HueShadeColorMap.h>
+
+using namespace DGtal;
+
+template <typename Predicate>
+void constructPredicate(Predicate &mySet, const unsigned int nbSeeds, const unsigned int domSize)
+{
+  Z2i::Point a(0,0);
+  Z2i::Point b(domSize,domSize);
+  Z2i::Domain domain(a,b);
+  
+  for(Z2i::Domain::ConstIterator it = domain.begin(), itend = domain.end();
+      it != itend;
+      ++it)
+    mySet.insertNew( *it );
+  
+  Z2i::DigitalSet sites(domain);
+  for(unsigned int i = 0; i < nbSeeds; i++)
+    sites.insert(Z2i::Point( rand() % domSize , rand()% domSize ));
+  
+  for(Z2i::DigitalSet::ConstIterator it = sites.begin(), itend = sites.end();
+      it != itend; ++it)
+    mySet.erase (*it);
+}
+
+
+int main(int argc, char **argv)
+{
+  unsigned int maxN = 500;
+  unsigned int domSize = 2048;
+  unsigned int nbSeeds = domSize;
+  
+  
+  Z2i::Domain domain(Z2i::Point(0,0), Z2i::Point(domSize,domSize));
+  
+  DigitalSetBySTLSet<Z2i::Domain> mySet(domain);
+  constructPredicate<DigitalSetBySTLSet<Z2i::Domain> >(mySet,nbSeeds, domSize);
+  
+  
+  for(unsigned int N = 2 ; N < maxN; )
+  {
+    ChamferNorm2D<Z2i::Space> mask(N);
+    trace.info() << mask<<std::endl;
+    Z2i::Point origin(0,0);
+   
+    trace.beginBlock("DT distances");
+  
[…]

### 2014-02-05 src/testLogChamfer.cpp

@@ -1,0 +1,151 @@
+#include <iostream>
+#include <DGtal/base/Common.h>
+#include <DGtal/helpers/StdDefs.h>
+#include <vector>
+#include <cstdlib>
+#include <string>
+#include <assert.h>
+#include <DGtal/io/boards/Board2D.h>
+
+using namespace DGtal;
+using namespace std;
+
+typedef Z2i::Vector Vector;
+typedef Z2i::Point Point;
+typedef vector<Vector> Mask;
+typedef int Abscissa;
+typedef Mask::const_iterator ConstIterator;
+
+
+bool LessThan(const Vector &a, const Vector &b)
+{
+  return (a[0]*b[1] - a[1]*b[0]) < 0;
+}
+
+
+bool LessEqThan(const Vector &a, const Vector &b)
+{
+  return (a[0]*b[1] - a[1]*b[0]) < 0;
+}
+
+
+/**
+ * Generate a mask from m random vectors.
+ *
+ * @param [in] m the number of vectors.
+ * @param [out] aMask the mask to populate.
+ *
+ */
+void populateMask(const unsigned int m, Mask &aMask)
+{
+
+  aMask.clear();
+  for(unsigned int i=0; i< m; i++)
+    aMask.push_back(Vector( i, rand() % 10 ));  //Before
+  sort(aMask.begin(), aMask.end(), LessThan );
+  
+  copy(aMask.begin(), aMask.end(),
+       ostream_iterator<Vector>(cout, "\n"));
+}
+
+/**
+ * Compute the cone in which a point belongs to using logarithmic search.
+ */
+unsigned int locatePoint(Mask &aMask, const Vector &p)
+{
+  ASSERT( LessEqThan(aMask[0], p) );
+  ASSERT( LessThan(p, aMask[aMask.size()-1] ));
+  
+  unsigned int top=0;
+  unsigned int size = aMask.size();
+  while (size >1)
+  {
+    size = size /2;
+    if ( ! LessThan( p , aMask[top+size]))
+      top += size;
+  }
+  return top;
+}
+
+/**
+ * Compute the cone in which a point belongs to using linear search.
+ * When the method ends, the cone is given by iterators
+ * [itBegin, itBegin+1]
+ *
+ * @param[in/out] itBegin the first iterator on the mask range
+ * @param[in/out] itEnd the end iterator on the mask range
[…]

### 2014-02-06 src/statVoronoil2.cpp
l2

@@ -1,0 +1,93 @@
+//
+//  statVoronoi.cpp
+//  ChamferSubQuad
+//
+//  Created by David Coeurjolly on 30/01/2014.
+//
+//
+
+#include <DGtal/base/Common.h>
+#include <DGtal/helpers/StdDefs.h>
+#include <DGtal/geometry/volumes/distance/ChamferNorm2D.h>
+#include <DGtal/geometry/volumes/distance/VoronoiMap.h>
+#include <DGtal/arithmetic/IntegerComputer.h>
+#include <stdio.h>
+#include <DGtal/io/boards/Board2D.h>
+#include <DGtal/io/colormaps/HueShadeColorMap.h>
+#include <DGtal/geometry/volumes/distance/ExactPredicateLpSeparableMetric.h>
+using namespace DGtal;
+
+template <typename Predicate>
+void constructPredicate(Predicate &mySet, const unsigned int nbSeeds, const unsigned int domSize)
+{
+  Z2i::Point a(0,0);
+  Z2i::Point b(domSize,domSize);
+  Z2i::Domain domain(a,b);
+
+  for(Z2i::Domain::ConstIterator it = domain.begin(), itend = domain.end();
+      it != itend;
+      ++it)
+    mySet.insertNew( *it );
+
+  Z2i::DigitalSet sites(domain);
+  for(unsigned int i = 0; i < nbSeeds; i++)
+    sites.insert(Z2i::Point( rand() % domSize , rand()% domSize ));
+
+  for(Z2i::DigitalSet::ConstIterator it = sites.begin(), itend = sites.end();
+      it != itend; ++it)
+    mySet.erase (*it);
+}
+
+
+int main(int argc, char **argv)
+{
+  unsigned int maxN = 500;
+  unsigned int domSize = 2048;
+  unsigned int nbSeeds = domSize;
+
+
+  Z2i::Domain domain(Z2i::Point(0,0), Z2i::Point(domSize,domSize));
+
+  DigitalSetBySTLSet<Z2i::Domain> mySet(domain);
+  constructPredicate<DigitalSetBySTLSet<Z2i::Domain> >(mySet,nbSeeds, domSize);
+
+
+  trace.beginBlock("DT distances");
+
+
+  typedef VoronoiMap<Z2i::Space, Z2i::DigitalSet, L2Metric > VoroChamf;
+  VoroChamf voro(&domain, &mySet,&l2Metric);
+  double duration = trace.endBlock();
+
[…]

### 2014-02-06 src/statVoronoil2.cpp
l2

@@ -59,8 +59,6 @@ int main(int argc, char **argv)
   VoroChamf voro(&domain, &mySet,&l2Metric);
   double duration = trace.endBlock();
 
-  std::cout <<mask.size()<<" "<<duration<<std::endl;
-
 
 #ifdef SVG_EXPORT
   Board2D board;

### 2014-02-06 src/statVoronoil2.cpp
l2

@@ -55,8 +55,8 @@ int main(int argc, char **argv)
   trace.beginBlock("DT distances");
 
 
-  typedef VoronoiMap<Z2i::Space, Z2i::DigitalSet, L2Metric > VoroChamf;
-  VoroChamf voro(&domain, &mySet,&l2Metric);
+  typedef VoronoiMap<Z2i::Space, Z2i::DigitalSet, Z2i::L2Metric > VoroChamf;
+  VoroChamf voro(&domain, &mySet,&Z2i::l2Metric);
   double duration = trace.endBlock();
 
 

### 2014-02-07 latex/dgci2014/article.tex
article

@@
 \usepackage{amsmath,amssymb}
+\usepackage{overpic}
+\usepackage{enumerate}
 \usepackage{graphicx}        % standard LaTeX graphics tool
@@
 \usepackage{todonotes}
+\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
 
@@
 
-Let us first present some definitions.
+Let us first define some elementary concepts and objects.
 \begin{definition}[Metrics and Metric Space]
@@
   \end{equation}
-characterize metric spaces $(\Z^n, \R , d_{\ell_p})$. However,  note that
-$(\Z^n,\Z, \lfloor d_{\ell_p}) \rfloor)$ is a metric space.
+characterize metric spaces $(\Z^n, \R , d_{\ell_p})$. However,
+rounding the metric $(\Z^n,\Z, \lceil d_{\ell_p}\rceil)$ implies a
+metric space \cite{klette_book}.
+
+\begin{definition}[Distance Transformation and Voronoi Map]
+  The distance transform $DT_X$ associated with a digital metric space
+  $(\Z^n,\Z,d)$ is a map  $X\rightarrow\Z$ such that
+  \begin{equation}
+    DT_X(a) = \min_{b\in \Z^n\setminus X} \{d(a,b)\}
+  \end{equation}
+The Voronoi map is the map $X\rightarrow\Z^n$:
+  \begin{equation}
+    \Pi_X(a) = \argmin_{b\in \Z^n\setminus X} \{d(a,b)\}
+  \end{equation}
+\end{definition}
+Voronoi map $\Pi_X$ corresponds to the intersection between the
+continuous Voronoi diagram for the metric $d$ of points
+$\Z^n\setminus$ and the lattice $\Z^n$. If a digital point $a$ belongs
+to a Voronoi diagram $d-$facet ($1\leq d< n$), $a$ is equidistant to 2
+or more points in $\Z^n\setminus X$ but only one is considered in
+$\Pi_X(a)$ (please refer to\cite{Couprie2007} for complete digital
+Voronoi map construction).
+
+\begin{definition}[Chamfer Mask]
+  A weighted vector is a pair $(\vec{v},w)$ with $\vec{v}\in\Z^n$ and
+  $w\in\N^*$. A chamfer mask $\M$ is a central-symmetric set of weighted
+  vectors with non-empty vectors and containing at least a basis of
+  $\Z^n$.
+\end{definition}
+
+In the literature
+\cite{borgefors,Thiel_hdr,Strand2008,normandHDR,fouard:ivc:2005} many
+authors have proposed algorithmic and/or analytic approaches to
+construct Chamfer masks approximating the Euclidean metric and being
+induced by norm. In the following, we focus on such \emph{chamfer
+  norms}.  To evaluate distances between two digital points for a
+given chamfer metric, direct formulations have been proposed with
+simple geometrical interpretation:
+\begin{definition}[Rational ball, minimal H-representation \cite{Thiel_hdr,DBLP:journals/pr/NormandE09}]
+  Given a Chamfer mask $\M$ inducing a norm, the rational ball
+  associated with $\M$ is the polytope
+  \begin{equation}
+    \B = conv\left\{ \frac{\vec{v}_i}{w_i};\; (\vec{v}_i,w_i)\in\M \right \}\,.
+  \end{equation}
+Rational ball $\B$ can also be described in a H-representation of
+polytope with minimal parameter \cite{DBLP:conf/dgci/NormandSE13}
+\begin{equation}
+  P = \{ x\in\Z^n; Ax \leq y\;\}\quad \text{ such that }  \forall
+  i\in[1\ldots l], \exists x\in P\quad A_ix=y_i\,.\footnote{$A_i$
+    being the $i^{th}$ row of $A$.}
+\end{equation}
+$l$ being the number of row in $A$ and the number of facets in $\B$,   and is thus related to $|\M|$.
+\end{definition}
+
+An important result for distance computation can be formalized as follows:
+\begin{proposition}[Direct Distance Computation \cite{DBLP:journals/pr/NormandE09}]
+  Given a chamfer mask $\M$ inducing a norm and $(A,y)$ its minimal
+  parameter H-representation, then for any $a\in\Z^n$, the chamfer
+  distance of $a$ from the origin is
+  \begin{equation}
+    \label{eq:1}
+    d_\M(O,a) =  \max_{1\leq i \leq l} \{ A_i a^T\}\,.
+  \end{equation}
+\end{proposition}
+
+Among path-based digital metric, we can also introduce (weighted)
+neighborhood sequences
+\cite{ROSEN_66,mukherjee,Nagy05,Strand2008,DBLP:conf/dgci/NormandSE13}
+whose objective is to have better approximation of the Euclidean
+metric from sequences of elementary chamfer masks.  A key result have
+been demonstrated in \cite{DBLP:journals/pr/NormandE09} stating
+that for such distance functions, a minimal parameter polytope
+representation exists and that distances can be from similar
+expression to (\ref{eq:1}):
+\begin{equation}
+  d(O,a)  =\max_{1\leq i \leq l} \{ f_i(A_i a^T)\}\,,
+\end{equation}
+($f_i$ being and integer sequence characterizing the neighborhood
+sequence metric).
+
+ In the following and for the sake of simplicity, we describe our
+ algorithms focusing to chamfer norms but similar results can be
+ obtained for more generic path-based metric such neighborhood
+ sequences.
 
@@
 
+\subsection{Voronoi Map from Separable Approach and Metric Conditions}
+\label{sec:voronoi-map-from}
+
+In \cite{Hirata1996,SaitTori:94,Breu1995,Meijster2000,Maurer2003},
+several authors have described optimal in time and separable
+techniques to compute error-free Voronoi maps or distance
+transformations for $L_2$ and $L_p$ metrics. Separability means that
+computations are performed dimension by dimension, allowing fast
+computations and multithread implementations (see
+\cite{dcoeurjo_ChapDT} for an overview).  In the following, we
+consider Voronoi map approach as defined in \cite{Breu1995} (see
+Fig.~\ref{fig:2Dbreu}): Let us first define hyper-rectangular domain
+$I_X: [0..N_1]\times\ldots[0..N_n] \rightarrow \{0,1\}$ such that
+$X\subset I_X$ and $I_X(a)= 1$ for $a\in [0..N_1]\times\ldots[0..N_n]$
+iff $a\in X$ ($I_X(a)=0$ otherwise). As illustrated in
+Fig.~\ref{fig:2Dbreu} in dimension 2, we first process each row of the
+input image to create independent 1D Voronoi maps along the first
+dimension for the metric. Then, for each further dimension, the
+partial Voronoi map $\Pi_X$ is updated using one dimensional
+independent processes on image spans along the $i^{th}$
+dimension.
+
+\begin{algorithm}[H]
+  \KwData{Input binary map $I_X$ if $i=1$ or  partial Voronoi map $\Pi_X$ obtained for
+    dimension $1<j<i$, and a 1D segment $S$ with points
+    $\{s_1,\ldots,s_{N_i}\}$ sorted by their $i^{th}$ coordinate.}
+  \KwResult{Updated partial Voronoi map $\Pi_X$ along $S$.}
+\If{ i = 1}
+{ $k=0$\;
+\ForEach{point $s_i$ in $S$}{
+    \If{$I_X(s_i) = 1$}
+     {
+       $L_S[k] = s_i$\;
+       $k++$\;
+     }
+}
+}
+\Else{
+ ${L}_S[0]=\Pi_X(s_1)$\;
+  ${L}_S[1]=\Pi_X(s_2)$\;
+  $k=2$ , $l=3$\;
+  \While{$l\leq N_i$}{
+    $w = \Pi_X(s_l)$\;
+    \While{$k\geq 2$ and \textsc{HiddenBy}(${L}_S[k-1],{L}_S[k],w, S$)}
+          {
+         $ k--$\;
+        }
+        $k++$ , $l++$\;
+        ${L}_S[k]=w$\;
+  }
+}
+  \ForEach{point  $s$ in $S$ by increasing $i^{th}$ component}
+  {
+    \While{($k < |L_S|$) and not(\textsc{Closest}($s$, $L_S[k]$, $L_S[k+1]$))}
+          {
+            $k++$\;
+          }
+    $\Pi_X[s] = L_S[k]$\;
+  }
+
+  \caption{Voronoi map pruning along 1D segment $S$ along the $i^{th}$
+    dimension.\label{alg:voro}}
+\end{algorithm}
+
+\begin{figure}
+  \begin{center}
+     \begin{overpic}[draft=false,width=12cm]{figs/edt_dcoeurjo}
+       \put(30,5){$Candidates_S$}
+       \put(57,0){$S$}
+     \end{overpic}
+  \end{center}
+  \caption{Voronoi Map construction in dimension 2.\label{fig:2Dbreu}}
+\end{figure}
+
+Algorithm \ref{alg:voro} describe the 1D processes to perform on each
+row, columns and higher dimension spans. In this process, metric
+information are embedded in the following two predicates:
+\begin{itemize}
+  \item \textsc{Closest}$(a, b, c)$: given three points $a,b,c\in\Z^n$
+    this predicate returns true if $d(a,b) < d(a,c)$ ;
+  \item \textsc{HiddenBy}$(a, b, c, S)$: given three points
+    $a,b,c\in\Z^n$ such that $a_i<b_i<c_i$ and a 1D image span $S^i$, this predicates returns
+    true if there is no  $s\in S$ such that
+    \begin{equation}
+      d(b,s) < d(a,s)\text{ and }  d(b,s) < d(c,s)\,.
+    \end{equation}
+\end{itemize}
+In other words, \textsc{HiddenBy} returns true if and only if the
+Voronoi cell of sites $a$ and $c$ \emph{hide} the Voronoi cell of $b$
+along $S$ (\emph{e.g.} $A$ and $E$ \emph{hide} $C$ and $B$ on $S$ in
+Fig.~\ref{fig:2Dbreu}).  For $L_1$, $L_2$ and $L_\infty$ metrics,
+\textsc{Closest} and \textsc{HiddenBy} predicates can be computed in
+$O(1)$ \cite{Breu1995,Hirata1996,Meijster2000}. Hence, Algorithm
+\ref{alg:voro} is in $O(N_i)$ for dimension $i$, leading to an overall
+computational time for the Voronoi map and distance transformation
+problem in $O(n\cdot N^n)$ (if we assume that $\forall i\in[1\ldots
+  n], N_i=N$).
+
+In \cite{Hirata1996} or \cite{maurer_pami}, authors discussed about
+conditions on the metric $d$ to ensure that Algorithm \ref{alg:voro}
+is correct. The key property can be informally describe as follows:
+given two points $a,b\in\Z^n$ such that $a_i<b_i$ and a straight line
+$l$ along the $i^{th}$ direction and if we denote by $v_l(a)$
+(resp. $v_l(b)$) the intersection between the Voronoi cell of $a$
+(resp. $b$) and l, then $v_l(a)$ and $v_l(b)$ are simply connected
+Euclidean segments and $v_l(a)$ appears \emph{before} $v_l(b)$ on
+$l$ (so called \emph{monotonicity property} in \cite{Maurer2003} and is
+related to \emph{quadrangle inequality} in \cite{Hirata1996}).
+
+To sum up these contributions, we use the following proposition
+adapted from \cite{Hirata1996}.
+\begin{proposition}[Metric conditions \cite{Hirata1996}]
+\label{prop:voronoi-map-from-1}
+  If $d$ is a metric induced by a norm and if distance comparison
+  predicate $d(a,b)<d(c,d)$ is exact (for $a,b,c,d\in\Z^n$), Algorithm
+  1 is correct and returns a Voronoi map $\Pi_X$.
+\end{proposition}
+
+For example, Algorithm \ref{alg:voro} provides exact Voronoi map
+computation for $L_p$ norms. In such case, distance comparison
+predicate can be implemented error-free form integer number comparison
+considering the $p$ power of the distance function $\left
+(d_{L_p}\right)^p$.
+
+Proposition \ref{prop:voronoi-map-from-1} also implies that Chamfer
+norms, neighborhood sequences based norms can also be considered in
+separable Algorithm \ref{alg:voro}. We just need algorithmic tools to
+implement efficiently both \textsc{Closest} and \textsc{HiddenBy}
+predicates.
+
 \subsection{A First Generic Adapter}
@@
 
-In
+Let suppose that $(\Z^n,F,d)$ is a metric space induced by a norm. We
+can first detail the overall computational cost of Algorithm
+\ref{alg:voro}:
+
+\begin{lemma}
+\label{lem:generic}
+   Let $(\Z^n, F, d)$ be a metric space induced by a norm. If $C$
+  denotes the computational cost of \textsc{Closest} predicate and $H$
+  is the computational cost of the \textsc{HiddenBy} predicate, then
+  Algorithm \ref{alg:voro} is in
+  \begin{equation}
+    O(n\cdot N^n\cdot (C+H))\;.
+  \end{equation}
+\end{lemma}
+
+A first improvement is given by Algorithms~\ref{alg:genclosest},
+\ref{alg:genedge} and \ref{alg:genhidden}: we only require the metric
+to be known and \textsc{HiddenBy} predicate is obtained by a binary
+search on the 1D image span $S$ to localize the abscissa of Voronoi
+edges of sites $(a,b)$ and $(b,c)$ (see Fig.XXXXXX). Please note that
+from \cite{Breu1995,roerdnik}, $C=H=O(1)$ for $L_1,L_2$ and $L_\infty$
+norms.
+
+\begin{algorithm}[H]
+  \Return $d(a,b) < d(a,c)$\;
+  \caption{Generic \textsc{Closest}($a,b,c\in\Z^n$).\label{alg:genclosest}}
+\end{algorithm}
+
+\begin{algorithm}[H]
+  \If{$(j-i=1)$}
+     {
+       \Return  i
+     }
+     $mid  = i + (j-i)/2$\;
+     \eIf{\textsc{Closest}$(s_{mid},a,b)$}
+       {
+         \tcp{$s_{mid}$ closer to $a$}
+         \Return \textsc{VoronoiEdge}($a,b,s_{mid},s_j$)
+}
+ {
+         \tcp{$s_{mid}$ closer to $b$}
+         \Return \textsc{VoronoiEdge}($a,b,s_{i},s_{mid}$)
+}
+
+  \caption{Generic \textsc{VoronoiEdge}($a,b,s_i,s_j\in\Z^n$).\label{alg:genedge}}
+\end{algorithm}
+
+\begin{algorithm}[H]
+  $v_{ab}$ = \textsc{VoronoiEdge}$(a,b,s_1, s_{N_i})$\;
+  $v_{bc}$ = \textsc{VoronoiEdge}$(b,c,s_1, s_{N_i})$\;
+  \Return $(v_{ab}> v_{bc})$\;
+  \caption{Generic \textsc{HiddenBy}($a,b,c\in\Z^n; S$ in the $i^{th}$
+    direction).\label{alg:genhidden}}
+\end{algorithm}
+
+Hence, we obtain a first generic metric adapter to transform it into
+separable predicates:
+
+\begin{lemma}
+\label{lem:generic}
+   Let $(\Z^n, F, d)$ be a metric space induced by a norm. If $C$
+   denotes the computational cost of \textsc{Closest} predicate
+   Algorithm \ref{alg:voro},  with predicates from Algorithms
+   \ref{alg:genclosest} and \ref{alg:genhidden}, is in
+  \begin{equation}
+    O(n\cdot N^n\cdot C\cdot \log{N}))\;.
+  \end{equation}
+\end{lemma}
+
+If we consider a chamfer norm with $l$ facet unit ball, Eq.~(\ref{eq:1})
+suggests that $C=O(l)$. Hence, we have the following corollary
+\begin{corollary}
+  Let $\M$ be a chamfer norm whose rational ball has $l$ facets,
+  separable exact Voronoi map $\Pi_X$ can be obtained in
+ \begin{equation}
+    O(n\cdot N^n\cdot l \cdot \log{N}))\;.
+  \end{equation}
+\end{corollary}
+
+Please remember that naive implementation of chamfer mask distance
+transformation using raster scan approach would lead to a $O(l\cdot
+N^d)$ computational cost. In the following sections, we use the convex
+structure of $\B$ to design a first subquadratic algorithm for chamfer
+norms.
 
@@
 
+Let us consider a 2D chamfer norm $\M$ with $m$ weighted vectors (note
+that $l\EqDef|\B| = m$ in 2D). We suppose that vectors
+$\{v_k\}_{k=1\ldots m}$ are sorted counterclockwise. We define a wedge
+as a pair $(\vec{v_k},\vec{v_{k+1}})$ of vectors. To each wedge is
+associated a row $A_k$ in the minimal H-representation of $A$ ($A_k$
+can also be seen as a non-unit normal vectors to $\B$
+facets\cite{DBLP:journals/pr/NormandE09})
+
+Using these notations, \cite{Thiel_hdr,Strand2008} demonstrate that
+the distance evaluation of point $a$ can be obtained in two steps:
+First, we compute the wedge $(\vec{v_k},\vec{v_{k+1}})$, $a$ belongs
+to. Then,
+\begin{equation}
+\label{eq:2}
+  d_\M(O,a) = A_k\cdot a^T
+\end{equation}
+
+\begin{lemma}
+\label{lem:log}
+  Given a chamfer norm $\M$ in dimension 2 with $m$ vectors, the distance computation
+  and thus the \textsc{Closest} predicate are in $O(\log{m})$.
+\end{lemma}
+\begin{proof}
+  Since vectors are sorted counter-clockwise,
+  $(\vec{v_k},\vec{v_{k+1}})$ wedge can be obtained by a dichotomic
+  search with $\O(\log{m}$ steps. At each step, we compute the local
+  orientation of point $a$ w.r.t. a direction which is in $O(1)$. Once
+  the wedge has been obtained, Eq.~(\ref{eq:2}) returns the distance
+  value in $O(1)$.$\Box$
+\end{proof}
+
+Please note that in practical implementations, we can use symmetries
+in $\M$ vectors to only work on restrictions of chamfer mask
+directions.
+
+To optimize the \textsc{HiddenBy} predicate, we focus on the
+\textsc{VoronoiEdge} function. Given two points $a$ and $b$
+($a_i<b_i$) and a 1D image span $S$ along the $i^{th}$ dimension, we
+can to find the lowest abscissa $e_i$ of the point $e$ on $S$ such
+that $d(a,e) < d(b,e)$ and $d(a,e')\geq d(b, e')$ for any $e'$ with
+$e'_i>e_i$.
+
+Let us first suppose that we don't have $e$ but we know the wedges
+$(v_{k},v_{k+1})$ (resp. $(v_j,v_{j+1})$) such that the vector
+$(e-a)^T$ (resp. $(e-b)^T$) should belong to (see Fig.XXXXX). In this
+situation, we know that $e$ is the solution of
+\begin{equation}
+\label{eq:3}
+  A_k\cdot  (e-a)^T = A_j\cdot (e -b)^T\;.
+\end{equation}
+(since $e\in S$, we have one linear equation for one unknown
+$e_i$). As a consequence, if we know the wedges the Voronoi edge
+belongs to, we have the abscissa in $O(1)$ (see Algorithm \ref{alg:chamedge}).
+
+\begin{algorithm}[H]
+  $(v_k,v_{k+1})$ = \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_1,\vec{v}_m, S)$\;
+  $(v_j,v_{j+1})$ = \textsc{VoronoiEdgeWedge}$(b,a,\vec{v}_1,\vec{v}_m, S)$\;
+
+  Compute the abscissa $e_i$ of the point $e$ such that $A_k\cdot
+  (e-a)^T = A_j\cdot (e -b)^T$\;
+
+  \Return $e_i$\;
+  \caption{2D chamfer norm \textsc{VoronoiEdge}($a,b,s_i,s_j\in\Z^2$).\label{alg:chamedge}}
+\end{algorithm}
+
+To obtain both wedges, we use a dichotomic search similar to
+Algorithm~\ref{alg:genedge}: Algorithm~\ref{alg:chamedgew} returns the
+wedge associated to $a$ containing the Voronoi edge with respect to
+$b$. Applying this algorithm to obtain the $b$ wedge with respect to
+$a$ gives exactly  Algorithm \ref{alg:chamedge}.
+
+The dichotomic search shrinks the set of vectors
+$\{\vec{v}_i,\ldots,\vec{v}_j\}$ to end up is a wedge $(v_k,v_{k+1})$
+such that the intersection point between the straight line $(a +
+\vec{v}_k)$ and $S$ is in the Voronoi cell of $a$ and such that the
+intersection between $(a + \vec{v}_k)$ and $S$ is in the Voronoi cell
+of $b$. Algorithm~\ref{alg:chamedgew} thus first compute the
+intersection points associated with a wedge $(\vec{v}_{i+(j-i)/2},
+\vec{v}_{i+(j-i)/2+1})$ (lines $5-6$); Evaluates the distances at
+these points (lines $7-8$) and then decides which set
+$\{\vec{v}_i,\ldots,\vec{v}_{i+(j-i)/2}\}$ or
+$\{\vec{v}_{i+(j-i)/2},\ldots,\vec{v}_j\}$ has to be considered for
+the recursive call (lines $14-25$).
+
+\begin{algorithm}[H]
+  \eIf{ $(j-i =1)$}{
+    \Return $(\vec{v}_k,\vec{v}_{k+1})$\;}
+{
+   $mid  = i + (j-i)/2$\;
+   Let $p_{mid}$  be the intersection point between $(a +
+   \vec{v}_{mid})$ and $S$\;
+  Let $p_{mid+1}$  be the intersection point between $(a +
+   \vec{v}_{mid+1})$ and $S$\;
+
+   \tcp*[f]{$O(1)$ evaluation of distances w.r.t. $a$}
+   $d^a_{p_{mid}} = A_{mid}\cdot (p_{mid}-e)^T$\;
+   $d^a_{p_{mid+1}} = A_{mid+1}\cdot (p_{mid+1}-e)^T$\;
+
+   \tcp*[f]{$O(\log{m})$ evaluation of distances w.r.t. $b$}
+   $d^b_{p_{mid}} = d_\M(b, p_{mid})$\;
+   $d^b_{p_{mid+1}} = d_\M(b,p_{mid+1})$\;
+
+   Let $b_{mid}$ be true if $d^a_{p_{mid}} < d^b_{p_{mid}}$; false otherwise\;
+   Let $b_{mid+1}$ be true if $d^a_{p_{mid+1}} < d^b_{p_{mid+1}}$; false otherwise\;
+
+   \If{ $b_{mid}\neq b_{mid+1}$ \tcp*[r]{we have the Voronoi edge
+       wedge}} { \Return $(\vec{v}_{mid},\vec{v}_{mid+1})$\; }
+
+    \If{ $b_{mid}=b_{mid+1}=true$ \tcp*[r]{Both points are in $a$'s cell}}
+{
+    \eIf{$a_i < b_i$}
+{
+  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_{mid}, \vec{v}_{j}, S)$\;
+}
+{
+  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_{i}, \vec{v}_{mid}, S)$\;
+}
+
+}
+    \If{ $b_{mid}= b_{mid+1}=false$\tcp*[r]{Both points are in $b$'s cell}}
+{
+    \eIf{$a_i < b_i$}
+{
+  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_{i}, \vec{v}_{mid}, S)$\;
+}
+{
+  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_{mid}, \vec{v}_{j}, S)$\;
+}
+
+}
+
+}
+  \caption{\textsc{VoronoiEdgeWedge}($a,b\in\Z^2; \vec{v}_i,\vec{v}_j$
+    in $\M$; $S$ along the $i^{th}$ direction).\label{alg:chamedgew}}
+\end{algorithm}
+
+\begin{theorem}
+  Let $\M$ be a 2D chamfer norm with $m$ weighted vectors, then we
+  have
+  \begin{enumerate}[(i)]
+  \item Algorithm     \ref{alg:chamedge} is   $O(\log^2{m})$\;;
+  \item Algorithm \ref{alg:voro} (with predicates from Algorithms
+    \ref{alg:chamedge} and Lemma \ref{lem:log}), computes a Voronoi
+    map $\Pi_X$ and thus the distance transformation of $X$ for metric
+    $d_{M}$ in
+  \begin{equation}
+    O( \log^2{m}\cdot N^2)\;.
+  \end{equation}
+  \end{enumerate}
+\end{theorem}
+\begin{proof}
+Let us first consider statement $(i)$. As described above, Algorithm
+\ref{alg:chamedgew} performs $\log{m}$ recursive calls and each step
+is in $O(\log{m})$. Indeed, $p_{mid}$ and $p_{mid+1}$ are given by the
+intersections between two rational slope straight lines plus a
+rounding operation on fractions, which are assumed to be $O(1)$. Then,
+line 8 requires two $O(\log{m})$ computations by
+Lemma~\ref{lem:log}. Hence, Eq.~(\ref{eq:3}) leads to $O(1)$
+computations, $O(\log^2{m})$ is required for
+Algorithm~\ref{alg:chamedge}.
+
+Statement $(ii)$ is a direct consequence of statement $(i)$ and
+$O(1)$ and Lemma~\ref{lem:generic} with $n=2$.$\Box$
+\end{proof}
+
 \subsection{Subquadratic Algorithms in Higher Dimension}
 \label{sec:subq-algor-high}
+In this section, we consider a general chamfer norm in arbitrary
+dimension $n$.  First, let us discuss about distance evaluation:
+\begin{lemma}
+   Let $\M$ be a chamfer norm with $m$ weighted vectors in dimension
+  $n$, then distance computation and thus \textsc{Closest} predicate
+  are in (amortized) $O(\log{m})$.
+\end{lemma}
+\begin{proof}
+ Similarly to the 2D case, the distance $d_\M(O,a)$ for $a\in\Z^n$ is
+ given by first solving a ray-shooting problem on convex polytopes
+ which consists in first computing the $(n-1)$-facet of $\B$ pierced by the
+ ray $(O,a)$. Once the facet is obtained, the associated $A_k$ row is
+ obtained to evaluate
+ \begin{displaymath}
+   d_\M(O,a) = A_k\cdot a^T\;.
+ \end{displaymath}
+Following \cite{DBLP:journals/dcg/MatousekS93}, such ray-shooting
+requests on convex polytopes can be solved in $O(\log{m})$ thanks to a
+preprocessing in $O()$
+  $\Box$
+\end{proof}
+
+\begin{theorem}
+  Let $\M$ be a chamfer norm with $m$ weighted vectors in dimes ion
+  $n$, Voronoi map $\Pi_X$ and thus the distance transformation of $X$
+  for metric $d_{M}$ can be obtained in
+  \begin{equation}
+    O(n\log^2{m}\cdot N^n)
+  \end{equation}
+  \end{enumerate}
+\end{theorem}
 

### 2014-02-12 latex/dgci2014/article.tex
article

@@
 \usepackage{amsmath,amssymb}
+\usepackage{url}
 \usepackage{overpic}
@@
 diagram based Euclidean distance
-\cite{BreuEtAl95,GotLin95,Guan,maurer_pami} or the square of the
+\cite{BreuEtAl95,maurer_pami} or the square of the
 Euclidean distance \cite{SaitTori:94,Hirata,roerdnik}.
@@
 \paragraph{Contributions} In this article,
+
+\begin{table}
+  \caption{Complexity summary.}
+  \label{tab:final}
+  \begin{center}
+    \begin{tabular}{|c|c|c|c|c|}
+      \hline
+      Metric &\textsc{Closest}& \textsc{HiddenBy} & Sep. Voronoi Map & Reference\\
+      \hline
+      $L_2$ & $O(1)$ &  $O(1)$ & $\Theta(n\cdot N^n)$ & \cite{Hirata1996}\\
+      $L_\infty$ & $O(1)$ & $O(1)$ &  $\Theta(n\cdot N^n)$ & \cite{roerdnik}\\
+      $L_1$ & $O(1)$ &   $O(1)$ &$\Theta(n\cdot N^n)$& \cite{roerdnik}\\
+      $L_p$  (exact pred.) & $O(\log{p})$ &
+      $O(\log{p}\cdot\log{N})$ & $O(n\cdot
+      N^n\cdot\log{p}\cdot\log{N})$& here and  \cite{dgtal}\\
+      $L_p$  (inexact pred.) & $O(1)$ &
+      $O(\log{N})$ & $O(n\cdot
+      N^n\cdot\log{N})$& here and  \cite{dgtal}\\
+      2D Chamfer norm &  $O(\log{m})$ &$O(\log^2{m})$
+      &$O(\log^2{m}\cdot N^2)$& Theorem \ref{them}\\
+      3D Chamfer norm &  $O(\log{m})$ &$O(\log^2{m})$
+      &$O(\log^2{m}\cdot N^3)$& Theorem \ref{them2}\\
+      nD Chamfer norm &  $O(n\cdot\log{f})$ &$O(n\cdot log^2{f}\cdot\log{N})$
+      & $O(n^2\cdot N^n\cdot \log{f}\cdot\log{N})$& Corollary \ref{coro2}\\
+      2D Neig. sequence norm  & $O(\log{m})$&
+      $O(\log^2{m})$& $O(\log^2{m}\cdot N^2)$& Theorem \ref{them} and  \cite{DBLP:conf/dgci/NormandSE13}\\
+      \hline
+    \end{tabular}
+  \end{center}
+\end{table}
 
@@
   \begin{equation}
+\label{eq:4}
     \B = conv\left\{ \frac{\vec{v}_i}{w_i};\; (\vec{v}_i,w_i)\in\M \right \}\,.
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[H]\small
   \KwData{Input binary map $I_X$ if $i=1$ or  partial Voronoi map $\Pi_X$ obtained for
@@
   \begin{center}
-     \begin{overpic}[draft=false,width=12cm]{figs/edt_dcoeurjo}
+     \begin{overpic}[draft=false,width=10cm]{figs/edt_dcoeurjo}
        \put(30,5){$Candidates_S$}
@@
 (resp. $b$) and l, then $v_l(a)$ and $v_l(b)$ are simply connected
-Euclidean segments and $v_l(a)$ appears \emph{before} $v_l(b)$ on
-$l$ (so called \emph{monotonicity property} in \cite{Maurer2003} and is
-related to \emph{quadrangle inequality} in \cite{Hirata1996}).
-
-To sum up these contributions, we use the following proposition
-adapted from \cite{Hirata1996}.
+Euclidean segments and $v_l(a)$ appears \emph{before} $v_l(b)$ on $l$
+(so called \emph{monotonicity property} in \cite{Maurer2003} and is
+related to \emph{quadrangle inequality} in \cite{Hirata1996}).  To sum
+up these contributions, we use the following proposition:
 \begin{proposition}[Metric conditions \cite{Hirata1996}]
 \label{prop:voronoi-map-from-1}
-  If $d$ is a metric induced by a norm and if distance comparison
-  predicate $d(a,b)<d(c,d)$ is exact (for $a,b,c,d\in\Z^n$), Algorithm
-  1 is correct and returns a Voronoi map $\Pi_X$.
+  Let $d$ be a metric induced by a norm whose unit ball is symmetric
+  with respect to grid axis. If distance comparison predicate
+  $d(a,b)<d(c,d)$ is exact (for $a,b,c,d\in\Z^n$), Algorithm 1 is
+  correct and returns a Voronoi map $\Pi_X$.
 \end{proposition}
@@
 considering the $p$ power of the distance function $\left
-(d_{L_p}\right)^p$.
-
-Proposition \ref{prop:voronoi-map-from-1} also implies that Chamfer
-norms, neighborhood sequences based norms can also be considered in
-separable Algorithm \ref{alg:voro}. We just need algorithmic tools to
-implement efficiently both \textsc{Closest} and \textsc{HiddenBy}
-predicates.
+(d_{L_p}\right)^p$.  Proposition \ref{prop:voronoi-map-from-1} also
+implies that Chamfer norms, neighborhood sequences based norms can
+also be considered in separable Algorithm \ref{alg:voro}. We just need
+algorithmic tools to implement efficiently both \textsc{Closest} and
+\textsc{HiddenBy} predicates.
 
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[H]\small
   \Return $d(a,b) < d(a,c)$\;
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[H]\small
   \If{$(j-i=1)$}
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}[H]\small
   $v_{ab}$ = \textsc{VoronoiEdge}$(a,b,s_1, s_{N_i})$\;
@@
   $(\vec{v_k},\vec{v_{k+1}})$ wedge can be obtained by a dichotomic
-  search with $\O(\log{m}$ steps. At each step, we compute the local
+  search with $O(\log{m})$ steps. At each step, we compute the local
   orientation of point $a$ w.r.t. a direction which is in $O(1)$. Once
@@
 belongs to, we have the abscissa in $O(1)$ (see Algorithm \ref{alg:chamedge}).
-
-\begin{algorithm}[H]
+\begin{algorithm}[h]\small
   $(v_k,v_{k+1})$ = \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_1,\vec{v}_m, S)$\;
@@
 \end{algorithm}
-
 To obtain both wedges, we use a dichotomic search similar to
@@
 
-\begin{algorithm}[H]
+\begin{algorithm}
+\small
   \eIf{ $(j-i =1)$}{
@@
 \begin{theorem}
+\label{them}
   Let $\M$ be a 2D chamfer norm with $m$ weighted vectors, then we
@@
 In this section, we consider a general chamfer norm in arbitrary
-dimension $n$.  First, let us discuss about distance evaluation:
+dimension $n$.  First, let us discuss about chamfer mask
+combinatorics. If $m$ denotes the number of weighted vectors of $\M$,
+its rational ball $\B$ has $O(m^{\lfloor \frac{n}{2}\rfloor})$
+$i-$facets ($0 \leq i \leq d$) \cite{deberg}. If we denote by $f$ the
+number of $(n-1)-$facets of $\B$ (\emph{i.e.} number of row in the
+H-representation of $\B$), we have by duality the result that $|\B| =
+O(f^{\lfloor \frac{n}{2}\rfloor})$. As a consequence, we have the
+following distance evaluation result:
+
 \begin{lemma}
-   Let $\M$ be a chamfer norm with $m$ weighted vectors in dimension
-  $n$, then distance computation and thus \textsc{Closest} predicate
-  are in (amortized) $O(\log{m})$.
+\label{lem:distnD}
+   Let $\M$ be a chamfer norm whose rational ball $\B$ has $f$
+   $(n-1)-$facets in dimension $n$, then distance computation and thus
+   \textsc{Closest} predicate are in (amortized) $O(n\cdot\log{f})$ with
+   $O\left (\frac{f^{\lfloor \frac{n}{2}\rfloor}}{(\log{ f})^{\lfloor
+       \frac{n}{2}\rfloor-\delta}}\right)$ space and preprocessing
+   time ($\delta$ is arbitrarily small positive constant).
 \end{lemma}
@@
  ray $(O,a)$. Once the facet is obtained, the associated $A_k$ row is
- obtained to evaluate
+ used to evaluate
  \begin{displaymath}
-   d_\M(O,a) = A_k\cdot a^T\;.
+   d_\M(O,a) = A_k\cdot a^T\;,
  \end{displaymath}
-Following \cite{DBLP:journals/dcg/MatousekS93}, such ray-shooting
-requests on convex polytopes can be solved in $O(\log{m})$ thanks to a
-preprocessing in $O()$
-  $\Box$
+in $O(n)$.  Following \cite{DBLP:journals/dcg/MatousekS93}, such
+ray-shooting requests on convex polytopes can be solved in
+$O(\log{f})$ thanks to a preprocessing in $O\left (\frac{f^{\lfloor
+    \frac{n}{2}\rfloor}}{(\log{ f})^{\lfloor
+    \frac{n}{2}\rfloor-\delta}}\right)$. Please note that this
+preprocessing time is roughly equivalent to the convex hull
+computation in higher dimension which is in $O(f^{\lfloor
+  \frac{n}{2}\rfloor})$. Hence, preprocessing for ray-shooting can be
+done while computing the $\B$ rational ball using
+Eq.~(\ref{eq:4}).$\Box$
 \end{proof}
 
+From Lemmas~\ref{lem:generic} and~\ref{lem:distnD}, we first have:
+\begin{corollary}
+\label{coro2}
+   Let $\M$ be a chamfer norm whose rational ball $\B$ has $f$
+   $(n-1)-$facets in dimension $n$, separable exact Voronoi Map
+   $\Pi_X$ can be obtained in
+   \begin{equation}
+     O(n^2\cdot N^n\cdot \log{f}\cdot\log{N})
+   \end{equation}
+thanks to a preprocessing in $O\left (\frac{f^{\lfloor
+    \frac{n}{2}\rfloor}}{(\log{ f})^{\lfloor
+    \frac{n}{2}\rfloor-\delta}}\right)$.
+\end{corollary}
+
+In higher dimension, we can still expect fast
+\textsc{VoronoiEdgeWedge} function. Let us consider the 3D case
+$n=3$ (and thus $f=O(m)$). In this situation, it turns out that the problem can be turned
+into a simple, 2D one: Given two points $a,b\in\Z^3$ and an isothetic
+line $l$, we need to compute the intersection between the Voronoi
+$2-$facet defined by $a$ and $b$ and $l$. Let us suppose that this the
+intersection point exists and that $a$, $b$ and $l$ are in
+\emph{general position} ($a\not\subset l$, $b\not\subset l$).  Then,
+the intersection point belongs to the two Euclidean planes $P_a$ and
+$P_b$, $P_a$ being respectively the Euclidean plane containing $a$ and
+$l$ (resp. $P_b$ defined by $b$ and $l$), see Fig.\ref{fig:3D}.
+
+To construct a variant of \textsc{VoronoiEdgeWedge} in 3D, we just
+have to replace the line 4 of Algorithm~\ref{alg:chamedgew} by the
+following steps: First, we construct $\vec{v} = (\vec{v}_i +
+\vec{v}_j)/2$. If we suppose that $\vec{v}_i$ and $\vec{v}_j$ belongs
+to $P_a$, $\vec{v}$ also belongs to $P_a$. Then, we perform a 3D
+ray-shooting to get the facet $F$ of $\B$ pierced by vector
+$\vec{v}$. From this facet $F$, we construct the 2D
+$(\vec{v}_{mid},\vec{v}_{mid+1})$ wedge on $P_a$ defined by the
+intersection of $F$ and $P_a$. Once $(\vec{v}_{mid},\vec{v}_{mid+1})$
+is obtained, we proceed with the rest of the \textsc{VoronoiEdgeWedge}
+function (point intersection construction, distance evaluations and
+recursive calls). Please note that the 3D ray shooting can be obtained
+in $O(\log{m})$. Hence, we have:
+
+\begin{lemma}
+\label{lem:wedge3D}
+  Let $\M$ be a chamfer norm with $m$ weighted vectors in dimension
+  3. We assume that the $m$ vectors span uniformly the set of
+  directions in $\R^3$, the 3D version of \textsc{VoronoiEdgeWedge} is
+  in
+  \begin{equation}
+    O(\log^2{m})\,.
+  \end{equation}
+\end{lemma}
+
+\begin{proof}
+  As in dimension 2, each step can be done in $O(\log{m})$
+  computations. Please note that ray-shooting, and intersection
+  computation between a (rational slope) facet $F$ and the (rational)
+  plane $P_a$ can be obtained in $O(1)$.  If we denote by $\M_{P_a}$
+  be the 2D chamfer norm induced by $\B\cap P_a$. The hypothesis that
+  the vectors uniformly span the sphere of directions is here to
+  ensure that if we split $\M_{P_a}$ along the mid direction
+  $\vec{v} =(\vec{v}_i + \vec{v}_j)/2$, both subsets of vectors have the same
+  size. If so, $O(\log{m})$ recursive calls is required. The stop
+  criterion of the recurrence could be that $\vec{v}$ belong to the
+  same facet as both $\vec{v}_i$ and $\vec{v}_j$.$\Box$
+\end{proof}
+
+From Lemma~\ref{lem:wedge3D} and proof of Theorem~\ref{them}, we
+conclude with the following result:
+
 \begin{theorem}
-  Let $\M$ be a chamfer norm with $m$ weighted vectors in dimes ion
-  $n$, Voronoi map $\Pi_X$ and thus the distance transformation of $X$
+\label{them2}
+  Let $\M$ be a chamfer norm with $m$ weighted vectors in dimension 3,
+  the Voronoi map $\Pi_X$ and thus the distance transformation of $X$
   for metric $d_{M}$ can be obtained in
   \begin{equation}
-    O(n\log^2{m}\cdot N^n)
+    O(\log^2{m}\cdot N^3)\;.
   \end{equation}
-  \end{enumerate}
 \end{theorem}
 
-\section{Experimental Analysis}
+\section{Implementation Details and Experimental Analysis}
 \label{sec:exper-analys}
 
-\subsection{Implementation details}
-\label{sec:impl-deta}
+In this section, we present some implementation details and
+experimental results for chamfer norm DT in dimension 2.
 
-\subsection{Voronoi Maps in dimension 2}
-\label{sec:impl-2D}
+First of all, since release 0.7, most algorithms presented here are
+available in the \textsc{DGtal} library \cite{dgtal}. For $L_p$
+metrics, several \textsc{Closest} and \textsc{HiddenBy} predicates are
+available:
+\begin{itemize}
+\item If $p=\{1,2,\infty\}$, exact computations are proposed and all
+  predicates are in $O(1)$ with only integer number computations
+  \cite{Hirata1996,Maurer2003,roerdnik};
+\item If $p\in \R$,  $p\geq 1$, we have approximated computations
+  on real numbers (\emph{double}) and we consider the Generic
+  \textsc{HiddenBy} predicate in $O(\log N)$
+  (Alg.~\ref{alg:genhidden})\;
+\item if $p\in \Z$, $p\geq 3$, we use exact integer number based
+  computations of distances  storing sum of power $p$ quantities (which can be
+  computed in $O(\log{p})$ thanks to exponentiation by squaring). The
+  \textsc{HiddenBy} predicate is also based on Algorithm~\ref{alg:genhidden}.
+\end{itemize}
+
+Beside these predicates for $L_p$ metrics, \textsc{DGtal} also
+contains a generic metric adapter: if the user specifies a distance
+function (taking two points and returning a value) corresponding to a
+norm, generic \textsc{Closest} and \textsc{HiddenBy} predicates can be
+automatically constructed. Please note that since all algorithms are
+separable, generic framework provided in \textsc{DGtal} allow us to
+have a free multi-thread implementation \cite{dcoeurjo_ChapDTWADGMM}.
+
+To implement efficient predicates leading to subquadratic algorithm in
+dimension 2 (Alg.~\ref{alg:chamedge} and \ref{alg:chamedgew}), we
+store the chamfer norm weighted vectors $\M$ in a random access
+container sorted counterclockwise to be able to get the mid-vector
+$\vec{v}_{mid}$ in $O(1)$.
+
+To be able to evaluate experimentally the
+computational cost given in Theorem~\ref{them}, we use the following
+setting: given a mask size $m$, we generate $m$ distinct random
+vectors $(x,y)^T$ with $gcd(x,y)=1$ (extracted from Farey series for
+instance). For a general mask of size $m$, we do not try to optimize
+the weights to approximate as best as possible the Euclidean metric
+(\emph{e.g.}  \cite{borgefors}). Weights do not play any role in the
+computational analysis, we just use here trivial weights that ensure
+that $\M$ is a norm.
+\begin{figure}[H]
+  \includegraphics[width=\textwidth]{data/result}
+  \caption{Experimental evaluation of subquadratic chamfer norm
+    Voronoi map computation.}
+  \label{fig:graph}
+\end{figure}
+In Fig.\ref{fig:graph}, we have considered a 2D domain $2048^2$ with
+$2048$ random sites (and chamfer norm with increasing size
+$m$). First, we observe that fixing $N$, the $\log^2{m}$ term is
+clearly visible in the computational cost of the Voronoi map (single
+thread curve). Bumps in the single thread curve may be due to memory
+cache issues. Please note that if we consider classical chamfer norm
+DT from raster scan (and half-masks), the computational cost would
+have been in $O(m\cdot N^2)$ and thus would have a linear behavior in
+Fig.~\ref{fig:graph}.
+
+Since we have a separable algorithm, we can trivially implement it in
+a multi-thread environment. Hence, on a bi-processor and quad-core
+(hyperthreading) Intel(R) Xeon(R) cpu (16 threads can run in
+parallel), we observe a speed-up by a factor 10 (multi-thread) curve
+in Fig.~\ref{fig:graph}).
+
+Please note that on this $2048^2$ domain with 2048 sites, Euclidean
+Voronoi Map ($L_2$) is obtained in  954.837 milliseconds on a single
+core and 723.196 msec on 16 cores.
 

### 2014-02-12 latex/dgci2014/data/trace.py

@@ -1,0 +1,262 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import pylab
+import glob
+import os
+
+from matplotlib import rc
+##rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+rc('text', usetex=True)
+
+current_path=os.getcwd()
+
+myx = np.linspace(0.01, 300000)
+mylog2 = np.log(myx)*np.log(myx)
+
+fig = plt.figure()
+axes = fig.add_subplot( 1, 1, 1 )
+
+datalist = pylab.loadtxt( "statVoronoi-mono.txt" )
+datalist2 = pylab.loadtxt( "statVoronoi-openmp.txt" )
+
+#plt.legend( loc=2 )
+plt.xlabel( "$m$" )
+plt.ylabel( 'Time in sec' )
+
+p1,=plt.plot( datalist[:,0],datalist[:,1]/1000, 'g',label="Voronoi Map (single thread)",alpha=1 )
+p2,=plt.plot( datalist2[:,0],datalist2[:,1]/1000, 'b',label="Voronoi Map (multi-thread)",alpha=1 )
+p3,=plt.plot( myx, 0.04*mylog2, '.r',label="$0.04\log^2{m}$",alpha=0.5 )
+p4,=plt.plot( myx, 0.4*mylog2, '.',label="$4\log^2{m}$",alpha=0.5 )
+
+lines=[p1,p2,p3,p4]
+##plt.legend( loc=2 )
+plt.legend(lines, [l.get_label() for l in lines], loc=7,frameon=False)
+
+
+##plt.show()
+plt.savefig( 'result.pdf', format='PDF' )
+
+
+
+#   #  o     o ooo.   .oPYo.      .oo
+#   #  8b   d8 8  `8. 8    8     .P 8
+#   #  8`b d'8 8   `8 8         .P  8
+#   #  8 `o' 8 8    8 8        oPooo8
+#   #  8     8 8   .P 8    8  .P    8
+#   #  8     8 8ooo'  `YooP' .P     8
+#   #  ..::::.......:::.....:..:::::..
+#   #  :::::::::::::::::::::::::::::::
+#   #  :::::::::::::::::::::::::::::::
+#   list_of_files = []
+#   for current_file in glob.glob( "StatisticsMDCA_*.dat" ):
+#       list_of_files.append( current_file )
+
[…]

### 2014-02-12 latex/dgci2014/article.tex
edis

@@
       & $O(n^2\cdot N^n\cdot \log{f}\cdot\log{N})$& Corollary \ref{coro2}\\
-      2D Neig. sequence norm  & $O(\log{m})$&
-      $O(\log^2{m})$& $O(\log^2{m}\cdot N^2)$& Theorem \ref{them} and  \cite{DBLP:conf/dgci/NormandSE13}\\
+      2D Neig. sequence norm  & $O(\log{f})$&
+      $O(\log^2{f})$& $O(\log^2{f}\cdot N^2)$& Theorem \ref{them} and  \cite{DBLP:conf/dgci/NormandSE13}\\
       \hline
@@
 but not a vector space) \cite{Thiel_hdr}.
-
-From the literature, path-based approaches (Chamfer masks, (weighted)
+From the literature, path-based approaches (Chamfer masks, -weighted-
 neighborhood sequences...)  aim at defining metrics induced by norms
@@
 \begin{equation}
-    d_{\ell_p} (a,b) = \left ( \sum_{i=0}^n w_i|a_i-b_i |^p \right )^{\frac{1}{p}}\,
+    d_{L_p} (a,b) = \left ( \sum_{i=0}^n w_i|a_i-b_i |^p \right )^{\frac{1}{p}}\;,
   \end{equation}
-characterize metric spaces $(\Z^n, \R , d_{\ell_p})$. However,
-rounding the metric $(\Z^n,\Z, \lceil d_{\ell_p}\rceil)$ implies a
+characterize metric spaces $(\Z^n, \R , d_{L_p})$. However,
+rounding the distance function $(\Z^n,\Z, \lceil d_{L_p}\rceil)$ implies a
 metric space \cite{klette_book}.
@@
   \begin{equation}
-    DT_X(a) = \min_{b\in \Z^n\setminus X} \{d(a,b)\}
+    DT_X(a) = \min_{b\in \Z^n\setminus X} \{d(a,b)\}\;.
   \end{equation}
@@
   \begin{equation}
-    \Pi_X(a) = \argmin_{b\in \Z^n\setminus X} \{d(a,b)\}
+    \Pi_X(a) = \argmin_{b\in \Z^n\setminus X} \{d(a,b)\}\;.
   \end{equation}
@@
 Rational ball $\B$ can also be described in a H-representation of
-polytope with minimal parameter \cite{DBLP:conf/dgci/NormandSE13}
+polytope with minimal parameter \cite{DBLP:conf/dgci/NormandSE13}:
 \begin{equation}
   P = \{ x\in\Z^n; Ax \leq y\;\}\quad \text{ such that }  \forall
-  i\in[1\ldots l], \exists x\in P\quad A_ix=y_i\,.\footnote{$A_i$
+  i\in[1\ldots f], \exists x\in P\quad A_ix=y_i\,.\footnote{$A_i$
     being the $i^{th}$ row of $A$.}
 \end{equation}
-$l$ being the number of row in $A$ and the number of facets in $\B$,   and is thus related to $|\M|$.
+$f$ being the number of row in $A$ and the number of facets in $\B$,   and is thus related to $|\M|$.
 \end{definition}
@@
 \end{itemize}
+
+\begin{figure}
+  \begin{center}
+    \subfigure[]{ \begin{overpic}[width=4cm]{figs/hiddenByTrue}
+    \put(32,5){$a$}
+    \put(5,35){$b$}
+    \put(25,75){$c$}
+    \put(60,-10){$S$}
+    \end{overpic}}
+    \subfigure[]{\begin{overpic}[width=4cm]{figs/hiddenByFalse}
+    \put(37,8){$a$}
+    \put(23,37){$b$}
+    \put(35,72){$c$}
+    \put(60,-10){$S$}
+      \end{overpic}}~~~~~~~~~~
+    \subfigure[]{\begin{overpic}[width=2.1cm]{figs/closest}
+    \put(-5,52){$a$}
+    \put(2,78){$b$}
+    \put(47,55){$c$}
+    \put(38,-10){$S$}
+      \end{overpic}
+    }
+  \end{center}
+  \caption{xxxxxxxxxxx}
+  \label{fig:predicates}
+\end{figure}
+
 In other words, \textsc{HiddenBy} returns true if and only if the
@@
 \ref{alg:voro}:
-
 \begin{lemma}
@@
 \end{lemma}
-
 A first improvement is given by Algorithms~\ref{alg:genclosest},
@@
 
-If we consider a chamfer norm with $l$ facet unit ball, Eq.~(\ref{eq:1})
-suggests that $C=O(l)$. Hence, we have the following corollary
+If we consider a chamfer norm with $f$ facet unit ball, Eq.~(\ref{eq:1})
+suggests that $C=O(f)$. Hence, we have the following corollary
 \begin{corollary}
-  Let $\M$ be a chamfer norm whose rational ball has $l$ facets,
+  Let $\M$ be a chamfer norm whose rational ball has $f$ facets,
   separable exact Voronoi map $\Pi_X$ can be obtained in
  \begin{equation}
-    O(n\cdot N^n\cdot l \cdot \log{N}))\;.
+    O(n\cdot N^n\cdot f \cdot \log{N}))\;.
   \end{equation}
@@
 Please remember that naive implementation of chamfer mask distance
-transformation using raster scan approach would lead to a $O(l\cdot
+transformation using raster scan approach would lead to a $O(f\cdot
 N^d)$ computational cost. In the following sections, we use the convex
@@
 associated a row $A_k$ in the minimal H-representation of $A$ ($A_k$
-can also be seen as a non-unit normal vectors to $\B$
-facets\cite{DBLP:journals/pr/NormandE09})
-
-Using these notations, \cite{Thiel_hdr,Strand2008} demonstrate that
-the distance evaluation of point $a$ can be obtained in two steps:
-First, we compute the wedge $(\vec{v_k},\vec{v_{k+1}})$, $a$ belongs
-to. Then,
+can also be seen as a non-unit normal vectors to $\B$ facets
+\cite{DBLP:journals/pr/NormandE09}). Using similar notations,
+\cite{Thiel_hdr,Strand2008} demonstrate that the distance evaluation
+of point $a$ can be obtained in two steps: First, we compute the wedge
+$(\vec{v_k},\vec{v_{k+1}})$, $a$ belongs to. Then,
 \begin{equation}
@@
 that $\M$ is a norm.
-\begin{figure}[H]
-  \includegraphics[width=\textwidth]{data/result}
+\begin{figure}[htbp]
+  \begin{center}
+    \includegraphics[width=10cm]{data/result}
+  \end{center}
   \caption{Experimental evaluation of subquadratic chamfer norm

### 2014-02-12 latex/dgci2014/article.tex
edis

@@
 
-\author{David Coeurjolly\inst{1}}
+\author{David Coeurjolly}
 
  \institute{ CNRS,  LIRIS, UMR5205, F-69621, France\\
-   \email{david.coeurjolly@liris.cnrs.fr}
+   %\email{david.coeurjolly@liris.cnrs.fr}
 }
@@
 
-\begin{abstract}
+\begin{abstract}\sloppy
 In many applications, separable algorithms have demonstrated their
@@
 sequences, ...), we detail a subquadratic algorithm to compute such
-volumetric transformations. More precisely, we describe a
-$O(N\log^2(m))$ algorithm in dimension 2 for shapes with $N$ grid
-points and for example a chamfer mask of size $m$.
+volumetric transformations. For example, we describe a
+$O(\log^2{m}\cdot N^2)$ algorithm in dimension 2 for shapes in
+$N\times N$ domain with chamfer norm with size $m$.
 
@@
       2D Neig. sequence norm  & $O(\log{f})$&
-      $O(\log^2{f})$& $O(\log^2{f}\cdot N^2)$& Theorem \ref{them} and  \cite{DBLP:conf/dgci/NormandSE13}\\
+      $O(\log^2{f})$& $O(\log^2{}f\cdot N^2)$& Theorem \ref{them} and  \cite{DBLP:conf/dgci/NormandSE13}\\
       \hline
@@
 \label{sec:preliminaries}
-
 Let us first define some elementary concepts and objects.
@@
 instead of a metric. Note that in the following, we will only consider
-metric spaces with properties $(1-4)$. Furthermore, we may have to
+metric spaces with properties $(1-4)$. Furthermore, we
 consider  metrics induced by a vector space norm:
@@
  sequences.
-
 \section{Separable Distance Transformation}
 \label{sec:separ-dist-transf}
-
 \subsection{Voronoi Map from Separable Approach and Metric Conditions}
 \label{sec:voronoi-map-from}
-
 In \cite{Hirata1996,SaitTori:94,Breu1995,Meijster2000,Maurer2003},
@@
 
-\begin{algorithm}[H]\small
+\begin{algorithm}[H]\footnotesize
   \KwData{Input binary map $I_X$ if $i=1$ or  partial Voronoi map $\Pi_X$ obtained for
@@
 }
-  \ForEach{point  $s$ in $S$ by increasing $i^{th}$ component}
+  \ForEach{point  $s$ in $S$ by increasing $i^{th}$ coordinate}
   {
@@
 
-\begin{figure}
-  \begin{center}
-     \begin{overpic}[draft=false,width=10cm]{figs/edt_dcoeurjo}
-       \put(30,5){$Candidates_S$}
-       \put(57,0){$S$}
-     \end{overpic}
-  \end{center}
-  \caption{Voronoi Map construction in dimension 2.\label{fig:2Dbreu}}
-\end{figure}
+%% \begin{figure}
+%%   \begin{center}
+%%      \begin{overpic}[draft=false,width=10cm]{figs/edt_dcoeurjo}
+%%        \put(30,5){$Candidates_S$}
+%%        \put(57,0){$S$}
+%%      \end{overpic}
+%%   \end{center}
+%%   \caption{Voronoi Map construction in dimension 2.\label{fig:2Dbreu}}
+%% \end{figure}
 
@@
 row, columns and higher dimension spans. In this process, metric
-information are embedded in the following two predicates:
-\begin{itemize}
-  \item \textsc{Closest}$(a, b, c)$: given three points $a,b,c\in\Z^n$
-    this predicate returns true if $d(a,b) < d(a,c)$ ;
-  \item \textsc{HiddenBy}$(a, b, c, S)$: given three points
-    $a,b,c\in\Z^n$ such that $a_i<b_i<c_i$ and a 1D image span $S^i$, this predicates returns
-    true if there is no  $s\in S$ such that
+information are embedded in the following two predicates (see Fig.~\ref{fig:predicates}):
+\textsc{Closest}$(a, b, c)$: given three points $a,b,c\in\Z^n$ this
+predicate returns true if $d(a,b) < d(a,c)$. \textsc{HiddenBy}$(a, b,
+c, S)$: given three points $a,b,c\in\Z^n$ such that $a_i<b_i<c_i$ and
+a 1D image span $S^i$, this predicates returns true if there is no
+$s\in S$ such that
     \begin{equation}
@@
     \end{equation}
-\end{itemize}
 
@@
   \begin{center}
-    \subfigure[]{ \begin{overpic}[width=4cm]{figs/hiddenByTrue}
+    \subfigure[]{ \begin{overpic}[width=3cm]{figs/hiddenByTrue}
     \put(32,5){$a$}
@@
     \end{overpic}}
-    \subfigure[]{\begin{overpic}[width=4cm]{figs/hiddenByFalse}
+    \subfigure[]{\begin{overpic}[width=3cm]{figs/hiddenByFalse}
     \put(37,8){$a$}
@@
       \end{overpic}}~~~~~~~~~~
-    \subfigure[]{\begin{overpic}[width=2.1cm]{figs/closest}
+    \subfigure[]{\begin{overpic}[width=1.68cm]{figs/closest}
     \put(-5,52){$a$}
@@
 along $S$ (\emph{e.g.} $A$ and $E$ \emph{hide} $C$ and $B$ on $S$ in
-Fig.~\ref{fig:2Dbreu}).  For $L_1$, $L_2$ and $L_\infty$ metrics,
+Fig.~\ref{fig:predicates}).  For $L_1$, $L_2$ and $L_\infty$ metrics,
 \textsc{Closest} and \textsc{HiddenBy} predicates can be computed in
@@
   is the computational cost of the \textsc{HiddenBy} predicate, then
-  Algorithm \ref{alg:voro} is in
-  \begin{equation}
-    O(n\cdot N^n\cdot (C+H))\;.
-  \end{equation}
+  Algorithm \ref{alg:voro} is in   $O(n\cdot N^n\cdot (C+H))$.
 \end{lemma}
@@
 
-\begin{algorithm}[H]\small
+\begin{algorithm}[H]\footnotesize
   \Return $d(a,b) < d(a,c)$\;
@@
 
-\begin{algorithm}[H]\small
+\begin{algorithm}[H]\footnotesize
   \If{$(j-i=1)$}
@@
 
-\begin{algorithm}[H]\small
+\begin{algorithm}[H]\footnotesize
   $v_{ab}$ = \textsc{VoronoiEdge}$(a,b,s_1, s_{N_i})$\;
@@
 
-Hence, we obtain a first generic metric adapter to transform it into
-separable predicates:
+Hence, we obtain a first generic adapter to transform any metric
+induced by a norm into separable predicates:
 
@@
    Algorithm \ref{alg:voro},  with predicates from Algorithms
-   \ref{alg:genclosest} and \ref{alg:genhidden}, is in
-  \begin{equation}
-    O(n\cdot N^n\cdot C\cdot \log{N}))\;.
-  \end{equation}
+   \ref{alg:genclosest} and \ref{alg:genhidden}, is in $O(n\cdot N^n\cdot C\cdot \log{N}))$.
 \end{lemma}
 
-If we consider a chamfer norm with $f$ facet unit ball, Eq.~(\ref{eq:1})
+If we consider a chamfer norm with $f$ facet rational ball, Eq.~(\ref{eq:1})
 suggests that $C=O(f)$. Hence, we have the following corollary
@@
   separable exact Voronoi map $\Pi_X$ can be obtained in
- \begin{equation}
-    O(n\cdot N^n\cdot f \cdot \log{N}))\;.
-  \end{equation}
+    $O(n\cdot N^n\cdot f \cdot \log{N})$.
 \end{corollary}
@@
 in $\M$ vectors to only work on restrictions of chamfer mask
-directions.
-
-To optimize the \textsc{HiddenBy} predicate, we focus on the
-\textsc{VoronoiEdge} function. Given two points $a$ and $b$
+directions.  To optimize the \textsc{HiddenBy} predicate, we focus on
+the \textsc{VoronoiEdge} function. Given two points $a$ and $b$
 ($a_i<b_i$) and a 1D image span $S$ along the $i^{th}$ dimension, we
@@
 belongs to, we have the abscissa in $O(1)$ (see Algorithm \ref{alg:chamedge}).
-\begin{algorithm}[h]\small
+\begin{algorithm}[h]\footnotesize
   $(v_k,v_{k+1})$ = \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_1,\vec{v}_m, S)$\;
@@
 \begin{algorithm}
-\small
+\footnotesize
   \eIf{ $(j-i =1)$}{
@@
     map $\Pi_X$ and thus the distance transformation of $X$ for metric
-    $d_{M}$ in
-  \begin{equation}
-    O( \log^2{m}\cdot N^2)\;.
-  \end{equation}
+    $d_{M}$ in   $ O( \log^2{m}\cdot N^2)$.
   \end{enumerate}
@@
 Algorithm~\ref{alg:chamedge}.
-
 Statement $(ii)$ is a direct consequence of statement $(i)$ and
@@
        \frac{n}{2}\rfloor-\delta}}\right)$ space and preprocessing
-   time ($\delta$ is arbitrarily small positive constant).
+   time\footnote{$\delta$ is arbitrarily small positive constant.}.
 \end{lemma}
@@
  used to evaluate
- \begin{displaymath}
-   d_\M(O,a) = A_k\cdot a^T\;,
- \end{displaymath}
+   $d_\M(O,a) = A_k\cdot a^T$
 in $O(n)$.  Following \cite{DBLP:journals/dcg/MatousekS93}, such
@@
    $(n-1)-$facets in dimension $n$, separable exact Voronoi Map
-   $\Pi_X$ can be obtained in
-   \begin{equation}
-     O(n^2\cdot N^n\cdot \log{f}\cdot\log{N})
-   \end{equation}
+   $\Pi_X$ can be obtained in     $O(n^2\cdot N^n\cdot
+   \log{f}\cdot\log{N})$,
 thanks to a preprocessing in $O\left (\frac{f^{\lfloor

### 2014-02-13 latex/dgci2014/article.tex
ok

@@
 sequences, ...), we detail a subquadratic algorithm to compute such
-volumetric transformations. For example, we describe a
-$O(\log^2{m}\cdot N^2)$ algorithm in dimension 2 for shapes in
+volumetric transformations in dimension 2. More precisely, we describe
+a $O(\log^2{m}\cdot N^2)$ algorithm in dimension 2 for shapes in
 $N\times N$ domain with chamfer norm with size $m$.
@@
       &$O(\log^2{m}\cdot N^2)$& Theorem \ref{them}\\
-      3D Chamfer norm &  $O(\log{m})$ &$O(\log^2{m})$
-      &$O(\log^2{m}\cdot N^3)$& Theorem \ref{them2}\\
-      nD Chamfer norm &  $O(n\cdot\log{f})$ &$O(n\cdot log^2{f}\cdot\log{N})$
-      & $O(n^2\cdot N^n\cdot \log{f}\cdot\log{N})$& Corollary \ref{coro2}\\
+  %    3D Chamfer norm &  $O(\log{m})$ &$O(\log^2{m})$
+  %    &$O(\log^2{m}\cdot N^3)$& Theorem \ref{them2}\\
+  %    nD Chamfer norm &  $O(n\cdot\log{f})$ &$O(n\cdot log^2{f}\cdot\log{N})$
+  %    & $O(n^2\cdot N^n\cdot \log{f}\cdot\log{N})$& Corollary \ref{coro2}\\
       2D Neig. sequence norm  & $O(\log{f})$&
-      $O(\log^2{f})$& $O(\log^2{}f\cdot N^2)$& Theorem \ref{them} and  \cite{DBLP:conf/dgci/NormandSE13}\\
+      $O(\log^2{f})$& $O(\log^2{}f\cdot N^2)$& Th.~\ref{them} and  \cite{DBLP:conf/dgci/NormandSE13}\\
       \hline
@@
 \end{definition}
-
 An important result for distance computation can be formalized as follows:
@@
 
+%% \begin{figure}
+%%   \begin{center}
+%%      \begin{overpic}[draft=false,width=10cm]{figs/edt_dcoeurjo}
+%%        \put(30,5){$Candidates_S$}
+%%        \put(57,0){$S$}
+%%      \end{overpic}
+%%   \end{center}
+%%   \caption{Voronoi Map construction in dimension 2.\label{fig:2Dbreu}}
+%% \end{figure}
+
+Algorithm \ref{alg:voro} describe the 1D processes to perform on each
+row, columns and higher dimension spans. In this process, metric
+information are embedded in the following two predicates (see Fig.~\ref{fig:predicates}):
+\textsc{Closest}$(a, b, c)$: given three points $a,b,c\in\Z^n$ this
+predicate returns true if $d(a,b) < d(a,c)$. \textsc{HiddenBy}$(a, b,
+c, S)$: given three points $a,b,c\in\Z^n$ such that $a_i<b_i<c_i$ and
+a 1D image span $S^i$, this predicates returns true if there is no
+$s\in S$ such that
+    \begin{equation}
+      d(b,s) < d(a,s)\text{ and }  d(b,s) < d(c,s)\,.
+    \end{equation}
 \begin{algorithm}[H]\footnotesize
@@
 \end{algorithm}
-
-%% \begin{figure}
-%%   \begin{center}
-%%      \begin{overpic}[draft=false,width=10cm]{figs/edt_dcoeurjo}
-%%        \put(30,5){$Candidates_S$}
-%%        \put(57,0){$S$}
-%%      \end{overpic}
-%%   \end{center}
-%%   \caption{Voronoi Map construction in dimension 2.\label{fig:2Dbreu}}
-%% \end{figure}
-
-Algorithm \ref{alg:voro} describe the 1D processes to perform on each
-row, columns and higher dimension spans. In this process, metric
-information are embedded in the following two predicates (see Fig.~\ref{fig:predicates}):
-\textsc{Closest}$(a, b, c)$: given three points $a,b,c\in\Z^n$ this
-predicate returns true if $d(a,b) < d(a,c)$. \textsc{HiddenBy}$(a, b,
-c, S)$: given three points $a,b,c\in\Z^n$ such that $a_i<b_i<c_i$ and
-a 1D image span $S^i$, this predicates returns true if there is no
-$s\in S$ such that
-    \begin{equation}
-      d(b,s) < d(a,s)\text{ and }  d(b,s) < d(c,s)\,.
-    \end{equation}
-
 \begin{figure}
   \begin{center}
-    \subfigure[]{ \begin{overpic}[width=3cm]{figs/hiddenByTrue}
-    \put(32,5){$a$}
-    \put(5,35){$b$}
+    \subfigure[]{ \begin{overpic}[width=2cm]{figs/hiddenByTrue}
+    \put(26,5){$a$}
+    \put(0,35){$b$}
     \put(25,75){$c$}
-    \put(60,-10){$S$}
+    \put(55,-15){$S$}
     \end{overpic}}
-    \subfigure[]{\begin{overpic}[width=3cm]{figs/hiddenByFalse}
+    \subfigure[]{\begin{overpic}[width=2cm]{figs/hiddenByFalse}
     \put(37,8){$a$}
     \put(23,37){$b$}
-    \put(35,72){$c$}
-    \put(60,-10){$S$}
+    \put(30,72){$c$}
+    \put(55,-15){$S$}
     \end{overpic}}~~~~~~~~~~
-    \subfigure[]{\begin{overpic}[width=1.68cm]{figs/closest}
+    \subfigure[]{\begin{overpic}[width=1.1cm]{figs/closest}
     \put(-5,52){$a$}
@@
     \put(47,55){$c$}
-    \put(38,-10){$S$}
+    \put(38,-15){$S$}
       \end{overpic}
@@
 \textsc{HiddenBy} predicates.
+
+\begin{figure}
+ {\includegraphics[width=1.65cm]{image-ball-1}}
+ {\includegraphics[width=1.65cm]{image-ball-1_3999999999999999.png}}
+ {\includegraphics[width=1.65cm]{image-ball-2}}
+ {\includegraphics[width=1.65cm]{image-ball-4}}
+ {\includegraphics[width=1.65cm]{image-ball-43_100000000000001.png}}
+ {\includegraphics[width=1.65cm]{image-ball-chamf34}}
+ {\includegraphics[width=1.65cm]{image-ball-chamf5711}}
+  \caption{Balls for different metrics satisfying Proposition \ref{prop:voronoi-map-from-1}: \emph{(from
+      left to right)} $L_1$, $L_{1.4}$, $L_2$, $L_4$, $L_{43.0}$,
+    $\M_{3-4}$ and $\M_{5-7-11}$.}
+  \label{fig:metrics}
+\end{figure}
 
@@
 $(v_{k},v_{k+1})$ (resp. $(v_j,v_{j+1})$) such that the vector
-$(e-a)^T$ (resp. $(e-b)^T$) should belong to (see Fig.XXXXX). In this
+$(e-a)^T$ (resp. $(e-b)^T$) should belong to (see Fig.~\ref{fig:algo}). In this
 situation, we know that $e$ is the solution of
@@
 
+\begin{figure}[htbp]
+  \begin{center}
+    \subfigure[]{
+      \begin{overpic}[width=3.2cm]{init}
+        \put(-5,60){$a$}
+        \put(85,40){$b$}
+        \put(42,105){$S$}
+      \end{overpic}
+    }~~~~~~~~~
+    \subfigure[]{
+      \begin{overpic}[width=3.2cm]{algoMid}
+      \put(-5,60){$a$}
+        \put(85,40){$b$}
+        \put(42,105){$S$}
+        \put(12,60){$\vec{v_{mid}}$}
+        \put(13,80){$\vec{v_{mid+1}}$}
+        \put(-5,98){$\vec{v_j}$}
+        \put(5,35){$\vec{v_i}$}
+        \put(50,90){$p_{mid+1}$}
+        \put(50,58){$p_{mid}$}
+      \end{overpic}
+    }~~~~~~~~~
+    \subfigure[]{
+      \begin{overpic}[width=3.2cm]{algoEnd}
+      \put(-5,60){$a$}
+        \put(85,40){$b$}
+        \put(42,105){$S$}
+        \put(50,50){$e$}
+        \put(10,50){$\vec{v_{k}}$}
+        \put(11,70){$\vec{v_{k+1}}$}
+        \put(60,40){$\vec{v_j}$}
+        \put(67,57){$\vec{v_{j+1}}$}
+      \end{overpic}
+    }
+  \end{center}
+  \caption{Illustrations notations of \textsc{VoronoiEdgeWedge} and
+    \textsc{VoronoiEdge}: $(a)$ initial problem, given two sites $a$
+    and $b$, we want to compute the intersection between $S$ and the
+    Voronoi edge of $a$ and $b$. $(b)$ an internal step of
+    \textsc{VoronoiEdgeWedge} to reduce the set of directions of $\M$
+    at $a$ (here the next recursive call will be on
+    $(v_i,v_{mid})$).$(c)$ final step of \textsc{VoronoiEdge} where
+    both wedges have been obtained and thus $e$ can be computed.}
+  \label{fig:algo}
+\end{figure}
+
 The dichotomic search shrinks the set of vectors
@@
 intersection between $(a + \vec{v}_k)$ and $S$ is in the Voronoi cell
-of $b$. Algorithm~\ref{alg:chamedgew} thus first compute the
+of $b$ (see Fig.~\ref{fig:algo}$-(b)$). Algorithm~\ref{alg:chamedgew} thus first compute the
 intersection points associated with a wedge $(\vec{v}_{i+(j-i)/2},
@@
 
-\subsection{Subquadratic Algorithms in Higher Dimension}
-\label{sec:subq-algor-high}
-In this section, we consider a general chamfer norm in arbitrary
-dimension $n$.  First, let us discuss about chamfer mask
-combinatorics. If $m$ denotes the number of weighted vectors of $\M$,
-its rational ball $\B$ has $O(m^{\lfloor \frac{n}{2}\rfloor})$
-$i-$facets ($0 \leq i \leq d$) \cite{deberg}. If we denote by $f$ the
-number of $(n-1)-$facets of $\B$ (\emph{i.e.} number of row in the
-H-representation of $\B$), we have by duality the result that $|\B| =
-O(f^{\lfloor \frac{n}{2}\rfloor})$. As a consequence, we have the
-following distance evaluation result:
+%% \subsection{Subquadratic Algorithms in Higher Dimension}
+%% \label{sec:subq-algor-high}
+%% In this section, we consider a general chamfer norm in arbitrary
+%% dimension $n$.  First, let us discuss about chamfer mask
+%% combinatorics. If $m$ denotes the number of weighted vectors of $\M$,
+%% its rational ball $\B$ has $O(m^{\lfloor \frac{n}{2}\rfloor})$
+%% $i-$facets ($0 \leq i \leq d$) \cite{deberg}. If we denote by $f$ the
+%% number of $(n-1)-$facets of $\B$ (\emph{i.e.} number of row in the
+%% H-representation of $\B$), we have by duality the result that $|\B| =
+%% O(f^{\lfloor \frac{n}{2}\rfloor})$. As a consequence, we have the
+%% following distance evaluation result:
 
-\begin{lemma}
-\label{lem:distnD}
-   Let $\M$ be a chamfer norm whose rational ball $\B$ has $f$
-   $(n-1)-$facets in dimension $n$, then distance computation and thus
-   \textsc{Closest} predicate are in (amortized) $O(n\cdot\log{f})$ with
-   $O\left (\frac{f^{\lfloor \frac{n}{2}\rfloor}}{(\log{ f})^{\lfloor
-       \frac{n}{2}\rfloor-\delta}}\right)$ space and preprocessing
-   time\footnote{$\delta$ is arbitrarily small positive constant.}.
-\end{lemma}
-\begin{proof}
- Similarly to the 2D case, the distance $d_\M(O,a)$ for $a\in\Z^n$ is
- given by first solving a ray-shooting problem on convex polytopes
- which consists in first computing the $(n-1)$-facet of $\B$ pierced by the
- ray $(O,a)$. Once the facet is obtained, the associated $A_k$ row is
- used to evaluate
-   $d_\M(O,a) = A_k\cdot a^T$
-in $O(n)$.  Following \cite{DBLP:journals/dcg/MatousekS93}, such
-ray-shooting requests on convex polytopes can be solved in
-$O(\log{f})$ thanks to a preprocessing in $O\left (\frac{f^{\lfloor
-    \frac{n}{2}\rfloor}}{(\log{ f})^{\lfloor
-    \frac{n}{2}\rfloor-\delta}}\right)$. Please note that this
-preprocessing time is roughly equivalent to the convex hull
-computation in higher dimension which is in $O(f^{\lfloor
-  \frac{n}{2}\rfloor})$. Hence, preprocessing for ray-shooting can be
-done while computing the $\B$ rational ball using
-Eq.~(\ref{eq:4}).$\Box$
-\end{proof}
+%% \begin{lemma}
+%% \label{lem:distnD}
+%%    Let $\M$ be a chamfer norm whose rational ball $\B$ has $f$
+%%    $(n-1)-$facets in dimension $n$, then distance computation and thus
+%%    \textsc{Closest} predicate are in (amortized) $O(n\cdot\log{f})$ with
+%%    $O\left (\frac{f^{\lfloor \frac{n}{2}\rfloor}}{(\log{ f})^{\lfloor
+%%        \frac{n}{2}\rfloor-\delta}}\right)$ space and preprocessing
+%%    time\footnote{$\delta$ is arbitrarily small positive constant.}.
+%% \end{lemma}
+%% \begin{proof}
+%%  Similarly to the 2D case, the distance $d_\M(O,a)$ for $a\in\Z^n$ is
+%%  given by first solving a ray-shooting problem on convex polytopes
+%%  which consists in first computing the $(n-1)$-facet of $\B$ pierced by the
+%%  ray $(O,a)$. Once the facet is obtained, the associated $A_k$ row is
+%%  used to evaluate
+%%    $d_\M(O,a) = A_k\cdot a^T$
+%% in $O(n)$.  Following \cite{DBLP:journals/dcg/MatousekS93}, such
+%% ray-shooting requests on convex polytopes can be solved in
+%% $O(\log{f})$ thanks to a preprocessing in $O\left (\frac{f^{\lfloor
+%%     \frac{n}{2}\rfloor}}{(\log{ f})^{\lfloor
+%%     \frac{n}{2}\rfloor-\delta}}\right)$. Please note that this
+%% preprocessing time is roughly equivalent to the convex hull
+%% computation in higher dimension which is in $O(f^{\lfloor
+%%   \frac{n}{2}\rfloor})$. Hence, preprocessing for ray-shooting can be
+%% done while computing the $\B$ rational ball using
+%% Eq.~(\ref{eq:4}).$\Box$
+%% \end{proof}
 
-From Lemmas~\ref{lem:generic} and~\ref{lem:distnD}, we first have:
-\begin{corollary}
-\label{coro2}
-   Let $\M$ be a chamfer norm whose rational ball $\B$ has $f$
-   $(n-1)-$facets in dimension $n$, separable exact Voronoi Map
-   $\Pi_X$ can be obtained in     $O(n^2\cdot N^n\cdot
-   \log{f}\cdot\log{N})$,
-thanks to a preprocessing in $O\left (\frac{f^{\lfloor
-    \frac{n}{2}\rfloor}}{(\log{ f})^{\lfloor
-    \frac{n}{2}\rfloor-\delta}}\right)$.
-\end{corollary}
+%% From Lemmas~\ref{lem:generic} and~\ref{lem:distnD}, we first have:
+%% \begin{corollary}
+%% \label{coro2}
+%%    Let $\M$ be a chamfer norm whose rational ball $\B$ has $f$
+%%    $(n-1)-$facets in dimension $n$, separable exact Voronoi Map
+%%    $\Pi_X$ can be obtained in     $O(n^2\cdot N^n\cdot
+%%    \log{f}\cdot\log{N})$,
+%% thanks to a preprocessing in $O\left (\frac{f^{\lfloor
+%%     \frac{n}{2}\rfloor}}{(\log{ f})^{\lfloor
+%%     \frac{n}{2}\rfloor-\delta}}\right)$.
+%% \end{corollary}
 
-In higher dimension, we can still expect fast
-\textsc{VoronoiEdgeWedge} function. Let us consider the 3D case
-$n=3$ (and thus $f=O(m)$). In this situation, it turns out that the problem can be turned
-into a simple, 2D one: Given two points $a,b\in\Z^3$ and an isothetic
-line $l$, we need to compute the intersection between the Voronoi
-$2-$facet defined by $a$ and $b$ and $l$. Let us suppose that this the
-intersection point exists and that $a$, $b$ and $l$ are in
-\emph{general position} ($a\not\subset l$, $b\not\subset l$).  Then,
-the intersection point belongs to the two Euclidean planes $P_a$ and
-$P_b$, $P_a$ being respectively the Euclidean plane containing $a$ and
-$l$ (resp. $P_b$ defined by $b$ and $l$), see Fig.\ref{fig:3D}.
+%% In higher dimension, we can still expect fast
+%% \textsc{VoronoiEdgeWedge} function. Let us consider the 3D case
+%% $n=3$ (and thus $f=O(m)$). In this situation, it turns out that the problem can be turned
+%% into a simple, 2D one: Given two points $a,b\in\Z^3$ and an isothetic
+%% line $l$, we need to compute the intersection between the Voronoi
+%% $2-$facet defined by $a$ and $b$ and $l$. Let us suppose that this the
+%% intersection point exists and that $a$, $b$ and $l$ are in
+%% \emph{general position} ($a\not\subset l$, $b\not\subset l$).  Then,
+%% the intersection point belongs to the two Euclidean planes $P_a$ and
+%% $P_b$, $P_a$ being respectively the Euclidean plane containing $a$ and
+%% $l$ (resp. $P_b$ defined by $b$ and $l$), see Fig.\ref{fig:3D}.
 
-To construct a variant of \textsc{VoronoiEdgeWedge} in 3D, we just
-have to replace the line 4 of Algorithm~\ref{alg:chamedgew} by the
-following steps: First, we construct $\vec{v} = (\vec{v}_i +
-\vec{v}_j)/2$. If we suppose that $\vec{v}_i$ and $\vec{v}_j$ belongs
-to $P_a$, $\vec{v}$ also belongs to $P_a$. Then, we perform a 3D
-ray-shooting to get the facet $F$ of $\B$ pierced by vector
-$\vec{v}$. From this facet $F$, we construct the 2D
-$(\vec{v}_{mid},\vec{v}_{mid+1})$ wedge on $P_a$ defined by the
-intersection of $F$ and $P_a$. Once $(\vec{v}_{mid},\vec{v}_{mid+1})$
-is obtained, we proceed with the rest of the \textsc{VoronoiEdgeWedge}
-function (point intersection construction, distance evaluations and
-recursive calls). Please note that the 3D ray shooting can be obtained
-in $O(\log{m})$. Hence, we have:
+%% To construct a variant of \textsc{VoronoiEdgeWedge} in 3D, we just
+%% have to replace the line 4 of Algorithm~\ref{alg:chamedgew} by the
+%% following steps: First, we construct $\vec{v} = (\vec{v}_i +
+%% \vec{v}_j)/2$. If we suppose that $\vec{v}_i$ and $\vec{v}_j$ belongs
+%% to $P_a$, $\vec{v}$ also belongs to $P_a$. Then, we perform a 3D
+%% ray-shooting to get the facet $F$ of $\B$ pierced by vector
+%% $\vec{v}$. From this facet $F$, we construct the 2D
+%% $(\vec{v}_{mid},\vec{v}_{mid+1})$ wedge on $P_a$ defined by the
+%% intersection of $F$ and $P_a$. Once $(\vec{v}_{mid},\vec{v}_{mid+1})$
+%% is obtained, we proceed with the rest of the \textsc{VoronoiEdgeWedge}
+%% function (point intersection construction, distance evaluations and
+%% recursive calls). Please note that the 3D ray shooting can be obtained
+%% in $O(\log{m})$. Hence, we have:
 
-\begin{lemma}
-\label{lem:wedge3D}
-  Let $\M$ be a chamfer norm with $m$ weighted vectors in dimension
-  3. We assume that the $m$ vectors span uniformly the set of
-  directions in $\R^3$, the 3D version of \textsc{VoronoiEdgeWedge} is
-  in
-  \begin{equation}
-    O(\log^2{m})\,.
-  \end{equation}
-\end{lemma}
+%% \begin{lemma}
+%% \label{lem:wedge3D}
+%%   Let $\M$ be a chamfer norm with $m$ weighted vectors in dimension
+%%   3. We assume that the $m$ vectors span uniformly the set of
+%%   directions in $\R^3$, the 3D version of \textsc{VoronoiEdgeWedge} is
+%%   in
+%%   \begin{equation}
+%%     O(\log^2{m})\,.
+%%   \end{equation}
+%% \end{lemma}
 
-\begin{proof}
-  As in dimension 2, each step can be done in $O(\log{m})$
-  computations. Please note that ray-shooting, and intersection
-  computation between a (rational slope) facet $F$ and the (rational)
-  plane $P_a$ can be obtained in $O(1)$.  If we denote by $\M_{P_a}$
-  be the 2D chamfer norm induced by $\B\cap P_a$. The hypothesis that
-  the vectors uniformly span the sphere of directions is here to
-  ensure that if we split $\M_{P_a}$ along the mid direction
-  $\vec{v} =(\vec{v}_i + \vec{v}_j)/2$, both subsets of vectors have the same
-  size. If so, $O(\log{m})$ recursive calls is required. The stop
-  criterion of the recurrence could be that $\vec{v}$ belong to the
-  same facet as both $\vec{v}_i$ and $\vec{v}_j$.$\Box$
-\end{proof}
+%% \begin{proof}
+%%   As in dimension 2, each step can be done in $O(\log{m})$
+%%   computations. Please note that ray-shooting, and intersection
+%%   computation between a (rational slope) facet $F$ and the (rational)
+%%   plane $P_a$ can be obtained in $O(1)$.  If we denote by $\M_{P_a}$
+%%   be the 2D chamfer norm induced by $\B\cap P_a$. The hypothesis that
+%%   the vectors uniformly span the sphere of directions is here to
+%%   ensure that if we split $\M_{P_a}$ along the mid direction
+%%   $\vec{v} =(\vec{v}_i + \vec{v}_j)/2$, both subsets of vectors have the same
+%%   size. If so, $O(\log{m})$ recursive calls is required. The stop
+%%   criterion of the recurrence could be that $\vec{v}$ belong to the
+%%   same facet as both $\vec{v}_i$ and $\vec{v}_j$.$\Box$
+%% \end{proof}
 
-From Lemma~\ref{lem:wedge3D} and proof of Theorem~\ref{them}, we
-conclude with the following result:
+%% From Lemma~\ref{lem:wedge3D} and proof of Theorem~\ref{them}, we
+%% conclude with the following result:
 
-\begin{theorem}
-\label{them2}
-  Let $\M$ be a chamfer norm with $m$ weighted vectors in dimension 3,
-  the Voronoi map $\Pi_X$ and thus the distance transformation of $X$
-  for metric $d_{M}$ can be obtained in
-  \begin{equation}
-    O(\log^2{m}\cdot N^3)\;.
-  \end{equation}
-\end{theorem}
+%% \begin{theorem}
+%% \label{them2}
+%%   Let $\M$ be a chamfer norm with $m$ weighted vectors in dimension 3,
+%%   the Voronoi map $\Pi_X$ and thus the distance transformation of $X$
+%%   for metric $d_{M}$ can be obtained in
+%%   \begin{equation}
+%%     O(\log^2{m}\cdot N^3)\;.
+%%   \end{equation}
+%% \end{theorem}
 
@@
 In this section, we present some implementation details and
-experimental results for chamfer norm DT in dimension 2.
-
-First of all, since release 0.7, most algorithms presented here are
-available in the \textsc{DGtal} library \cite{dgtal}. For $L_p$
-metrics, several \textsc{Closest} and \textsc{HiddenBy} predicates are
-available:
+experimental results for chamfer norm DT in dimension 2.  First of
+all, since release 0.7, most algorithms presented here are available
+in the \textsc{DGtal} library \cite{dgtal}. For $L_p$ metrics, we have
+implemented several \textsc{Closest} and \textsc{HiddenBy} predicates:
 \begin{itemize}
-\item If $p=\{1,2,\infty\}$, exact computations are proposed and all
+\item If $p=\{1,2\}$, exact computations are proposed and all
   predicates are in $O(1)$ with only integer number computations
@@
   \textsc{HiddenBy} predicate in $O(\log N)$
-  (Alg.~\ref{alg:genhidden})\;
+  (Alg.~\ref{alg:genhidden}). Since predicates are based on floating
+  point computations, numerical issues may occur;
 \item if $p\in \Z$, $p\geq 3$, we use exact integer number based
@@
 container sorted counterclockwise to be able to get the mid-vector
-$\vec{v}_{mid}$ in $O(1)$.
+$\vec{v}_{mid}$ in $O(1)$. When implementing Algorithms
+\ref{alg:chamedge} and \ref{alg:chamedgew}, few special cases have to
+be taken into account. For instance, we have to handle situations
+where $a$, $b$ or $c$ belongs to $S$ in Alg.~\ref{alg:chamedge} and
+\ref{alg:chamedgew}. Furthermore, Eq.~(\ref{eq:3}) has a solution iff
+$A_k\neq A_j$. Thanks to the geometrical representation of the
+dichotomic process (Fig.xxxxxxxxx), such special cases are easy to
+handle. Fig. \ref{fig:2Dvoro} illustrates some comparisons on a small
+domain.
+
+\begin{figure}
+  \begin{center}
+    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-voro-chamf_5711}}
+    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-dt-chamf_5711}}
+    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-voro-chamf_5711-2}}
+    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-dt-chamf_5711-2}}\\
+    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-voro-chamf_l_2}}
+    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-dt-chamf_l_2}}
+    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-voro-chamf_l_22}}
+    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-dt-chamf_l_22}}
+  \end{center}
+  \caption{Voronoi map and distance transformation comparison between
+    $\M_{5-7-11}$ and $L_2$: on a $256^2$ domain with $256$ and $2$
+    random seeds, the first row corresponds to $\M_{5-7-11}$ and the second
+    one to $L_2$.}
+  \label{fig:2Dvoro}
+\end{figure}
 

### 2014-02-13 src/statVoronoi.cpp

@@ -41,8 +41,8 @@ void constructPredicate(Predicate &mySet, const unsigned int nbSeeds, const unsi
 
 int main(int argc, char **argv)
 {
-  unsigned int maxN = 500;
-  unsigned int domSize = 2048;
+  unsigned int maxN = 3;
+  unsigned int domSize = 64;
   unsigned int nbSeeds = domSize;
   
   
@@ -68,6 +68,7 @@ int main(int argc, char **argv)
     
     N++;
     
+#define SVG_EXPORT
     
 #ifdef SVG_EXPORT
     Board2D board;
@@ -92,6 +93,8 @@ int main(int argc, char **argv)
     board.saveCairo(title.c_str(), Board2D::CairoPNG );
     trace.info()<<"Exporting CAIRO"<<std::endl;
 
+        
+    
 #endif
     
   }

### 2014-02-13 src/statVoronoil2.cpp

@@ -10,6 +10,7 @@
 #include <DGtal/helpers/StdDefs.h>
 #include <DGtal/geometry/volumes/distance/ChamferNorm2D.h>
 #include <DGtal/geometry/volumes/distance/VoronoiMap.h>
+#include <DGtal/geometry/volumes/distance/DistanceTransformation.h>
 #include <DGtal/arithmetic/IntegerComputer.h>
 #include <stdio.h>
 #include <DGtal/io/boards/Board2D.h>
@@ -42,7 +43,7 @@ void constructPredicate(Predicate &mySet, const unsigned int nbSeeds, const unsi
 int main(int argc, char **argv)
 {
   unsigned int maxN = 500;
-  unsigned int domSize = 2048;
+  unsigned int domSize = 256;
   unsigned int nbSeeds = domSize;
 
 
@@ -56,15 +57,18 @@ int main(int argc, char **argv)
 
 
   typedef VoronoiMap<Z2i::Space, Z2i::DigitalSet, Z2i::L2Metric > VoroChamf;
+  typedef DistanceTransformation<Z2i::Space, Z2i::DigitalSet, Z2i::L2Metric > DT;
+
+  
   VoroChamf voro(&domain, &mySet,&Z2i::l2Metric);
-  double duration = trace.endBlock();
+  DT dt(&domain, &mySet,&Z2i::l2Metric);
+  
+  trace.endBlock();
 
 
-#ifdef SVG_EXPORT
   Board2D board;
   HueShadeColorMap< int> map(0, 256,2);
   board.setUnit ( LibBoard::Board::UCentimeter );
-
   for(VoroChamf::Domain::ConstIterator it=voro.domain().begin(),
         itend=voro.domain().end(); it!= itend;
       ++it)
@@ -83,9 +87,103 @@ int main(int argc, char **argv)
   board.saveCairo(title.c_str(), Board2D::CairoPNG );
   trace.info()<<"Exporting CAIRO"<<std::endl;
 
-#endif
+  
+  double maxv=0;
+  for(DT::Domain::ConstIterator it=dt.domain().begin(),
+      itend=dt.domain().end(); it!= itend;
+      ++it)
+    if (dt(*it)>maxv) maxv=dt(*it);
+  
+  board.clear();
+  HueShadeColorMap< double> map2(0, maxv,2);
+  for(DT::Domain::ConstIterator it=dt.domain().begin(),
[…]

### 2014-02-18 latex/dgci2014/article.tex
ok

@@
 \documentclass{llncs}
+\usepackage{multirow}
 \usepackage{amsmath,amssymb}
@@
 
-\title{Generic Separable Algorithms for Distance Transformation: A
-  Subquadratic Approach for Path Based Norms\thanks{This work has been
-    mainly funded by ANR-11-BS02-009 and ANR-11-IDEX-0007-02
-    PALSE/2013/21 research grants.}}
+\title{2D Subquadratic Separable Distance Transformation for
+  Path-Based Norms\thanks{This work has been mainly funded by
+    ANR-11-BS02-009 and ANR-11-IDEX-0007-02 PALSE/2013/21 research
+    grants.}}
+
+%% \title{Generic Separable Algorithms for Distance Transformation: A
+%%   Subquadratic Approach for Path Based Norms\thanks{This work has been
+%%     mainly funded by ANR-11-BS02-009 and ANR-11-IDEX-0007-02
+%%     PALSE/2013/21 research grants.}}
 
@@
 volumetric transformations in dimension 2. More precisely, we describe
-a $O(\log^2{m}\cdot N^2)$ algorithm in dimension 2 for shapes in
-$N\times N$ domain with chamfer norm with size $m$.
+a $O(\log^2{m}\cdot N^2)$ algorithm in dimension 2 for shapes in a
+$N\times N$ domain with chamfer norm of size $m$.
 
-\keywords{Digital Geometry, Distance Transformation, Chamfer Norms}
+\keywords{Digital Geometry, Distance Transformation, Path-based Norms}
 \end{abstract}
@@
 $X\subset \Z^n$, the distance transformation labels each point in $X$
-with the distance to the closest point in $\Z^n \setminus X$. Since
-such characterization is parametrized by a distance function, many
-works have been done to address this distance transformation problem
-with a trade-off between algorithmic performances and the
-\emph{accuracy} of the digital distance function with respect to the
-Euclidean one.  Hence, authors have considered distances based on
-chamfer masks
-\cite{Rosenfeld1968,borgefors,Thiel_IWCIA7,fouard:ivc:2005} or
-sequences of chamfer masks
-\cite{ROSEN_66,mukherjee,Nagy05,Strand2008,DBLP:conf/dgci/NormandSE13};
+with the distance to its closest point in $\Z^n \setminus X$ (labeling
+each point by the closest background point leads to Voronoi maps, see
+below). Since such characterization is parametrized by a distance
+function, many works have been done to address this distance
+transformation problem with a trade-off between algorithmic
+performances and the \emph{accuracy} of the digital distance function
+with respect to the Euclidean one.  Hence, authors have considered
+distances based on chamfer masks
+\cite{Rosenfeld1968,borgefors,fouard:ivc:2005} or sequences of chamfer
+masks \cite{ROSEN_66,mukherjee,Strand2008,DBLP:conf/dgci/NormandSE13};
 the vector displacement based Euclidean distance
-\cite{danielson,ragnemalm,MULL_92,Cuisenaire1999_268}; the Voronoi
-diagram based Euclidean distance
-\cite{BreuEtAl95,maurer_pami} or the square of the
-Euclidean distance \cite{SaitTori:94,Hirata,roerdnik}.
+\cite{danielson,ragnemalm}; the Voronoi diagram based Euclidean
+distance \cite{BreuEtAl95,maurer_pami} or the square of the Euclidean
+distance \cite{Hirata,roerdnik}.  For Euclidean or $L_p$ metrics,
+separable volumetric computations have demonstrated to be very
+efficient: optimal $O(n\cdot N^n)$ time algorithms for shapes in $N^n$
+domains, optimal multi-thread/GPU implementation\ldots (please refer
+to \cite{dcoeurjo_ChapDTWADGMM} for a discussion). For path-based
+metrics (chamfer mask, -weighted- neighborhood sequences,\ldots), two
+main techniques exist to compute the distance transformation. The
+first one considers a weighted graph formulation of the problem, and
+shortest path in graphs using Dijkstra-like algorithm can be
+considered. If $m$ denotes the size of the chamfer mask, computational
+cost could be in $O(m\cdot N^n)$ using a cyclic bucket data structure
+\cite{verwer_uniform}. Another approach consists in a raster scan of
+the domain: first the chamfer mask is decomposed into two disjoint
+sub-masks. Then the domain grid points are scanned in a given order
+(consistent with the sub-masks construction) and a local minimum
+computation is performed and then propagated
+\cite{ROSEN_66,borgefors}. Scanning the domain twice for each
+sub-masks leads to the distance transformation. Again, we end up with
+a $O(m\cdot N^n)$ computational cost. This complexity is said to be
+quadratic in $m$ and $N$ since for arbitrary large image $N$, even if
+$m \ll N$, $m$ has to be in $O(N^n)$ to have accurate asymptotic DT.
+Please note that Dijkstra's graph approach allows us to defined
+constrained distance transformation (\emph{i.e.} geodesic metric),
+both separable approaches and raster-scan for path-based metrics are
+only dedicated to compact convex domains (usually hyper-rectangular)
+distance transformation.
 
-\paragraph{Contributions} In this article,
-
-\begin{table}
-  \caption{Complexity summary.}
-  \label{tab:final}
+\textbf{Contributions} In this article, we first describe the generic
+framework for separable distance transformation and conditions on the
+metric to be consistent with this model. Then, we describe
+subquadratic algorithms in dimension 2 to compute error-free distance
+transformation and Voronoi map for chamfer norms and other path-based
+metrics. Overall computational costs can be summarized as follows:
+%\begin{table}
+%  \caption{Computational cost summary for separable Voronoi map
+%    computation on $N^n$ domains ($m$ being the size of the chamfer
+%    norm and $f$ the number of row in a H-representation, see below).}
+ % \label{tab:final}
   \begin{center}
@@
       $O(\log{p}\cdot\log{N})$ & $O(n\cdot
-      N^n\cdot\log{p}\cdot\log{N})$& here and  \cite{dgtal}\\
+      N^n\cdot\log{p}\cdot\log{N})$& Lem.~\ref{lem:generic},  \cite{dgtal}\\
       $L_p$  (inexact pred.) & $O(1)$ &
       $O(\log{N})$ & $O(n\cdot
-      N^n\cdot\log{N})$& here and  \cite{dgtal}\\
+      N^n\cdot\log{N})$& Lem.~\ref{lem:generic},  \cite{dgtal}\\
       2D Chamfer norm &  $O(\log{m})$ &$O(\log^2{m})$
@@
   %    & $O(n^2\cdot N^n\cdot \log{f}\cdot\log{N})$& Corollary \ref{coro2}\\
-      2D Neig. sequence norm  & $O(\log{f})$&
+      2D Neig. seq. norm  & $O(\log{f})$&
       $O(\log^2{f})$& $O(\log^2{}f\cdot N^2)$& Th.~\ref{them} and  \cite{DBLP:conf/dgci/NormandSE13}\\
@@
   \end{center}
-\end{table}
+%\end{table}
 
@@
 \label{sec:preliminaries}
-Let us first define some elementary concepts and objects.
-\begin{definition}[Metrics and Metric Space]
-  \label{def:distance}
-  A metric is a map $d$ from $E$ to a sub-group $F$ of $\R$ such that
-  $\forall a,b,c\in E$,
-  \begin{align}
-    (\text{non-negative})\quad & d(a,b)\geq 0\\
-    (\text{identity of indiscernibles}) \quad&  d(a,b)= 0
-    \Leftrightarrow a=b\\
-    (\text{symmetry})\quad &  d(a,b)=d(b,a)\\
-    (\text{triangular inequality})\quad &   d(a,c) \leq d(a,b) + d(b,c)
-  \end{align}
-$(E, F, d)$ is called a metric space.
-\end{definition}
-If property $(4)$ is omitted, we are defining a distance function
-instead of a metric. Note that in the following, we will only consider
-metric spaces with properties $(1-4)$. Furthermore, we
-consider  metrics induced by a vector space norm:
+%% Let us first define some elementary concepts and objects.
+%% \begin{definition}[Metrics and Metric Space]
+%%   \label{def:distance}
+%%   A metric is a map $d$ from $E$ to a sub-group $F$ of $\R$ such that
+%%   $\forall a,b,c\in E$,
+%%   \begin{align}
+%%     (\text{non-negative})\quad & d(a,b)\geq 0\\
+%%     (\text{identity of indiscernibles}) \quad&  d(a,b)= 0
+%%     \Leftrightarrow a=b\\
+%%     (\text{symmetry})\quad &  d(a,b)=d(b,a)\\
+%%     (\text{triangular inequality})\quad &   d(a,c) \leq d(a,b) + d(b,c)
+%%   \end{align}
+%% $(E, F, d)$ is called a metric space.
+%% \end{definition}
+%% If property $(4)$ is omitted, we are defining a distance function
+%% instead of a metric.
 \begin{definition}[Norm and metric induced by a norm]
-  \label{def:distance}
+  \label{def:norm}
   Given a vector space EV, a norm is a map $g$ from  $EV$ to a sub-group
@@
     (\text{homogeneity})\quad &  \forall \lambda\in\R, \quad
-    g(\lambda\cdot\vec{x}) = |\lambda|\cdot g(\lambda\cdot\vec{x})
+    g(\lambda\cdot\vec{x}) = |\lambda|\cdot g(\cdot\vec{x})
   \end{align}
 $d(a,b) \EqDef g(b-a)$ is the metric induced by the
-  norm $g$.
+  norm $g$.  $(E, F, d)$ is called a  metric space if $d:~E\rightarrow
+  F$.
 \end{definition}
@@
 \emph{modules} on a commutative ring ($\Z^n$ being a module on $\Z$
-but not a vector space) \cite{Thiel_hdr}.
-From the literature, path-based approaches (Chamfer masks, -weighted-
-neighborhood sequences...)  aim at defining metrics induced by norms
-in metric spaces $(\Z^n, \Z , d)$.  Note that (weighed, with $w_i\geq 0$) $L_p$ norms inducing
-metrics
+but not a vector space) \cite{Thiel_hdr}. Path-based approaches
+(chamfer masks, -weighted- neighborhood sequences...)  aim at defining
+metrics induced by norms in metric spaces $(\Z^n, \Z , d)$.  Note that
+(weighed, with $w_i\geq 0$) $L_p$ metrics
 \begin{equation}
-    d_{L_p} (a,b) = \left ( \sum_{i=0}^n w_i|a_i-b_i |^p \right )^{\frac{1}{p}}\;,
+    d_{L_p} (a,b) = \left ( \sum_{k=1}^n w_k|a_k-b_k |^p \right )^{\frac{1}{p}}\;,
   \end{equation}
-characterize metric spaces $(\Z^n, \R , d_{L_p})$. However,
-rounding the distance function $(\Z^n,\Z, \lceil d_{L_p}\rceil)$ implies a
-metric space \cite{klette_book}.
+characterize metric spaces $(\Z^n, \R , d_{L_p})$. Rounding the \sloppy
+distance function $(\Z^n,\Z, \lceil d_{L_p}\rceil)$ is a metric
+space \cite{klette_book}.
 
@@
   The distance transform $DT_X$ associated with a digital metric space
-  $(\Z^n,\Z,d)$ is a map  $X\rightarrow\Z$ such that
-  \begin{equation}
-    DT_X(a) = \min_{b\in \Z^n\setminus X} \{d(a,b)\}\;.
-  \end{equation}
+  $(\Z^n,\Z,d)$ is a map  $X\rightarrow\Z$ such that, for $a\in X$
+  $    DT_X(a) = \min_{b\in \Z^n\setminus X} \{d(a,b)\}$.
 The Voronoi map is the map $X\rightarrow\Z^n$:
-  \begin{equation}
-    \Pi_X(a) = \argmin_{b\in \Z^n\setminus X} \{d(a,b)\}\;.
-  \end{equation}
+$    \Pi_X(a) = \argmin_{b\in \Z^n\setminus X} \{d(a,b)\}$.
 \end{definition}
@@
 or more points in $\Z^n\setminus X$ but only one is considered in
-$\Pi_X(a)$ (please refer to\cite{Couprie2007} for complete digital
-Voronoi map construction).
-
+$\Pi_X(a)$ this choice has no influence on $DT_X$.
+% (please refer to \cite{Couprie2007} for complete digital
+%Voronoi map).
 \begin{definition}[Chamfer Mask]
@@
 \end{definition}
-
-In the literature
-\cite{borgefors,Thiel_hdr,Strand2008,normandHDR,fouard:ivc:2005} many
-authors have proposed algorithmic and/or analytic approaches to
-construct Chamfer masks approximating the Euclidean metric and being
-induced by norm. In the following, we focus on such \emph{chamfer
+Many authors have proposed algorithmic and/or analytic approaches to
+construct chamfer masks approximating the Euclidean metric and being
+induced by a norm. In the following, we focus on such \emph{chamfer
   norms}.  To evaluate distances between two digital points for a
@@
 \label{eq:4}
-    \B = conv\left\{ \frac{\vec{v}_i}{w_i};\; (\vec{v}_i,w_i)\in\M \right \}\,.
+    \B = conv\left\{ \frac{\vec{v}_k}{w_k};\; (\vec{v}_k,w_k)\in\M \right \}\,.
   \end{equation}
 Rational ball $\B$ can also be described in a H-representation of
-polytope with minimal parameter \cite{DBLP:conf/dgci/NormandSE13}:
-\begin{equation}
-  P = \{ x\in\Z^n; Ax \leq y\;\}\quad \text{ such that }  \forall
-  i\in[1\ldots f], \exists x\in P\quad A_ix=y_i\,.\footnote{$A_i$
-    being the $i^{th}$ row of $A$.}
-\end{equation}
-$f$ being the number of row in $A$ and the number of facets in $\B$,   and is thus related to $|\M|$.
+polytope with minimal parameter \cite{DBLP:conf/dgci/NormandSE13}: $ P
+= \{ x\in\Z^n; Ax \leq y\;\}$ such that $\forall k\in[1\ldots f],
+~\exists x\in P\quad A_kx=y_k.\footnote{$A_k$ being the $k^{th}$ row
+  of $A$.}$ $f$ being the number of row in $A$ and the number of
+facets in $\B$, and is thus related to $|\M|$.
 \end{definition}
@@
 \begin{proposition}[Direct Distance Computation \cite{DBLP:journals/pr/NormandE09}]
-  Given a chamfer mask $\M$ inducing a norm and $(A,y)$ its minimal
+  Given a chamfer mask $\M$ induced by a  norm and $(A,y)$ its minimal
   parameter H-representation, then for any $a\in\Z^n$, the chamfer
@@
     \label{eq:1}
-    d_\M(O,a) =  \max_{1\leq i \leq l} \{ A_i a^T\}\,.
+    d_\M(O,a) =  \max_{1\leq k \leq f} \{ A_k a^T\}\,.
   \end{equation}
 \end{proposition}
-
 Among path-based digital metric, we can also introduce (weighted)
 neighborhood sequences
-\cite{ROSEN_66,mukherjee,Nagy05,Strand2008,DBLP:conf/dgci/NormandSE13}
+\cite{ROSEN_66,mukherjee,Strand2008,DBLP:conf/dgci/NormandSE13}
 whose objective is to have better approximation of the Euclidean
 metric from sequences of elementary chamfer masks.  A key result have
-been demonstrated in \cite{DBLP:journals/pr/NormandE09} stating
-that for such distance functions, a minimal parameter polytope
-representation exists and that distances can be from similar
+been demonstrated in \cite{DBLP:conf/dgci/NormandSE13} stating that
+for such distance functions, a minimal parameter polytope
+representation exists and that distances can be obtained from similar
 expression to (\ref{eq:1}):
 \begin{equation}
-  d(O,a)  =\max_{1\leq i \leq l} \{ f_i(A_i a^T)\}\,,
+  d(O,a)  =\max_{1\leq k \leq f} \{ f_k(A_k a^T)\}\,,
 \end{equation}
-($f_i$ being and integer sequence characterizing the neighborhood
-sequence metric).
-
- In the following and for the sake of simplicity, we describe our
- algorithms focusing to chamfer norms but similar results can be
- obtained for more generic path-based metric such neighborhood
- sequences.
+$f_k$ being some integer sequence characterizing the neighborhood
+sequence metric. In the following and for the sake of simplicity, we
+describe our algorithms focusing on chamfer norms but similar results
+can be obtained for more generic path-based metric such as
+neighborhood sequences.
 \section{Separable Distance Transformation}
@@
 \label{sec:voronoi-map-from}
-In \cite{Hirata1996,SaitTori:94,Breu1995,Meijster2000,Maurer2003},
+In \cite{Hirata1996,Breu1995,Meijster2000,Maurer2003},
 several authors have described optimal in time and separable
@@
 transformations for $L_2$ and $L_p$ metrics. Separability means that
-computations are performed dimension by dimension, allowing fast
-computations and multithread implementations (see
-\cite{dcoeurjo_ChapDT} for an overview).  In the following, we
-consider Voronoi map approach as defined in \cite{Breu1995} (see
-Fig.~\ref{fig:2Dbreu}): Let us first define hyper-rectangular domain
-$I_X: [0..N_1]\times\ldots[0..N_n] \rightarrow \{0,1\}$ such that
-$X\subset I_X$ and $I_X(a)= 1$ for $a\in [0..N_1]\times\ldots[0..N_n]$
-iff $a\in X$ ($I_X(a)=0$ otherwise). As illustrated in
-Fig.~\ref{fig:2Dbreu} in dimension 2, we first process each row of the
-input image to create independent 1D Voronoi maps along the first
-dimension for the metric. Then, for each further dimension, the
+computations are performed dimension by dimension
+%, allowing fast
+%computations and multithread implementations (see
+%\cite{dcoeurjo_ChapDT} for an overview).
+In the following, we
+consider Voronoi map approach as defined in \cite{Breu1995}: Let us
+first define hyper-rectangular image $I_X:
+[1..N_1]\times\ldots\times[1..N_n] \rightarrow \{0,1\}$ such that $X\subset
+I_X$ and $I_X(a)= 1$ for $a\in [1..N_1]\times\ldots\times[1..N_n]$ iff $a\in
+X$ ($I_X(a)=0$ otherwise). In dimension 2, we first process each row
+of the input image to create independent 1D Voronoi maps along the
+first dimension for the metric. Then, for each further dimension, the
 partial Voronoi map $\Pi_X$ is updated using one dimensional
-independent processes on image spans along the $i^{th}$
-dimension.
-
+independent processes on image spans along the $i^{th}$ dimension.
 %% \begin{figure}
@@
 %% \end{figure}
-
-Algorithm \ref{alg:voro} describe the 1D processes to perform on each
-row, columns and higher dimension spans. In this process, metric
-information are embedded in the following two predicates (see Fig.~\ref{fig:predicates}):
-\textsc{Closest}$(a, b, c)$: given three points $a,b,c\in\Z^n$ this
-predicate returns true if $d(a,b) < d(a,c)$. \textsc{HiddenBy}$(a, b,
-c, S)$: given three points $a,b,c\in\Z^n$ such that $a_i<b_i<c_i$ and
-a 1D image span $S^i$, this predicates returns true if there is no
-$s\in S$ such that
+Algorithm \ref{alg:voro} describes the 1D processes to perform on each
+row, column and higher dimensional image span\footnote{An image span
+  $S$ along the $i^{th}$ direction is a vector of $N_i$ points with
+  same coordinates except at $i$.} In this process, metric information
+are embedded in the following two predicates (see
+Fig.~\ref{fig:predicates}): \textsc{Closest}$(a, b, c)$, given three
+points $a,b,c\in\Z^n$ this predicate returns true if $d(a,b) <
+d(a,c)$. \textsc{HiddenBy}$(a, b, c, S)$, given three points
+$a,b,c\in\Z^n$ such that $a_i<b_i<c_i$ and a 1D image span
+$S$\footnote{Subscript $a_i$ denotes the $i^{th}$ coordinate of point
+  $a\in\Z^n$.}, this
+predicates returns true if there is no $s\in S$ such that
     \begin{equation}
@@
   \KwData{Input binary map $I_X$ if $i=1$ or  partial Voronoi map $\Pi_X$ obtained for
-    dimension $1<j<i$, and a 1D segment $S$ with points
-    $\{s_1,\ldots,s_{N_i}\}$ sorted by their $i^{th}$ coordinate.}
+    dimensions lower than $i$, and a 1D span $S$ with points
+    $\{s^1,\ldots,s^{N_i}\}$ sorted by their $i^{th}$ coordinate.}
   \KwResult{Updated partial Voronoi map $\Pi_X$ along $S$.}
@@
 { $k=0$\;
-\ForEach{point $s_i$ in $S$}{
-    \If{$I_X(s_i) = 1$}
+\ForEach{point $s$ in $S$}{
+    \If{$I_X(s) = 1$}
      {
-       $L_S[k] = s_i$\;
+       $L_S[k] = s$\;
        $k++$\;
@@
 \Else{
- ${L}_S[0]=\Pi_X(s_1)$\;
-  ${L}_S[1]=\Pi_X(s_2)$\;
+ ${L}_S[0]=\Pi_X(s^1)$\;
+  ${L}_S[1]=\Pi_X(s^2)$\;
   $k=2$ , $l=3$\;
   \While{$l\leq N_i$}{
-    $w = \Pi_X(s_l)$\;
+    $w = \Pi_X(s^l)$\;
     \While{$k\geq 2$ and \textsc{HiddenBy}(${L}_S[k-1],{L}_S[k],w, S$)}
@@
         }
-        $k++$ , $l++$\;
+        $k++$ ; $l++$\;
         ${L}_S[k]=w$\;
@@
   {
-    \While{($k < |L_S|$) and not(\textsc{Closest}($s$, $L_S[k]$, $L_S[k+1]$))}
+    \While{($k < |L_S|$) and not(\textsc{Closest}($s^i$, $L_S[k]$, $L_S[k+1]$))}
           {
@@
 
-  \caption{Voronoi map pruning along 1D segment $S$ along the $i^{th}$
-    dimension.\label{alg:voro}}
+  \caption{Voronoi map construction on 1D image span $S$ along the
+    $i^{th}$ dimension.\label{alg:voro}}
 \end{algorithm}
@@
   \end{center}
-  \caption{xxxxxxxxxxx}
+  \caption{\small Geometrical predicates for Voronoi map construction:
+    \textsc{HiddenBy}($a,b,c,S)$ returns false in $(a)$ and true in
+    $(b)$ (straight segments correspond to Voronoi diagram
+    edges). $(c)$ illustrates the \textsc{Closest}($a,b,c$) predicate
+    for $c\in S$.}
   \label{fig:predicates}
@@
 Voronoi cell of sites $a$ and $c$ \emph{hide} the Voronoi cell of $b$
-along $S$ (\emph{e.g.} $A$ and $E$ \emph{hide} $C$ and $B$ on $S$ in
-Fig.~\ref{fig:predicates}).  For $L_1$, $L_2$ and $L_\infty$ metrics,
+along $S$.  For $L_1$, $L_2$ and $L_\infty$ metrics,
 \textsc{Closest} and \textsc{HiddenBy} predicates can be computed in
@@
 computational time for the Voronoi map and distance transformation
-problem in $O(n\cdot N^n)$ (if we assume that $\forall i\in[1\ldots
+problem in $\Theta(n\cdot N^n)$ (if we assume that $\forall i\in[1\ldots
   n], N_i=N$).
@@
 related to \emph{quadrangle inequality} in \cite{Hirata1996}).  To sum
-up these contributions, we use the following proposition:
+up these contributions, we have the following proposition:
 \begin{proposition}[Metric conditions \cite{Hirata1996}]
 \label{prop:voronoi-map-from-1}
-  Let $d$ be a metric induced by a norm whose unit ball is symmetric
-  with respect to grid axis. If distance comparison predicate
-  $d(a,b)<d(c,d)$ is exact (for $a,b,c,d\in\Z^n$), Algorithm 1 is
-  correct and returns a Voronoi map $\Pi_X$.
+  Let $d$ be a metric induced by a \textbf{norm whose unit ball is
+    symmetric with respect to grid axes} and if distance comparison
+  predicate is exact, Algorithm 1 is correct and returns a Voronoi map
+  $\Pi_X$.
 \end{proposition}
-
-For example, Algorithm \ref{alg:voro} provides exact Voronoi map
-computation for $L_p$ norms. In such case, distance comparison
-predicate can be implemented error-free form integer number comparison
-considering the $p$ power of the distance function $\left
-(d_{L_p}\right)^p$.  Proposition \ref{prop:voronoi-map-from-1} also
-implies that Chamfer norms, neighborhood sequences based norms can
-also be considered in separable Algorithm \ref{alg:voro}. We just need
-algorithmic tools to implement efficiently both \textsc{Closest} and
+When implementing Algorithm 1, we say that the distance comparison
+predicate is exact if we can compare two distances, \emph{e.g.}
+\textsc{Closest} predicate, without error. Hence, Algorithm \ref{alg:voro}
+provides exact Voronoi map computation for $L_p$ norms. In this case,
+distance comparison predicate can be implemented error-free from
+integer number comparison considering the $p$ power of the distance
+function $\left (d_{L_p}\right)^p$.  Proposition
+\ref{prop:voronoi-map-from-1} also implies that most chamfer norms and
+neighborhood sequences based norms can also be considered in separable
+Algorithm \ref{alg:voro} (see Fig.~\ref{fig:metrics}). We just need
+algorithmic tools to efficiently implement both \textsc{Closest} and
 \textsc{HiddenBy} predicates.
-
-\begin{figure}
+\begin{figure}[htbp]
  {\includegraphics[width=1.65cm]{image-ball-1}}
- {\includegraphics[width=1.65cm]{image-ball-1_3999999999999999.png}}
+ {\includegraphics[width=1.65cm]{image-ball-1-4}}
  {\includegraphics[width=1.65cm]{image-ball-2}}
  {\includegraphics[width=1.65cm]{image-ball-4}}
- {\includegraphics[width=1.65cm]{image-ball-43_100000000000001.png}}
+ {\includegraphics[width=1.65cm]{image-ball-43-1}}
  {\includegraphics[width=1.65cm]{image-ball-chamf34}}
@@
   \caption{Balls for different metrics satisfying Proposition \ref{prop:voronoi-map-from-1}: \emph{(from
-      left to right)} $L_1$, $L_{1.4}$, $L_2$, $L_4$, $L_{43.0}$,
+      left to right)} $L_1$, $L_{1.4}$, $L_2$, $L_4$, $L_{43.1}$,
     $\M_{3-4}$ and $\M_{5-7-11}$.}
@@
 \end{figure}
-
+%
+\vspace{-1cm}
 \subsection{A First Generic Adapter}
 \label{sec:first-gener-adapt}
-
-Let suppose that $(\Z^n,F,d)$ is a metric space induced by a norm. We
-can first detail the overall computational cost of Algorithm
+We first detail the overall computational cost of Algorithm
 \ref{alg:voro}:
@@
 \label{lem:generic}
-   Let $(\Z^n, F, d)$ be a metric space induced by a norm. If $C$
-  denotes the computational cost of \textsc{Closest} predicate and $H$
-  is the computational cost of the \textsc{HiddenBy} predicate, then
-  Algorithm \ref{alg:voro} is in   $O(n\cdot N^n\cdot (C+H))$.
+Let $(\Z^n, F, d)$ be a metric space induced by a norm with axis
+symmetric unit ball. If $C$ denotes the computational cost of
+\textsc{Closest} predicate and $H$ is the computational cost of the
+\textsc{HiddenBy} predicate, then Algorithm \ref{alg:voro} is in
+$O(n\cdot N^n\cdot (C+H))$.
 \end{lemma}
-A first improvement is given by Algorithms~\ref{alg:genclosest},
-\ref{alg:genedge} and \ref{alg:genhidden}: we only require the metric
-to be known and \textsc{HiddenBy} predicate is obtained by a binary
-search on the 1D image span $S$ to localize the abscissa of Voronoi
-edges of sites $(a,b)$ and $(b,c)$ (see Fig.XXXXXX). Please note that
-from \cite{Breu1995,roerdnik}, $C=H=O(1)$ for $L_1,L_2$ and $L_\infty$
-norms.
+From \cite{Breu1995,roerdnik}, $C=H=O(1)$ for $L_1,L_2$ and $L_\infty$
+norms.  For prescribed norm $d$, we first define generic
+Algorithms~\ref{alg:genclosest}, \ref{alg:genedge} and
+\ref{alg:genhidden}: from some evaluations of $d$, \textsc{HiddenBy}
+predicate is obtained by a dichotomic search on the 1D image span $S$
+to localize the abscissa of Voronoi edges of sites $\{a,b\}$ and
+$\{b,c\}$ (see Fig.~\ref{fig:algo}).
 
@@
   \Return $d(a,b) < d(a,c)$\;
-  \caption{Generic \textsc{Closest}($a,b,c\in\Z^n$).\label{alg:genclosest}}
+  \caption{\footnotesize Generic \textsc{Closest}($a,b,c\in\Z^n$).\label{alg:genclosest}}
 \end{algorithm}
@@
      {
-       \Return  i
+       \If{$i=1$ and \textsc{Closest}$(s^{i},b,a)$ }{\Return $-\infty$\;}
+       \If{$i=N_i$ and \textsc{Closest}$(s^{i},a,b)$ }{\Return $\infty$\;}
+       \Return  i\;
      }
      $mid  = i + (j-i)/2$\;
-     \eIf{\textsc{Closest}$(s_{mid},a,b)$}
+     \eIf{\textsc{Closest}$(s^{mid},a,b)$}
        {
          \tcp{$s_{mid}$ closer to $a$}
-         \Return \textsc{VoronoiEdge}($a,b,s_{mid},s_j$)
+         \Return \textsc{VoronoiEdge}($a,b,s^{mid},s^j$)
 }
@@
          \tcp{$s_{mid}$ closer to $b$}
-         \Return \textsc{VoronoiEdge}($a,b,s_{i},s_{mid}$)
+         \Return \textsc{VoronoiEdge}($a,b,s^{i},s^{mid}$)
 }
 
-  \caption{Generic \textsc{VoronoiEdge}($a,b,s_i,s_j\in\Z^n$).\label{alg:genedge}}
+  \caption{\footnotesize Generic \textsc{VoronoiEdge}($a,b,s^i,s^j\in\Z^n$), $a_i<b_i$.\label{alg:genedge}}
 \end{algorithm}
@@
 \begin{algorithm}[H]\footnotesize
-  $v_{ab}$ = \textsc{VoronoiEdge}$(a,b,s_1, s_{N_i})$\;
-  $v_{bc}$ = \textsc{VoronoiEdge}$(b,c,s_1, s_{N_i})$\;
+  $v_{ab}$ = \textsc{VoronoiEdge}$(a,b,s^1, s^{N_i})$\;
+  $v_{bc}$ = \textsc{VoronoiEdge}$(b,c,s^1, s^{N_i})$\;
   \Return $(v_{ab}> v_{bc})$\;
-  \caption{Generic \textsc{HiddenBy}($a,b,c\in\Z^n; S$ in the $i^{th}$
-    direction).\label{alg:genhidden}}
+  \caption{\footnotesize Generic \textsc{HiddenBy}($a,b,c\in\Z^n; S$ in the $i^{th}$
+    direction) $a_i<b_i<c_i$.\label{alg:genhidden}}
 \end{algorithm}
-
-Hence, we obtain a first generic adapter to transform any metric
-induced by a norm into separable predicates:
-
 \begin{lemma}
-\label{lem:generic}
-   Let $(\Z^n, F, d)$ be a metric space induced by a norm. If $C$
-   denotes the computational cost of \textsc{Closest} predicate
-   Algorithm \ref{alg:voro},  with predicates from Algorithms
-   \ref{alg:genclosest} and \ref{alg:genhidden}, is in $O(n\cdot N^n\cdot C\cdot \log{N}))$.
+\label{lem:genericDich}
+   Let $(\Z^n, F, d)$ be a metric space induced by a norm with axis
+   symmetric unit ball,   from Algorithms \ref{alg:genclosest} and
+   \ref{alg:genhidden}, we have $H=O(C\cdot \log{N})$.
 \end{lemma}
-
+\begin{proof}
+  First, the generic \textsc{VoronoiEdge} is dichotomic in
+  $O(\log{N})$ steps and $O(C)$ for each one. \textsc{VoronoiEdge} is
+  in $O(C\cdot\log{N})$.  To prove the correctness of
+  \textsc{VoronoiEdge} (and thus Alg.~\ref{alg:voro}), we use the
+  convexity of the metric and the quadrangle property: since
+  $a_i<b_i$, all grid points closer to $a$ than $b$ in $S$ (if exist)
+  are \emph{lower} than all pixels on $S$ closer to $b$ than to $a$
+  (if exist too). Thanks to test in line $4$, recursive call maintain
+  this invariant. Note that tests $2-5$ handle the fact that the edge
+  may not belong to $S$.$\Box$
+\end{proof}
 If we consider a chamfer norm with $f$ facet rational ball, Eq.~(\ref{eq:1})
-suggests that $C=O(f)$. Hence, we have the following corollary
+suggests that $C=O(f)$. Hence, we have the following corollary:
 \begin{corollary}
@@
 \end{corollary}
-
 Please remember that naive implementation of chamfer mask distance
 transformation using raster scan approach would lead to a $O(f\cdot
-N^d)$ computational cost. In the following sections, we use the convex
+N^n)$ computational cost. In the following sections, we use the convex
 structure of $\B$ to design a first subquadratic algorithm for chamfer
@@
 Let us consider a 2D chamfer norm $\M$ with $m$ weighted vectors (note
-that $l\EqDef|\B| = m$ in 2D). We suppose that vectors
-$\{v_k\}_{k=1\ldots m}$ are sorted counterclockwise. We define a wedge
-as a pair $(\vec{v_k},\vec{v_{k+1}})$ of vectors. To each wedge is
+that $f\EqDef|\B| = m$ in 2D). We suppose that vectors
+$\{\vec{v}^k\}_{k=1\ldots m}$ are sorted counterclockwise. We define a wedge
+as a pair $(\vec{v}^k,\vec{v}^{k+1})$ of vectors. To each wedge is
 associated a row $A_k$ in the minimal H-representation of $A$ ($A_k$
-can also be seen as a non-unit normal vectors to $\B$ facets
+can also be seen as a  --non-unitary-- normal vectors to $\B$ facets
 \cite{DBLP:journals/pr/NormandE09}). Using similar notations,
@@
 of point $a$ can be obtained in two steps: First, we compute the wedge
-$(\vec{v_k},\vec{v_{k+1}})$, $a$ belongs to. Then,
+$(\vec{v}^k,\vec{v}^{k+1})$, $a$ belongs to. Then,
 \begin{equation}
@@
   Since vectors are sorted counter-clockwise,
-  $(\vec{v_k},\vec{v_{k+1}})$ wedge can be obtained by a dichotomic
+  $(\vec{v}^k,\vec{v}^{k+1})$ wedge can be obtained by a dichotomic
   search with $O(\log{m})$ steps. At each step, we compute the local
@@
 ($a_i<b_i$) and a 1D image span $S$ along the $i^{th}$ dimension, we
-can to find the lowest abscissa $e_i$ of the point $e$ on $S$ such
+have to find the lowest abscissa $e_i$ of the point $e$ on $S$ such
 that $d(a,e) < d(b,e)$ and $d(a,e')\geq d(b, e')$ for any $e'$ with
 $e'_i>e_i$.
-
-Let us first suppose that we don't have $e$ but we know the wedges
-$(v_{k},v_{k+1})$ (resp. $(v_j,v_{j+1})$) such that the vector
-$(e-a)^T$ (resp. $(e-b)^T$) should belong to (see Fig.~\ref{fig:algo}). In this
-situation, we know that $e$ is the solution of
+Let us first suppose that we don't have $e$ but we know the two wedges
+$(\vec{v}^{k},\vec{v}^{k+1})$ (resp. $(\vec{v}^j,\vec{v}^{j+1})$) such
+that the vector $(e-a)^T$ (resp. $(e-b)^T$) belongs to (see
+Fig.~\ref{fig:algo}). In this situation, we know that $e$ is the
+solution of
 \begin{equation}
@@
 \end{equation}
-(since $e\in S$, we have one linear equation for one unknown
-$e_i$). As a consequence, if we know the wedges the Voronoi edge
-belongs to, we have the abscissa in $O(1)$ (see Algorithm \ref{alg:chamedge}).
+(since $e\in S$, we have one linear equation with only one unknown
+$e_i$). As a consequence, if we know the two wedges the Voronoi edge
+belongs to, we have the abscissa in $O(1)$ (see Algorithm
+\ref{alg:chamedge} and Fig.~\ref{fig:algo}$-(c)$).
 \begin{algorithm}[h]\footnotesize
-  $(v_k,v_{k+1})$ = \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_1,\vec{v}_m, S)$\;
-  $(v_j,v_{j+1})$ = \textsc{VoronoiEdgeWedge}$(b,a,\vec{v}_1,\vec{v}_m, S)$\;
+  $(\vec{v}^k,\vec{v}^{k+1})$ = \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}^1,\vec{v}^m, S)$\;
+  $(\vec{v}^j,\vec{v}^{j+1})$ = \textsc{VoronoiEdgeWedge}$(b,a,\vec{v}^1,\vec{v}^m, S)$\;
 
@@
   \Return $e_i$\;
-  \caption{2D chamfer norm \textsc{VoronoiEdge}($a,b,s_i,s_j\in\Z^2$).\label{alg:chamedge}}
+  \caption{\footnotesize
+2D chamfer norm \textsc{VoronoiEdge}($a,b,s^i,s^j\in\Z^2$).\label{alg:chamedge}}
 \end{algorithm}
@@
 Algorithm~\ref{alg:genedge}: Algorithm~\ref{alg:chamedgew} returns the
-wedge associated to $a$ containing the Voronoi edge with respect to
-$b$. Applying this algorithm to obtain the $b$ wedge with respect to
+wedge associated with $a$ containing the Voronoi edge with respect to
+$b$. Applying this algorithm to obtain the wedge associated with $b$ with respect to
 $a$ gives exactly  Algorithm \ref{alg:chamedge}.
-
-\begin{figure}[htbp]
-  \begin{center}
+\begin{figure}[h]
+  \begin{center}\scriptsize
     \subfigure[]{
-      \begin{overpic}[width=3.2cm]{init}
+      \begin{overpic}[width=2.5cm]{init}
         \put(-5,60){$a$}
@@
     \subfigure[]{
-      \begin{overpic}[width=3.2cm]{algoMid}
+      \begin{overpic}[width=2.5cm]{algoMid}
       \put(-5,60){$a$}
@@
         \put(42,105){$S$}
-        \put(12,60){$\vec{v_{mid}}$}
-        \put(13,80){$\vec{v_{mid+1}}$}
-        \put(-5,98){$\vec{v_j}$}
-        \put(5,35){$\vec{v_i}$}
-        \put(50,90){$p_{mid+1}$}
-        \put(50,58){$p_{mid}$}
+        \put(12,60){$\vec{\vec{v}^{mid}}$}
+        \put(13,80){$\vec{\vec{v}^{mid+1}}$}
+        \put(-5,98){$\vec{\vec{v}^j}$}
+        \put(5,32){$\vec{\vec{v}^i}$}
+        \put(50,90){$p^{mid+1}$}
+        \put(50,58){$p^{mid}$}
       \end{overpic}
@@
     \subfigure[]{
-      \begin{overpic}[width=3.2cm]{algoEnd}
+      \begin{overpic}[width=2.5cm]{algoEnd}
       \put(-5,60){$a$}
@@
         \put(50,50){$e$}
-        \put(10,50){$\vec{v_{k}}$}
-        \put(11,70){$\vec{v_{k+1}}$}
-        \put(60,40){$\vec{v_j}$}
-        \put(67,57){$\vec{v_{j+1}}$}
+        \put(7,45){$\vec{\vec{v}^{k}}$}
+        \put(11,70){$\vec{\vec{v}^{k+1}}$}
+        \put(60,40){$\vec{\vec{v}^j}$}
+        \put(67,57){$\vec{\vec{v}^{j+1}}$}
       \end{overpic}
@@
   \end{center}
-  \caption{Illustrations notations of \textsc{VoronoiEdgeWedge} and
-    \textsc{VoronoiEdge}: $(a)$ initial problem, given two sites $a$
-    and $b$, we want to compute the intersection between $S$ and the
-    Voronoi edge of $a$ and $b$. $(b)$ an internal step of
+  \caption{\small \textsc{VoronoiEdgeWedge} and \textsc{VoronoiEdge}: $(a)$
+    initial problem, we want to compute the intersection between $S$
+    and the Voronoi edge of $a$ and $b$. $(b)$ an internal step of
     \textsc{VoronoiEdgeWedge} to reduce the set of directions of $\M$
     at $a$ (here the next recursive call will be on
-    $(v_i,v_{mid})$).$(c)$ final step of \textsc{VoronoiEdge} where
-    both wedges have been obtained and thus $e$ can be computed.}
+    $(\vec{v}^i,\vec{v}^{mid})$).$(c)$ final step of
+    \textsc{VoronoiEdge} where both wedges have been obtained and thus
+    $e$ can be computed.}
   \label{fig:algo}
 \end{figure}
+The dichotomic search shrinks the set of vectors
+$\{\vec{v}^i,\ldots,\vec{v}^j\}$ to end up with a wedge
+$(\vec{v}^k,\vec{v}^{k+1})$ such that the intersection point between
+the straight line $(a + \vec{v}^k)$ and $S$ is in the Voronoi cell of
+$a$ and such that the intersection between $(a + \vec{v}^k)$ and $S$
+is in the Voronoi cell of $b$ (see
+Fig.~\ref{fig:algo}$-(c)$). Algorithm~\ref{alg:chamedgew} thus first
+compute the intersection points associated with a wedge
+$(\vec{v}^{i+(j-i)/2}, \vec{v}^{i+(j-i)/2+1})$ (lines $5-6$);
+Evaluates the distances at these points (lines $7-8$) and then decides
+which set $\{\vec{v}^i,\ldots,\vec{v}^{i+(j-i)/2}\}$ or
+$\{\vec{v}^{i+(j-i)/2},\ldots,\vec{v}^j\}$ has to be considered for
+the recursive call (lines $14-25$ and Fig.~\ref{fig:algo}$-(b)$).
 
-The dichotomic search shrinks the set of vectors
-$\{\vec{v}_i,\ldots,\vec{v}_j\}$ to end up is a wedge $(v_k,v_{k+1})$
-such that the intersection point between the straight line $(a +
-\vec{v}_k)$ and $S$ is in the Voronoi cell of $a$ and such that the
-intersection between $(a + \vec{v}_k)$ and $S$ is in the Voronoi cell
-of $b$ (see Fig.~\ref{fig:algo}$-(b)$). Algorithm~\ref{alg:chamedgew} thus first compute the
-intersection points associated with a wedge $(\vec{v}_{i+(j-i)/2},
-\vec{v}_{i+(j-i)/2+1})$ (lines $5-6$); Evaluates the distances at
-these points (lines $7-8$) and then decides which set
-$\{\vec{v}_i,\ldots,\vec{v}_{i+(j-i)/2}\}$ or
-$\{\vec{v}_{i+(j-i)/2},\ldots,\vec{v}_j\}$ has to be considered for
-the recursive call (lines $14-25$).
-
-\begin{algorithm}
+\begin{algorithm}[t]
 \footnotesize
   \eIf{ $(j-i =1)$}{
-    \Return $(\vec{v}_k,\vec{v}_{k+1})$\;}
+    \Return $(\vec{v}^i,\vec{v}^{i+1})$\;}
 {
    $mid  = i + (j-i)/2$\;
-   Let $p_{mid}$  be the intersection point between $(a +
-   \vec{v}_{mid})$ and $S$\;
-  Let $p_{mid+1}$  be the intersection point between $(a +
-   \vec{v}_{mid+1})$ and $S$\;
+   Let $p^{mid}$  be the intersection point between $(a +
+   \vec{v}^{mid})$ and $S$\;
+  Let $p^{mid+1}$  be the intersection point between $(a +
+   \vec{v}^{mid+1})$ and $S$\;
 
    \tcp*[f]{$O(1)$ evaluation of distances w.r.t. $a$}
-   $d^a_{p_{mid}} = A_{mid}\cdot (p_{mid}-e)^T$\;
-   $d^a_{p_{mid+1}} = A_{mid+1}\cdot (p_{mid+1}-e)^T$\;
+   $d^a_{p^{mid}} = A_{mid}\cdot (p^{mid}-e)^T$\;
+   $d^a_{p^{mid+1}} = A_{mid+1}\cdot (p^{mid+1}-e)^T$\;
 
    \tcp*[f]{$O(\log{m})$ evaluation of distances w.r.t. $b$}
-   $d^b_{p_{mid}} = d_\M(b, p_{mid})$\;
-   $d^b_{p_{mid+1}} = d_\M(b,p_{mid+1})$\;
+   $d^b_{p^{mid}} = d_\M(b, p^{mid})$\;
+   $d^b_{p^{mid+1}} = d_\M(b,p^{mid+1})$\;
 
-   Let $b_{mid}$ be true if $d^a_{p_{mid}} < d^b_{p_{mid}}$; false otherwise\;
-   Let $b_{mid+1}$ be true if $d^a_{p_{mid+1}} < d^b_{p_{mid+1}}$; false otherwise\;
+   Let $b_{mid}$ be true if $d^a_{p^{mid}} < d^b_{p^{mid}}$; false otherwise\;
+   Let $b_{mid+1}$ be true if $d^a_{p^{mid+1}} < d^b_{p^{mid+1}}$; false otherwise\;
 
    \If{ $b_{mid}\neq b_{mid+1}$ \tcp*[r]{we have the Voronoi edge
-       wedge}} { \Return $(\vec{v}_{mid},\vec{v}_{mid+1})$\; }
+       wedge}} { \Return $(\vec{v}^{mid},\vec{v}^{mid+1})$\; }
 
@@
 {
-  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_{mid}, \vec{v}_{j}, S)$\;
+  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}^{mid}, \vec{v}^{j}, S)$\;
 }
 {
-  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_{i}, \vec{v}_{mid}, S)$\;
+  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}^{i}, \vec{v}^{mid}, S)$\;
 }
@@
 {
-  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_{i}, \vec{v}_{mid}, S)$\;
+  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}^{i}, \vec{v}^{mid}, S)$\;
 }
 {
-  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}_{mid}, \vec{v}_{j}, S)$\;
+  \Return \textsc{VoronoiEdgeWedge}$(a,b,\vec{v}^{mid}, \vec{v}^{j}, S)$\;
 }
@@
 }
-  \caption{\textsc{VoronoiEdgeWedge}($a,b\in\Z^2; \vec{v}_i,\vec{v}_j$
+  \caption{\footnotesize
+\textsc{VoronoiEdgeWedge}($a,b\in\Z^2; \vec{v}^i,\vec{v}^j$
     in $\M$; $S$ along the $i^{th}$ direction).\label{alg:chamedgew}}
 \end{algorithm}
-
 \begin{theorem}
 \label{them}
-  Let $\M$ be a 2D chamfer norm with $m$ weighted vectors, then we
-  have
-  \begin{enumerate}[(i)]
-  \item Algorithm     \ref{alg:chamedge} is   $O(\log^2{m})$\;;
-  \item Algorithm \ref{alg:voro} (with predicates from Algorithms
+  Let $\M$ be a 2D chamfer norm with axis symmetric unit ball and  $m$ weighted vectors, then we
+  have:
+  $(i)$ Algorithm     \ref{alg:chamedge} is in  $O(\log^2{m})$;
+  $(ii)$ Algorithm \ref{alg:voro} (with predicates from Algorithms
     \ref{alg:chamedge} and Lemma \ref{lem:log}), computes a Voronoi
@@
     $d_{M}$ in   $ O( \log^2{m}\cdot N^2)$.
-  \end{enumerate}
 \end{theorem}
 \begin{proof}
-Let us first consider statement $(i)$. As described above, Algorithm
+Let us first consider  $(i)$. As described above, Algorithm
 \ref{alg:chamedgew} performs $\log{m}$ recursive calls and each step
-is in $O(\log{m})$. Indeed, $p_{mid}$ and $p_{mid+1}$ are given by the
+is in $O(\log{m})$. Indeed, $p^{mid}$ and $p^{mid+1}$ are given by the
 intersections between two rational slope straight lines plus a
@@
 computations, $O(\log^2{m})$ is required for
-Algorithm~\ref{alg:chamedge}.
-Statement $(ii)$ is a direct consequence of statement $(i)$ and
-$O(1)$ and Lemma~\ref{lem:generic} with $n=2$.$\Box$
+Algorithm~\ref{alg:chamedge}.   $(ii)$ is a direct
+consequence of  $(i)$ and Lemma~\ref{lem:genericDich} with
+$n=2$.$\Box$
 \end{proof}
@@
 %% \emph{general position} ($a\not\subset l$, $b\not\subset l$).  Then,
-%% the intersection point belongs to the two Euclidean planes $P_a$ and
-%% $P_b$, $P_a$ being respectively the Euclidean plane containing $a$ and
-%% $l$ (resp. $P_b$ defined by $b$ and $l$), see Fig.\ref{fig:3D}.
+%% the intersection point belongs to the two Euclidean planes $P^a$ and
+%% $P^b$, $P^a$ being respectively the Euclidean plane containing $a$ and
+%% $l$ (resp. $P^b$ defined by $b$ and $l$), see Fig.\ref{fig:3D}.
 
@@
 %% have to replace the line 4 of Algorithm~\ref{alg:chamedgew} by the
-%% following steps: First, we construct $\vec{v} = (\vec{v}_i +
-%% \vec{v}_j)/2$. If we suppose that $\vec{v}_i$ and $\vec{v}_j$ belongs
-%% to $P_a$, $\vec{v}$ also belongs to $P_a$. Then, we perform a 3D
+%% following steps: First, we construct $\vec{v} = (\vec{v}^i +
+%% \vec{v}^j)/2$. If we suppose that $\vec{v}^i$ and $\vec{v}^j$ belongs
+%% to $P^a$, $\vec{v}$ also belongs to $P^a$. Then, we perform a 3D
 %% ray-shooting to get the facet $F$ of $\B$ pierced by vector
 %% $\vec{v}$. From this facet $F$, we construct the 2D
-%% $(\vec{v}_{mid},\vec{v}_{mid+1})$ wedge on $P_a$ defined by the
-%% intersection of $F$ and $P_a$. Once $(\vec{v}_{mid},\vec{v}_{mid+1})$
+%% $(\vec{v}^{mid},\vec{v}^{mid+1})$ wedge on $P^a$ defined by the
+%% intersection of $F$ and $P^a$. Once $(\vec{v}^{mid},\vec{v}^{mid+1})$
 %% is obtained, we proceed with the rest of the \textsc{VoronoiEdgeWedge}
@@
 %%   computation between a (rational slope) facet $F$ and the (rational)
-%%   plane $P_a$ can be obtained in $O(1)$.  If we denote by $\M_{P_a}$
-%%   be the 2D chamfer norm induced by $\B\cap P_a$. The hypothesis that
+%%   plane $P^a$ can be obtained in $O(1)$.  If we denote by $\M_{P^a}$
+%%   be the 2D chamfer norm induced by $\B\cap P^a$. The hypothesis that
 %%   the vectors uniformly span the sphere of directions is here to
-%%   ensure that if we split $\M_{P_a}$ along the mid direction
-%%   $\vec{v} =(\vec{v}_i + \vec{v}_j)/2$, both subsets of vectors have the same
+%%   ensure that if we split $\M_{P^a}$ along the mid direction
+%%   $\vec{v} =(\vec{v}^i + \vec{v}^j)/2$, both subsets of vectors have the same
 %%   size. If so, $O(\log{m})$ recursive calls is required. The stop
 %%   criterion of the recurrence could be that $\vec{v}$ belong to the
-%%   same facet as both $\vec{v}_i$ and $\vec{v}_j$.$\Box$
+%%   same facet as both $\vec{v}^i$ and $\vec{v}^j$.$\Box$
 %% \end{proof}
@@
 
-In this section, we present some implementation details and
-experimental results for chamfer norm DT in dimension 2.  First of
-all, since release 0.7, most algorithms presented here are available
-in the \textsc{DGtal} library \cite{dgtal}. For $L_p$ metrics, we have
-implemented several \textsc{Closest} and \textsc{HiddenBy} predicates:
-\begin{itemize}
-\item If $p=\{1,2\}$, exact computations are proposed and all
-  predicates are in $O(1)$ with only integer number computations
-  \cite{Hirata1996,Maurer2003,roerdnik};
-\item If $p\in \R$,  $p\geq 1$, we have approximated computations
-  on real numbers (\emph{double}) and we consider the Generic
-  \textsc{HiddenBy} predicate in $O(\log N)$
+In this section, we give some implementation details and experimental
+results for chamfer norm Voronoi map in dimension 2.  First of all,
+most algorithms presented here are available in the \textsc{DGtal}
+library \cite{dgtal}. For $L_p$ metrics, we have implemented several
+\textsc{Closest} and \textsc{HiddenBy} predicates: If $p=\{1,2\}$,
+exact computations are proposed and all predicates are in $O(1)$ with
+only integer number computations
+\cite{Hirata1996,Maurer2003,roerdnik}; If $p\in \R$, $p\geq 1$, we
+have approximated computations on real numbers (\emph{double}) and we
+consider the Generic \textsc{HiddenBy} predicate in $O(\log N)$
 (Alg.~\ref{alg:genhidden}). Since predicates are based on floating
-  point computations, numerical issues may occur;
-\item if $p\in \Z$, $p\geq 3$, we use exact integer number based
-  computations of distances  storing sum of power $p$ quantities (which can be
-  computed in $O(\log{p})$ thanks to exponentiation by squaring). The
-  \textsc{HiddenBy} predicate is also based on Algorithm~\ref{alg:genhidden}.
-\end{itemize}
-
+point computations, numerical issues may occur. If $p\in \Z$, $p\geq
+3$, we use exact integer number based computations of distances
+storing sum of power $p$ quantities (which can be computed in
+$O(\log{p})$ thanks to exponentiation by squaring). The
+\textsc{HiddenBy} predicate is also based on
+Algorithm~\ref{alg:genhidden}.
 Beside these predicates for $L_p$ metrics, \textsc{DGtal} also
@@
 container sorted counterclockwise to be able to get the mid-vector
-$\vec{v}_{mid}$ in $O(1)$. When implementing Algorithms
+$\vec{v}^{mid}$ in $O(1)$. When implementing Algorithms
 \ref{alg:chamedge} and \ref{alg:chamedgew}, few special cases have to
@@
 $A_k\neq A_j$. Thanks to the geometrical representation of the
-dichotomic process (Fig.xxxxxxxxx), such special cases are easy to
-handle. Fig. \ref{fig:2Dvoro} illustrates some comparisons on a small
+dichotomic process (Fig.~\ref{fig:algo}), such special cases are easy to
+handle. Fig. \ref{fig:2Dvoro}-$(a)$ illustrates some results on a small
 domain.
-
-\begin{figure}
-  \begin{center}
-    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-voro-chamf_5711}}
-    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-dt-chamf_5711}}
-    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-voro-chamf_5711-2}}
-    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-dt-chamf_5711-2}}\\
-    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-voro-chamf_l_2}}
-    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-dt-chamf_l_2}}
-    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-voro-chamf_l_22}}
-    \subfigure[]{\includegraphics[width=2.8cm]{figs/image-dt-chamf_l_22}}
-  \end{center}
-  \caption{Voronoi map and distance transformation comparison between
-    $\M_{5-7-11}$ and $L_2$: on a $256^2$ domain with $256$ and $2$
-    random seeds, the first row corresponds to $\M_{5-7-11}$ and the second
-    one to $L_2$.}
-  \label{fig:2Dvoro}
-\end{figure}
-
-To be able to evaluate experimentally the
-computational cost given in Theorem~\ref{them}, we use the following
-setting: given a mask size $m$, we generate $m$ distinct random
-vectors $(x,y)^T$ with $gcd(x,y)=1$ (extracted from Farey series for
-instance). For a general mask of size $m$, we do not try to optimize
-the weights to approximate as best as possible the Euclidean metric
-(\emph{e.g.}  \cite{borgefors}). Weights do not play any role in the
-computational analysis, we just use here trivial weights that ensure
-that $\M$ is a norm.
 \begin{figure}[htbp]
   \begin{center}
-    \includegraphics[width=10cm]{data/result}
+    \subfigure[]{\begin{tabular}{cccc}
+      {\includegraphics[width=1.5cm]{figs/image-voro-chamf_5711}}&
+      {\includegraphics[width=1.5cm]{figs/image-dt-chamf_5711}}&
+      {\includegraphics[width=1.5cm]{figs/image-voro-chamf_5711-2}}&
+      {\includegraphics[width=1.5cm]{figs/image-dt-chamf_5711-2}}\\
+      {\includegraphics[width=1.5cm]{figs/image-voro-chamf_l_2}}&
+      {\includegraphics[width=1.5cm]{figs/image-dt-chamf_l_2}}&
+      {\includegraphics[width=1.5cm]{figs/image-voro-chamf_l_22}}&
+      {\includegraphics[width=1.5cm]{figs/image-dt-chamf_l_22}}
+    \end{tabular}}
+    \begin{tabular}{c}
+      \subfigure[]{\includegraphics[origin=b,width=5.6cm]{data/result}}
+    \end{tabular}
   \end{center}
-  \caption{Experimental evaluation of subquadratic chamfer norm
-    Voronoi map computation.}
-  \label{fig:graph}
+  \caption{$(a)$ Separable Voronoi map and distance transformation for $\M_{5-7-11}$
+    and $L_2$: on a $256^2$ domain with $256$ and $2$ random seeds,
+    the first row corresponds to $\M_{5-7-11}$ and the second one to
+    $L_2$. $(b)$ Experimental evaluation of subquadratic chamfer norm
+    Voronoi map computation.  \label{fig:2Dvoro}}
 \end{figure}
-In Fig.\ref{fig:graph}, we have considered a 2D domain $2048^2$ with
-$2048$ random sites (and chamfer norm with increasing size
-$m$). First, we observe that fixing $N$, the $\log^2{m}$ term is
-clearly visible in the computational cost of the Voronoi map (single
-thread curve). Bumps in the single thread curve may be due to memory
-cache issues. Please note that if we consider classical chamfer norm
-DT from raster scan (and half-masks), the computational cost would
-have been in $O(m\cdot N^2)$ and thus would have a linear behavior in
-Fig.~\ref{fig:graph}.
+To evaluate experimentally the computational cost given in
+Theorem~\ref{them}, we use the following setting: given a mask size
+$m$, we generate $m$ distinct random vectors $(x,y)^T$ with
+$gcd(x,y)=1$ (extracted from Farey series for instance). For a general
+mask of size $m$, we do not optimize the weights to approximate as
+best as possible the Euclidean metric. Indeed, weights do not play any
+role in the computational analysis, we just use trivial ones that
+ensure that $\M$ is a norm with axis symmetric unit ball.
+In Fig.\ref{fig:2Dvoro}-$(b)$, we have considered a 2D domain $2048^2$
+with $2048$ random sites. First, we observe that fixing $N$, the
+$\log^2{m}$ term is clearly visible in the computational cost of the
+Voronoi map (single thread curve). Bumps in the single thread curve
+may be due to memory cache issues. Please note that if we consider
+classical chamfer norm DT from raster scan (and half-masks), the
+computational cost would have been in $O(m\cdot N^2)$ and thus would
+have a linear behavior in Fig.~\ref{fig:2Dvoro}-$(b)$. Since we have a
+separable algorithm, we can trivially implement it in a multi-thread
+environment. Hence, on a bi-processor and quad-core (hyper-threading)
+Intel(R) Xeon(R) cpu (16 threads can run in parallel), we observe a
+speed-up by a factor 10 (blue curve in Fig.~\ref{fig:2Dvoro}-$(b)$).  Please
+note that on this $2048^2$ domain with 2048 sites, Euclidean Voronoi
+Map ($L_2$) is obtained in 954.837 milliseconds on a single core and
+723.196 msec on 16 cores.
 
-Since we have a separable algorithm, we can trivially implement it in
-a multi-thread environment. Hence, on a bi-processor and quad-core
-(hyperthreading) Intel(R) Xeon(R) cpu (16 threads can run in
-parallel), we observe a speed-up by a factor 10 (multi-thread) curve
-in Fig.~\ref{fig:graph}).
+\section{Conclusion and Discussion}
+\label{sec:discussion}
 
-Please note that on this $2048^2$ domain with 2048 sites, Euclidean
-Voronoi Map ($L_2$) is obtained in  954.837 milliseconds on a single
-core and 723.196 msec on 16 cores.
-
-\section{Discussion}
-\label{sec:discussion}
+In the literature, several authors discussed about the fact that a
+large class of metrics can be considered in separable approaches for
+volumetric analysis. In this article, we have proposed several
+algorithms to efficiently solve the Voronoi map and distance
+transformation: given a user-specified distance function (induced by a
+norm with some properties) a first generic separable algorithm can be
+used. Focusing to chamfer norms, geometrical interpretation of this
+generic approach allows us to design a first subquadratic algorithm in
+dimension 2 to compute the Voronoi map.  \sloppy In higher dimensions,
+it turns out that most results are still true: distance function can
+be evaluated in $O(n\cdot\log{m})$ and the dichotomic search described
+in \textsc{VoronoiEdgeWedge} can also be extended to $n$-dimensional
+chamfer norms.
 

### 2014-02-18 latex/dgci2014/data/trace.py

@@ -24,9 +24,9 @@ plt.xlabel( "$m$" )
 plt.ylabel( 'Time in sec' )
 
 p1,=plt.plot( datalist[:,0],datalist[:,1]/1000, 'g',label="Voronoi Map (single thread)",alpha=1 )
-p2,=plt.plot( datalist2[:,0],datalist2[:,1]/1000, 'b',label="Voronoi Map (multi-thread)",alpha=1 )
+p2,=plt.plot( datalist2[:,0],datalist2[:,1]/1000, 'r',label="Voronoi Map (multi-thread)",alpha=1 )
 p3,=plt.plot( myx, 0.04*mylog2, '.r',label="$0.04\log^2{m}$",alpha=0.5 )
-p4,=plt.plot( myx, 0.4*mylog2, '.',label="$4\log^2{m}$",alpha=0.5 )
+p4,=plt.plot( myx, 0.4*mylog2, '.g',label="$0.4\log^2{m}$",alpha=0.5 )
 
 lines=[p1,p2,p3,p4]
 ##plt.legend( loc=2 )

### 2014-02-21 latex/dgci2014/article.tex
release

@@
 \cite{Rosenfeld1968,borgefors,fouard:ivc:2005} or sequences of chamfer
-masks \cite{ROSEN_66,mukherjee,Strand2008,DBLP:conf/dgci/NormandSE13};
+masks \cite{Rosenfeld1966,mukherjee,Strand2008,DBLP:conf/dgci/NormandSE13};
 the vector displacement based Euclidean distance
 \cite{danielson,ragnemalm}; the Voronoi diagram based Euclidean
-distance \cite{BreuEtAl95,maurer_pami} or the square of the Euclidean
+distance \cite{BreuEtAl95,Maurer2003} or the square of the Euclidean
 distance \cite{Hirata,roerdnik}.  For Euclidean or $L_p$ metrics,
@@
 computation is performed and then propagated
-\cite{ROSEN_66,borgefors}. Scanning the domain twice for each
+\cite{Rosenfeld1966,borgefors}. Scanning the domain twice for each
 sub-masks leads to the distance transformation. Again, we end up with
@@
       \hline
-      $L_2$ & $O(1)$ &  $O(1)$ & $\Theta(n\cdot N^n)$ & \cite{Hirata1996}\\
+      $L_2$ & $O(1)$ &  $O(1)$ & $\Theta(n\cdot N^n)$ & \cite{Hirata}\\
       $L_\infty$ & $O(1)$ & $O(1)$ &  $\Theta(n\cdot N^n)$ & \cite{roerdnik}\\
@@
 %\end{table}
-
 \section{Preliminaries}
@@
 neighborhood sequences
-\cite{ROSEN_66,mukherjee,Strand2008,DBLP:conf/dgci/NormandSE13}
+\cite{Rosenfeld1966,mukherjee,Strand2008,DBLP:conf/dgci/NormandSE13}
 whose objective is to have better approximation of the Euclidean
@@
 \label{sec:voronoi-map-from}
-In \cite{Hirata1996,Breu1995,Meijster2000,Maurer2003},
+In \cite{Hirata,BreuEtAl95,roerdnik,Maurer2003},
 several authors have described optimal in time and separable
@@
 In the following, we
-consider Voronoi map approach as defined in \cite{Breu1995}: Let us
+consider Voronoi map approach as defined in \cite{BreuEtAl95}: Let us
 first define hyper-rectangular image $I_X:
@@
 \textsc{Closest} and \textsc{HiddenBy} predicates can be computed in
-$O(1)$ \cite{Breu1995,Hirata1996,Meijster2000}. Hence, Algorithm
+$O(1)$ \cite{BreuEtAl95,Hirata,roerdnik}. Hence, Algorithm
 \ref{alg:voro} is in $O(N_i)$ for dimension $i$, leading to an overall
@@
 
-In \cite{Hirata1996} or \cite{maurer_pami}, authors discussed about
+In \cite{Hirata} or \cite{Maurer2003}, authors discussed about
 conditions on the metric $d$ to ensure that Algorithm \ref{alg:voro}
@@
 (so called \emph{monotonicity property} in \cite{Maurer2003} and is
-related to \emph{quadrangle inequality} in \cite{Hirata1996}).  To sum
+related to \emph{quadrangle inequality} in \cite{Hirata}).  To sum
 up these contributions, we have the following proposition:
-\begin{proposition}[Metric conditions \cite{Hirata1996}]
+\begin{proposition}[Metric conditions \cite{Hirata}]
 \label{prop:voronoi-map-from-1}
@@
 \end{lemma}
-From \cite{Breu1995,roerdnik}, $C=H=O(1)$ for $L_1,L_2$ and $L_\infty$
+From \cite{BreuEtAl95,roerdnik}, $C=H=O(1)$ for $L_1,L_2$ and $L_\infty$
 norms.  For prescribed norm $d$, we first define generic
@@
 only integer number computations
-\cite{Hirata1996,Maurer2003,roerdnik}; If $p\in \R$, $p\geq 1$, we
+\cite{Hirata,Maurer2003,roerdnik}; If $p\in \R$, $p\geq 1$, we
 have approximated computations on real numbers (\emph{double}) and we

### 2014-04-18 latex/dgci2014/rebuttal.txt
rebuttal

        First of all, we would like to thank the reviewers for their
comments. In the following, We will comment some of major remarks
(please note that all remaining remarks, typos and suggestions will be
considered in the camera ready version if the paper is finally
accepted).

**Path based vs. Euclidean Metrics and quadratic complexity**

The first objective of the paper is to propose an algorithmic solution
to efficiently compute distance transformation for some path based
norms which mimics the parallel and separable approach used for
Euclidean and $L_p$ metrics. We will double-check the introduction to
make it clear that the paper focuses on that point.

Concerning the discussion about path based metric vs. Euclidean one,
we are convinced that path based norms are very interesting
mathematical objects and crucial in some applications (non-convex
domains, streaming DT, when the anisotropic nature of their unit ball
is consistent with the application, e.g. in crystallography...).

However, the huge literature about path-based metric optimization to
minimize the rotational dependency tends to illustrate that the
approximation quality (w.r.t. Euclidean distance) also matters. In this
context, the size of the mask is an important parameter (together with
optimized weights). Introduction will be rephrased to clarify this
context.

It is out of the scope of the paper (and won't be added in the
introduction) but please note that for medial axis extraction purposes
(defined as centers of maximal balls), linear  time algorithms
exists for the Euclidean metric [Coeurjolly-PAMI 2007, Hesselink PAMI
2008..]. For path based norms, pre-computations and look-up tables are
usually considered. As far as we know, it is still an active open
problem to prove that distances on shortest paths can be used to
extract the set of (or a subset of) maximal ball centers for the
metric [Strand, DGCI 2011].

**Experiments**

 - Graph size: we agree that graphs labels are quite small. We will
   correct this for the final version if the paper is accepted.

 - Scale-up w.r.t. to number of threads:  definitely
   doable. Experiments will be done and could be included in the final
   version (depending on the final version page limit).

 - Timings for low-size mask: zoom-in to the left-part of the graph
   can be added.

 - Comparison w.r.t. double-scan approach: doable too. However, we may
   end-up with issues with respect to page limit.

**Spelling, Grammar, Paper structure**

All apologizes for the bad English. The text will be double-checked
for the final version.

### 2014-05-13 latex/dgci2014/article.tex
raster scan

@@
 In many applications, separable algorithms have demonstrated their
-efficiency to perform high performance volumetric computations, such
-as distance transformation or medial axis extraction. In the
-literature, several authors have discussed about the conditions on the
-metric to be considered in a separable approach.  In this article, we
-present generic separable algorithms to efficiently compute Voronoi
-maps and distance transformations for a large class of
+efficiency to perform high performance and parallel volumetric
+computations, such as distance transformation or medial axis
+extraction. In the literature, several authors have discussed about
+conditions on the metric to be considered in a separable approach.  In
+this article, we present generic separable algorithms to efficiently
+compute Voronoi maps and distance transformations for a large class of
 metrics. Focusing to path based norms (chamfer masks, neighborhood
 sequences, ...), we detail a subquadratic algorithm to compute such
-volumetric transformations in dimension 2. More precisely, we describe
-a $O(\log^2{m}\cdot N^2)$ algorithm in dimension 2 for shapes in a
-$N\times N$ domain with chamfer norm of size $m$.
+volumetric transformation in dimension 2. More precisely, we describe
+a $O(\log^2{m}\cdot N^2)$ algorithm for shapes in a $N\times N$ domain
+with chamfer norm of size $m$.
 
@@
 $X\subset \Z^n$, the distance transformation labels each point in $X$
-with the distance to its closest point in $\Z^n \setminus X$ (labeling
-each point by the closest background point leads to Voronoi maps, see
-below). Since such characterization is parametrized by a distance
-function, many works have been done to address this distance
-transformation problem with a trade-off between algorithmic
-performances and the \emph{accuracy} of the digital distance function
-with respect to the Euclidean one.  Hence, authors have considered
-distances based on chamfer masks
-\cite{Rosenfeld1968,borgefors,fouard:ivc:2005} or sequences of chamfer
-masks \cite{Rosenfeld1966,mukherjee,Strand2008,DBLP:conf/dgci/NormandSE13};
+with the distance to its closest point in $\Z^n \setminus X$. Labeling
+each point by the closest background point leads to Voronoi
+maps. Since such characterization is parametrized by a distance
+function, many authors address this distance transformation problem
+with trade-offs between algorithmic performances and the
+\emph{accuracy} of the digital distance function with respect to the
+Euclidean one.  Hence, authors have considered distances based on
+chamfer masks \cite{Rosenfeld1968,borgefors,fouard:ivc:2005} or
+sequences of chamfer masks
+\cite{Rosenfeld1966,mukherjee,Strand2008,DBLP:conf/dgci/NormandSE13};
 the vector displacement based Euclidean distance
-\cite{danielson,ragnemalm}; the Voronoi diagram based Euclidean
-distance \cite{BreuEtAl95,Maurer2003} or the square of the Euclidean
-distance \cite{Hirata,roerdnik}.  For Euclidean or $L_p$ metrics,
-separable volumetric computations have demonstrated to be very
-efficient: optimal $O(n\cdot N^n)$ time algorithms for shapes in $N^n$
-domains, optimal multi-thread/GPU implementation\ldots (please refer
-to \cite{dcoeurjo_ChapDTWADGMM} for a discussion). For path-based
-metrics (chamfer mask, -weighted- neighborhood sequences,\ldots), two
-main techniques exist to compute the distance transformation. The
-first one considers a weighted graph formulation of the problem, and
-shortest path in graphs using Dijkstra-like algorithm can be
-considered. If $m$ denotes the size of the chamfer mask, computational
-cost could be in $O(m\cdot N^n)$ using a cyclic bucket data structure
+\cite{danielson,ragnemalm}; Voronoi diagram based Euclidean distance
+\cite{BreuEtAl95,Maurer2003} or the square of the Euclidean distance
+\cite{Hirata,roerdnik}.  For the Euclidean metric, separable
+volumetric computations have demonstrated to be very efficient:
+optimal $O(n\cdot N^n)$ time algorithms for shapes in $N^n$ domains,
+optimal multi-thread/GPU implementation\ldots (please refer to
+\cite{dcoeurjo_ChapDTWADGMM} for a discussion). For path-based metrics
+(chamfer mask, -weighted- neighborhood sequences,\ldots), two main
+techniques exist to compute the distance transformation. The first one
+considers a weighted graph formulation of the problem and
+Dijkstra-like algorithms on weighted graphs to compute distances. If
+$m$ denotes the size of the chamfer mask, computational cost could be
+in $O(m\cdot N^n)$ using a cyclic bucket data structure
 \cite{verwer_uniform}. Another approach consists in a raster scan of
-the domain: first the chamfer mask is decomposed into two disjoint
+the domain: first the chamfer mask is decomposed into disjoint
 sub-masks. Then the domain grid points are scanned in a given order
-(consistent with the sub-masks construction) and a local minimum
-computation is performed and then propagated
-\cite{Rosenfeld1966,borgefors}. Scanning the domain twice for each
-sub-masks leads to the distance transformation. Again, we end up with
-a $O(m\cdot N^n)$ computational cost. This complexity is said to be
-quadratic in $m$ and $N$ since for arbitrary large image $N$, even if
-$m \ll N$, $m$ has to be in $O(N^n)$ to have accurate asymptotic DT.
+(consistent with the sub-mask construction) and a local computation is
+performed before being propagated
+\cite{Rosenfeld1966,borgefors}. Scanning the domain several times (one
+per sub-mask) leads to the distance transformation values. Again, we
+end up with a $O(m\cdot N^n)$ computational cost.
+
+Beside specific applications which use the anisotropic nature of the
+chamfer mask, rotational dependency is usually ensured with increasing
+mask size $m$ together with weight optimization. In this context and
+for arbitrarily large image $N$, both Dijsktra-like and raster scan
+approach have computational cost which is quadratic with respect to
+$N$ and $m$. In practical situations, $m \ll N$ but $m$ still needs to
+be in $O(N^n)$ to have accurate asymptotic DT.
+
 Please note that Dijkstra's graph approach allows us to defined
@@
 \textbf{Contributions} In this article, we first describe the generic
-framework for separable distance transformation and conditions on the
-metric to be consistent with this model. Then, we describe
-subquadratic algorithms in dimension 2 to compute error-free distance
+framework for separable distance transformation and metric conditions
+to be consistent with this model. Then, we describe subquadratic and
+parallel algorithms in dimension 2 to compute error-free distance
 transformation and Voronoi map for chamfer norms and other path-based
@@
   norm $g$.  $(E, F, d)$ is called a  metric space if $d:~E\rightarrow
-  F$.
+  F$ (with $E$ such that for $a,b\in E$, $(b-a)\in EV$).
 \end{definition}
@@
 (chamfer masks, -weighted- neighborhood sequences...)  aim at defining
+\emph{digital}
 metrics induced by norms in metric spaces $(\Z^n, \Z , d)$.  Note that
@@
   \end{equation}
-characterize metric spaces $(\Z^n, \R , d_{L_p})$. Rounding the \sloppy
-distance function $(\Z^n,\Z, \lceil d_{L_p}\rceil)$ is a metric
-space \cite{klette_book}.
+defines metric spaces $(\Z^n, \R , d_{L_p})$ which are not
+\emph{digital}. However, rounding up the \sloppy distance function
+$(\Z^n,\Z, \lceil d_{L_p}\rceil)$ is a digital metric space
+\cite{klette_book}.
 
@@
 continuous Voronoi diagram for the metric $d$ of points
-$\Z^n\setminus$ and the lattice $\Z^n$. If a digital point $a$ belongs
-to a Voronoi diagram $d-$facet ($1\leq d< n$), $a$ is equidistant to 2
+$\Z^n\setminus X$ and the lattice $\Z^n$. If a digital point $a$ belongs
+to a Voronoi diagram $d-$facet ($0\leq d< n$), $a$ is equidistant to 2
 or more points in $\Z^n\setminus X$ but only one is considered in
@@
   $w\in\N^*$. A chamfer mask $\M$ is a central-symmetric set of weighted
-  vectors with non-empty vectors and containing at least a basis of
+  vectors with no null vectors and containing at least a basis of
   $\Z^n$.
@@
 Many authors have proposed algorithmic and/or analytic approaches to
-construct chamfer masks approximating the Euclidean metric and being
-induced by a norm. In the following, we focus on such \emph{chamfer
-  norms}.  To evaluate distances between two digital points for a
+construct chamfer masks approximating the Euclidean metric. In the following, we focus on such \emph{chamfer
+  norms} which are chamfer metric induced by a norm).  To evaluate distances between two digital points for a
 given chamfer metric, direct formulations have been proposed with
@@
 \begin{definition}[Rational ball, minimal H-representation \cite{Thiel_hdr,DBLP:journals/pr/NormandE09}]
-  Given a Chamfer mask $\M$ inducing a norm, the rational ball
-  associated with $\M$ is the polytope
+  Given a Chamfer norm $\M$, the
+  rational ball associated with $\M$ is the polytope
   \begin{equation}
@@
   \end{equation}
-Rational ball $\B$ can also be described in a H-representation of
+Rational ball $\B$ can also be described as the H-representation of
 polytope with minimal parameter \cite{DBLP:conf/dgci/NormandSE13}: $ P
@@
 ~\exists x\in P\quad A_kx=y_k.\footnote{$A_k$ being the $k^{th}$ row
-  of $A$.}$ $f$ being the number of row in $A$ and the number of
+  of $A$.}$ $f$ being the number of rows in $A$ and the number of
 facets in $\B$, and is thus related to $|\M|$.
@@
 \end{proposition}
-Among path-based digital metric, we can also introduce (weighted)
-neighborhood sequences
-\cite{Rosenfeld1966,mukherjee,Strand2008,DBLP:conf/dgci/NormandSE13}
-whose objective is to have better approximation of the Euclidean
-metric from sequences of elementary chamfer masks.  A key result have
-been demonstrated in \cite{DBLP:conf/dgci/NormandSE13} stating that
-for such distance functions, a minimal parameter polytope
-representation exists and that distances can be obtained from similar
-expression to (\ref{eq:1}):
+Among path-based digital metric, (weighted) neighborhood sequences
+have been proposed to have better approximation of the Euclidean
+metric from sequences of elementary chamfer masks
+\cite{Rosenfeld1966,mukherjee,Strand2008,DBLP:conf/dgci/NormandSE13}.
+A key result have been demonstrated in
+\cite{DBLP:conf/dgci/NormandSE13} stating that for such distance
+functions, a minimal parameter polytope representation exists and that
+distances can be obtained from similar expression to (\ref{eq:1}):
 \begin{equation}
@@
 %\cite{dcoeurjo_ChapDT} for an overview).
-In the following, we
-consider Voronoi map approach as defined in \cite{BreuEtAl95}: Let us
-first define hyper-rectangular image $I_X:
-[1..N_1]\times\ldots\times[1..N_n] \rightarrow \{0,1\}$ such that $X\subset
-I_X$ and $I_X(a)= 1$ for $a\in [1..N_1]\times\ldots\times[1..N_n]$ iff $a\in
-X$ ($I_X(a)=0$ otherwise). In dimension 2, we first process each row
-of the input image to create independent 1D Voronoi maps along the
-first dimension for the metric. Then, for each further dimension, the
-partial Voronoi map $\Pi_X$ is updated using one dimensional
-independent processes on image spans along the $i^{th}$ dimension.
+In the following, we consider Voronoi map approach as defined in
+\cite{BreuEtAl95}: Let us first define hyper-rectangular image $I_X:
+     [1..N_1]\times\ldots\times[1..N_n] \rightarrow \{0,1\}$ such that
+     $I_X(a)= 1$ for $a\in [1..N_1]\times\ldots\times[1..N_n]$ iff
+     $a\in X$ ($I_X(a)=0$ otherwise). In dimension 2, each row of the
+     input image are processed to create independent 1D Voronoi maps
+     along the first dimension for the metric. Then, for each further
+     dimension, the partial Voronoi map $\Pi_X$ is updated using one
+     dimensional independent processes on image spans along the
+     $i^{th}$ dimension.
 %% \begin{figure}
@@
   $S$ along the $i^{th}$ direction is a vector of $N_i$ points with
-  same coordinates except at $i$.} In this process, metric information
-are embedded in the following two predicates (see
+  same coordinates except at $i$.}. In this process, metric information
+are embedded in the following  predicates (see
 Fig.~\ref{fig:predicates}): \textsc{Closest}$(a, b, c)$, given three
@@
   \KwResult{Updated partial Voronoi map $\Pi_X$ along $S$.}
-\If{ i = 1}
+\If{ $i == 1$ \tcp*[r]{Special case for the first  dimension}}
 { $k=0$\;
 \ForEach{point $s$ in $S$}{
-    \If{$I_X(s) = 1$}
+    \If{$I_X(s) == 1$}
      {
@@
   {
-    \While{($k < |L_S|$) and not(\textsc{Closest}($s^i$, $L_S[k]$, $L_S[k+1]$))}
+    \While{($k < |L_S|$) and not(\textsc{Closest}($s$, $L_S[k]$, $L_S[k+1]$))}
           {
@@
     \subfigure[]{\begin{overpic}[width=1.1cm]{figs/closest}
-    \put(-5,52){$a$}
-    \put(2,78){$b$}
-    \put(47,55){$c$}
+    \put(-5,52){$b$}
+    \put(2,78){$c$}
+    \put(47,55){$a$}
     \put(38,-15){$S$}
@@
 In other words, \textsc{HiddenBy} returns true if and only if the
-Voronoi cell of sites $a$ and $c$ \emph{hide} the Voronoi cell of $b$
+Voronoi cells of sites $a$ and $c$ \emph{hide} the Voronoi cell of $b$
 along $S$.  For $L_1$, $L_2$ and $L_\infty$ metrics,
@@
 (resp. $v_l(b)$) the intersection between the Voronoi cell of $a$
-(resp. $b$) and l, then $v_l(a)$ and $v_l(b)$ are simply connected
+(resp. $b$) and $l$, then $v_l(a)$ and $v_l(b)$ are simply connected
 Euclidean segments and $v_l(a)$ appears \emph{before} $v_l(b)$ on $l$
@@
 related to \emph{quadrangle inequality} in \cite{Hirata}).  To sum
-up these contributions, we have the following proposition:
+up these contributions, we have the following sufficient conditions on
+the metric:
 \begin{proposition}[Metric conditions \cite{Hirata}]
@@
 \end{proposition}
-When implementing Algorithm 1, we say that the distance comparison
+When implementing Algorithm 1, the distance comparison
 predicate is exact if we can compare two distances, \emph{e.g.}
-\textsc{Closest} predicate, without error. Hence, Algorithm \ref{alg:voro}
-provides exact Voronoi map computation for $L_p$ norms. In this case,
-distance comparison predicate can be implemented error-free from
-integer number comparison considering the $p$ power of the distance
-function $\left (d_{L_p}\right)^p$.  Proposition
+\textsc{Closest} predicate, without error.
+
+For $L_p$ norms Algorithm \ref{alg:voro} provides exact Voronoi map
+computation. Indeed, distance comparison predicate can be implemented
+error-free from integer number comparisons considering the $p$ power of
+the distance function $\left (d_{L_p}\right)^p$.
+
+Proposition
 \ref{prop:voronoi-map-from-1} also implies that most chamfer norms and
-neighborhood sequences based norms can also be considered in separable
+neighborhood sequence based norms can also be considered in separable
 Algorithm \ref{alg:voro} (see Fig.~\ref{fig:metrics}). We just need
@@
 Algorithms~\ref{alg:genclosest}, \ref{alg:genedge} and
-\ref{alg:genhidden}: from some evaluations of $d$, \textsc{HiddenBy}
+\ref{alg:genhidden}: From some evaluations of $d$, \textsc{HiddenBy}
 predicate is obtained by a dichotomic search on the 1D image span $S$
@@
 \begin{proof}
-  First, the generic \textsc{VoronoiEdge} is dichotomic in
+  First, the generic \textsc{VoronoiEdge} is dichotomic with
   $O(\log{N})$ steps and $O(C)$ for each one. \textsc{VoronoiEdge} is
@@
 N^n)$ computational cost. In the following sections, we use the convex
-structure of $\B$ to design a first subquadratic algorithm for chamfer
+structure of $\B$ to design a parallel subquadratic algorithm for chamfer
 norms.
@@
 associated a row $A_k$ in the minimal H-representation of $A$ ($A_k$
-can also be seen as a  --non-unitary-- normal vectors to $\B$ facets
+can also be seen as a  --non-unitary-- normal vector to $\B$ facets
 \cite{DBLP:journals/pr/NormandE09}). Using similar notations,
@@
 Please note that in practical implementations, we can use symmetries
-in $\M$ vectors to only work on restrictions of chamfer mask
-directions.  To optimize the \textsc{HiddenBy} predicate, we focus on
+in $\M$  to only work on restrictions of chamfer mask
+directions, so called \emph{generator} in the literature.  To optimize the \textsc{HiddenBy} predicate, we focus on
 the \textsc{VoronoiEdge} function. Given two points $a$ and $b$
@@
 $e'_i>e_i$.
-Let us first suppose that we don't have $e$ but we know the two wedges
+Let us first suppose that we do not have $e$ but we know the two wedges
 $(\vec{v}^{k},\vec{v}^{k+1})$ (resp. $(\vec{v}^j,\vec{v}^{j+1})$) such
@@
 $b$. Applying this algorithm to obtain the wedge associated with $b$ with respect to
-$a$ gives exactly  Algorithm \ref{alg:chamedge}.
+$a$ defines  Algorithm \ref{alg:chamedge}.
 \begin{figure}[h]
@@
     initial problem, we want to compute the intersection between $S$
-    and the Voronoi edge of $a$ and $b$. $(b)$ an internal step of
+    and the Voronoi edge of $a$ and $b$ (in red). $(b)$ an internal step of
     \textsc{VoronoiEdgeWedge} to reduce the set of directions of $\M$
@@
 intersections between two rational slope straight lines plus a
-rounding operation on fractions, which are assumed to be $O(1)$. Then,
+rounding operations on rational fractions, which are assumed to be $O(1)$. Then,
 line 8 requires two $O(\log{m})$ computations by
@@
 function (taking two points and returning a value) corresponding to a
-norm, generic \textsc{Closest} and \textsc{HiddenBy} predicates can be
+norm with axis symmetric unit ball, generic \textsc{Closest} and \textsc{HiddenBy} predicates can be
 automatically constructed. Please note that since all algorithms are
@@
 be taken into account. For instance, we have to handle situations
-where $a$, $b$ or $c$ belongs to $S$ in Alg.~\ref{alg:chamedge} and
+where $a$, $b$ or $c$ belong to $S$ in Alg.~\ref{alg:chamedge} and
 \ref{alg:chamedgew}. Furthermore, Eq.~(\ref{eq:3}) has a solution iff
@@
     \subfigure[]{\begin{tabular}{cccc}
-      {\includegraphics[width=1.5cm]{figs/image-voro-chamf_5711}}&
-      {\includegraphics[width=1.5cm]{figs/image-dt-chamf_5711}}&
-      {\includegraphics[width=1.5cm]{figs/image-voro-chamf_5711-2}}&
-      {\includegraphics[width=1.5cm]{figs/image-dt-chamf_5711-2}}\\
-      {\includegraphics[width=1.5cm]{figs/image-voro-chamf_l_2}}&
-      {\includegraphics[width=1.5cm]{figs/image-dt-chamf_l_2}}&
-      {\includegraphics[width=1.5cm]{figs/image-voro-chamf_l_22}}&
-      {\includegraphics[width=1.5cm]{figs/image-dt-chamf_l_22}}
+      {\includegraphics[width=3cm]{figs/image-voro-chamf_5711}}&
+      {\includegraphics[width=3cm]{figs/image-dt-chamf_5711}}&
+      {\includegraphics[width=3cm]{figs/image-voro-chamf_5711-2}}&
+      {\includegraphics[width=3cm]{figs/image-dt-chamf_5711-2}}\\
+      {\includegraphics[width=3cm]{figs/image-voro-chamf_l_2}}&
+      {\includegraphics[width=3cm]{figs/image-dt-chamf_l_2}}&
+      {\includegraphics[width=3cm]{figs/image-voro-chamf_l_22}}&
+      {\includegraphics[width=3cm]{figs/image-dt-chamf_l_22}}
     \end{tabular}}
     \begin{tabular}{c}
-      \subfigure[]{\includegraphics[origin=b,width=5.6cm]{data/result}}
+      \subfigure[]{\includegraphics[origin=b,width=6.5cm]{data/result}}
+      \subfigure[]{\includegraphics[origin=b,width=6.5cm]{data/result-zoom}}
     \end{tabular}
@@
 \end{figure}
+
 To evaluate experimentally the computational cost given in
@@
 may be due to memory cache issues. Please note that if we consider
-classical chamfer norm DT from raster scan (and half-masks), the
+classical chamfer norm DT from raster scan (and sub-masks), the
 computational cost would have been in $O(m\cdot N^2)$ and thus would
@@
 generic approach allows us to design a first subquadratic algorithm in
-dimension 2 to compute the Voronoi map.  \sloppy In higher dimensions,
-it turns out that most results are still true: distance function can
-be evaluated in $O(n\cdot\log{m})$ and the dichotomic search described
-in \textsc{VoronoiEdgeWedge} can also be extended to $n$-dimensional
-chamfer norms.
+dimension 2 to compute the Voronoi map. Thanks to separability,
+parallel implementation of the distance transformation leads to
+efficient distance computation.
+
+\sloppy In higher dimensions, it turns out that most results are still
+true: distance function can be evaluated in $O(n\cdot\log{m})$ and the
+dichotomic search described in \textsc{VoronoiEdgeWedge} can also be
+extended to $n$-dimensional chamfer norms.
 

### 2014-05-13 latex/dgci2014/data/trace.py

@@ -5,7 +5,7 @@ import glob
 import os
 
 from matplotlib import rc
-##rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+rc('font',**{'size': 18})
 rc('text', usetex=True)
 
 current_path=os.getcwd()
@@ -20,7 +20,7 @@ datalist = pylab.loadtxt( "statVoronoi-mono.txt" )
 datalist2 = pylab.loadtxt( "statVoronoi-openmp.txt" )
 
 #plt.legend( loc=2 )
-plt.xlabel( "$m$" )
+plt.xlabel( "Mask size $m$" )
 plt.ylabel( 'Time in sec' )
 
 p1,=plt.plot( datalist[:,0],datalist[:,1]/1000, 'g',label="Voronoi Map (single thread)",alpha=1 )
@@ -35,6 +35,35 @@ plt.legend(lines, [l.get_label() for l in lines], loc=7,frameon=False)
 
 ##plt.show()
 plt.savefig( 'result.pdf', format='PDF' )
+
+
+datalistt = pylab.loadtxt( "statVoronoi-mono-short.txt" )
+datalistt2 = pylab.loadtxt( "statVoronoi-openmp-short.txt" )
+
+
+myxx = np.linspace(0.01, 90)
+myylog2 = np.log(myxx)*np.log(myxx)
+
+fig2 = plt.figure()
+axes2 = fig2.add_subplot( 1, 1, 1 )
+
+plt.xlabel( "Mask size $m$" )
+plt.ylabel( 'Time in sec' )
+
+p1,=plt.plot( datalistt[:,0],datalistt[:,1]/1000, 'g',label="Voronoi Map (single thread)",alpha=1 )
+p2,=plt.plot( datalistt2[:,0],datalistt2[:,1]/1000, 'r',label="Voronoi Map (multi-thread)",alpha=1 )
+p3,=plt.plot( myxx, 0.04*myylog2, '.r',label="$0.04\log^2{m}$",alpha=0.5 )
+p4,=plt.plot( myxx, 0.4*myylog2, '.g',label="$0.4\log^2{m}$",alpha=0.5 )
+
+liness=[p1,p2,p3,p4]
+##plt.legend( loc=2 )
+plt.legend(liness, [l.get_label() for l in lines], loc=2,frameon=False)
+
+
+##plt.show()
+plt.savefig( 'result-zoom.pdf', format='PDF' )
+
+
 
 
 

### 2014-05-13 src/statVoronoi-raster.cpp

@@ -41,11 +41,58 @@ void constructPredicate(Predicate &mySet, const unsigned int nbSeeds, const unsi
     mySet.erase (*it);
 }
 
+template <typename Domain, typename Predicate, typename Metric>
+ImageContainerBySTLVector< Domain, int> rasterScan(const  Domain &aDomain,
+                                                  const  Predicate &aPred,
+                                                  const  Metric &aMask)
+{
+  //Init image
+  ImageContainerBySTLVector<Domain, int> image;
+  for(typename Domain::ConstIterator it = aDomain.begin(), itend = aDomain.end();
+      it != itend; ++it)
+    if (aPred (*it))
+      image.setValue(*it, 0);
+    else
+      image.setValue(*it, 10001);
+  
+  //top down
+  for(typename Domain::ConstIterator it = aDomain.begin(), itend = aDomain.end();
+      it != itend; ++it)
+  {
+    int myMin = image( *it );
+    for (typename Metric::ConstIterator itm = aMask. begin(), itmend = aMask.end();
+         itm != itmend;
+         itm++)
+    {
+      if ((image.domain().isInside( *it + *itm)) && (myMin > image(*it) + image(*it + *itm)))  //w=1
+        myMin = image(*it) + image(*it + *itm);
+    }
+    image.setValue( *it , myMin);
+  }
+ 
+  
+  //downtop
+  for(typename Domain::ReverseConstIterator it = aDomain.begin(), itend = aDomain.end();
+      it != itend; ++it)
+  {
+    int myMin = image( *it );
+    for (typename Metric::ConstIterator itm = aMask. begin(), itmend = aMask.end();
+         itm != itmend;
+         itm++)
+    {
+      if ((image.domain().isInside( *it - *itm)) && (myMin > image(*it) + image(*it - *itm)))  //w=1
+        myMin = image(*it) + image(*it - *itm);
+        }
+    image.setValue( *it , myMin);
+  }
+  return image ;
+}
+
 
 int main(int argc, char **argv)
 {
-  unsigned int maxN = 3;
-  unsigned int domSize = 64;
+  unsigned int maxN = 5;
+  unsigned int domSize = 2048;
   unsigned int nbSeeds = domSize;
   
   
@@ -64,7 +111,7 @@ int main(int argc, char **argv)
     trace.beginBlock("DT distances");
   
[…]

### 2014-05-13 src/statVoronoi-raster.cpp
fix

@@ -60,7 +60,7 @@ ImageContainerBySTLVector< Domain, int> rasterScan(const  Domain &aDomain,
       it != itend; ++it)
   {
     int myMin = image( *it );
-    for (typename Metric::ConstIterator itm = aMask. begin(), itmend = aMask.end();
+    for (typename Metric::ConstIterator itm = aMask. rbegin(), itmend = aMask.rend();
          itm != itmend;
          itm++)
     {

### 2014-05-13 src/statVoronoi-raster.cpp
ok

@@ -60,7 +60,7 @@ ImageContainerBySTLVector< Domain, int> rasterScan(const  Domain &aDomain,
       it != itend; ++it)
   {
     int myMin = image( *it );
-    for (typename Metric::ConstIterator itm = aMask. rbegin(), itmend = aMask.rend();
+    for (typename Metric::ConstIterator itm = aMask. begin(), itmend = aMask.end();
          itm != itmend;
          itm++)
     {
@@ -72,7 +72,7 @@ ImageContainerBySTLVector< Domain, int> rasterScan(const  Domain &aDomain,
  
   
   //downtop
-  for(typename Domain::ReverseConstIterator it = aDomain.begin(), itend = aDomain.end();
+  for(typename Domain::ConstReverseIterator it = aDomain.rbegin(), itend = aDomain.rend();
       it != itend; ++it)
   {
     int myMin = image( *it );

### 2014-05-13 src/statVoronoi-raster.cpp
fixing types

@@ -43,17 +43,18 @@ void constructPredicate(Predicate &mySet, const unsigned int nbSeeds, const unsi
 
 template <typename Domain, typename Predicate, typename Metric>
 ImageContainerBySTLVector< Domain, int> rasterScan(const  Domain &aDomain,
-                                                  const  Predicate &aPred,
-                                                  const  Metric &aMask)
+                                                   const  Predicate &aPred,
+                                                   Metric &aMask)
 {
   //Init image
-  ImageContainerBySTLVector<Domain, int> image;
+  ImageContainerBySTLVector<Domain, int> image(aDomain);
   for(typename Domain::ConstIterator it = aDomain.begin(), itend = aDomain.end();
       it != itend; ++it)
     if (aPred (*it))
       image.setValue(*it, 0);
     else
       image.setValue(*it, 10001);
+  
   
   //top down
   for(typename Domain::ConstIterator it = aDomain.begin(), itend = aDomain.end();
@@ -69,7 +70,6 @@ ImageContainerBySTLVector< Domain, int> rasterScan(const  Domain &aDomain,
     }
     image.setValue( *it , myMin);
   }
- 
   
   //downtop
   for(typename Domain::ConstReverseIterator it = aDomain.rbegin(), itend = aDomain.rend();
@@ -111,7 +111,7 @@ int main(int argc, char **argv)
     trace.beginBlock("DT distances");
   
     typedef VoronoiMap<Z2i::Space, Z2i::DigitalSet, ChamferNorm2D<Z2i::Space> > VoroChamf;
-    ImageContainerBySTLVector<Z2i::Domain, int> result = rasterScan(&domain, &mySet,&mask);
+    ImageContainerBySTLVector<Z2i::Domain, int> result = rasterScan(domain, mySet,mask);
     double duration = trace.endBlock();
     
     std::cout <<mask.size()<<" "<<duration<<std::endl;

### 2014-05-13 src/statVoronoi-raster.cpp
ok

@@ -91,7 +91,7 @@ ImageContainerBySTLVector< Domain, int> rasterScan(const  Domain &aDomain,
 
 int main(int argc, char **argv)
 {
-  unsigned int maxN = 5;
+  unsigned int maxN = 50;
   unsigned int domSize = 2048;
   unsigned int nbSeeds = domSize;
   
@@ -114,7 +114,7 @@ int main(int argc, char **argv)
     ImageContainerBySTLVector<Z2i::Domain, int> result = rasterScan(domain, mySet,mask);
     double duration = trace.endBlock();
     
-    std::cout <<mask.size()<<" "<<duration<<std::endl;
+    std::cout <<mask.size()<<" "<<duration / 2.0<<std::endl;
     
     N++;
     

### 2014-05-13 src/statVoronoi-raster.cpp
image

@@ -41,13 +41,13 @@ void constructPredicate(Predicate &mySet, const unsigned int nbSeeds, const unsi
     mySet.erase (*it);
 }
 
-template <typename Domain, typename Predicate, typename Metric>
-ImageContainerBySTLVector< Domain, int> rasterScan(const  Domain &aDomain,
+template <typename Domain, typename Predicate, typename Metric, typename Image>
+void rasterScan(const  Domain &aDomain,
                                                    const  Predicate &aPred,
-                                                   Metric &aMask)
+                                                   Metric &aMask,
+                                                   Image &image)
 {
   //Init image
-  ImageContainerBySTLVector<Domain, int> image(aDomain);
   for(typename Domain::ConstIterator it = aDomain.begin(), itend = aDomain.end();
       it != itend; ++it)
     if (aPred (*it))
@@ -85,7 +85,6 @@ ImageContainerBySTLVector< Domain, int> rasterScan(const  Domain &aDomain,
         }
     image.setValue( *it , myMin);
   }
-  return image ;
 }
 
 
@@ -108,10 +107,13 @@ int main(int argc, char **argv)
     trace.info() << mask<<std::endl;
     Z2i::Point origin(0,0);
    
+    ImageContainerBySTLVector<Z2i:: Domain, int> image(domain);
+
+    
     trace.beginBlock("DT distances");
   
     typedef VoronoiMap<Z2i::Space, Z2i::DigitalSet, ChamferNorm2D<Z2i::Space> > VoroChamf;
-    ImageContainerBySTLVector<Z2i::Domain, int> result = rasterScan(domain, mySet,mask);
+    rasterScan(domain, mySet,mask, image);
     double duration = trace.endBlock();
     
     std::cout <<mask.size()<<" "<<duration / 2.0<<std::endl;

### 2014-05-14 latex/dgci2014/data/trace.py
resul

@@ -18,6 +18,7 @@ axes = fig.add_subplot( 1, 1, 1 )
 
 datalist = pylab.loadtxt( "statVoronoi-mono.txt" )
 datalist2 = pylab.loadtxt( "statVoronoi-openmp.txt" )
+datalist3 = pylab.loadtxt( "result-raster.txt" )
 
 #plt.legend( loc=2 )
 plt.xlabel( "Mask size $m$" )
@@ -25,10 +26,11 @@ plt.ylabel( 'Time in sec' )
 
 p1,=plt.plot( datalist[:,0],datalist[:,1]/1000, 'g',label="Voronoi Map (single thread)",alpha=1 )
 p2,=plt.plot( datalist2[:,0],datalist2[:,1]/1000, 'r',label="Voronoi Map (multi-thread)",alpha=1 )
+p2b,=plt.plot( datalist3[:,0],datalist3[:,1]/1000, 'b',label="Raster scan",alpha=1 )
 p3,=plt.plot( myx, 0.04*mylog2, '.r',label="$0.04\log^2{m}$",alpha=0.5 )
 p4,=plt.plot( myx, 0.4*mylog2, '.g',label="$0.4\log^2{m}$",alpha=0.5 )
 
-lines=[p1,p2,p3,p4]
+lines=[p1,p2,p2b,p3,p4]
 ##plt.legend( loc=2 )
 plt.legend(lines, [l.get_label() for l in lines], loc=7,frameon=False)
 
@@ -39,6 +41,7 @@ plt.savefig( 'result.pdf', format='PDF' )
 
 datalistt = pylab.loadtxt( "statVoronoi-mono-short.txt" )
 datalistt2 = pylab.loadtxt( "statVoronoi-openmp-short.txt" )
+datalistt3 = pylab.loadtxt( "result-raster-short.txt" )
 
 
 myxx = np.linspace(0.01, 90)
@@ -52,10 +55,11 @@ plt.ylabel( 'Time in sec' )
 
 p1,=plt.plot( datalistt[:,0],datalistt[:,1]/1000, 'g',label="Voronoi Map (single thread)",alpha=1 )
 p2,=plt.plot( datalistt2[:,0],datalistt2[:,1]/1000, 'r',label="Voronoi Map (multi-thread)",alpha=1 )
[…]

### 2014-05-14 latex/dgci2014/article.tex
Final

@@
 compute Voronoi maps and distance transformations for a large class of
-metrics. Focusing to path based norms (chamfer masks, neighborhood
+metrics. Focusing on path based norms (chamfer masks, neighborhood
 sequences, ...), we detail a subquadratic algorithm to compute such
@@
 
-Since early works on digital geometry, distance transformation plays
+Since early works on digital geometry, distance transformation has
+been playing
 an important role in many applications
@@
 Beside specific applications which use the anisotropic nature of the
-chamfer mask, rotational dependency is usually ensured with increasing
-mask size $m$ together with weight optimization. In this context and
-for arbitrarily large image $N$, both Dijsktra-like and raster scan
-approach have computational cost which is quadratic with respect to
+chamfer mask, rotational dependency is usually ensured  increasing
+the mask size $m$ together with optimizing weights. In this context and
+for arbitrarily large  $N$, both Dijsktra-like and raster scan
+approaches have a quadratic computational cost   with respect to
 $N$ and $m$. In practical situations, $m \ll N$ but $m$ still needs to
@@
 transformation and Voronoi map for chamfer norms and other path-based
-metrics. Overall computational costs can be summarized as follows:
+metrics. Overall computational costs can be summarized as follows (see
+\ref{sec:first-gener-adapt} for predicate definitions):
 %\begin{table}
@@
 metrics induced by norms in metric spaces $(\Z^n, \Z , d)$.  Note that
-(weighed, with $w_i\geq 0$) $L_p$ metrics
+(weighted, with $w_i\geq 0$) $L_p$ metrics
 \begin{equation}
@@
   \end{equation}
-defines metric spaces $(\Z^n, \R , d_{L_p})$ which are not
+define metric spaces $(\Z^n, \R , d_{L_p})$ which are not
 \emph{digital}. However, rounding up the \sloppy distance function
@@
 construct chamfer masks approximating the Euclidean metric. In the following, we focus on such \emph{chamfer
-  norms} which are chamfer metric induced by a norm).  To evaluate distances between two digital points for a
+  norms} which are chamfer metric induced by a norm.  To evaluate distances between two digital points for a
 given chamfer metric, direct formulations have been proposed with
@@
 ~\exists x\in P\quad A_kx=y_k.\footnote{$A_k$ being the $k^{th}$ row
-  of $A$.}$ $f$ being the number of rows in $A$ and the number of
+  of $A$.}$ $f$ is the number of rows in $A$ and the number of
 facets in $\B$, and is thus related to $|\M|$.
@@
 functions, a minimal parameter polytope representation exists and that
-distances can be obtained from similar expression to (\ref{eq:1}):
+distances can be obtained from a expression similar to (\ref{eq:1}):
 \begin{equation}
@@
 transformations for $L_2$ and $L_p$ metrics. Separability means that
-computations are performed dimension by dimension
+computations are performed dimension by dimension.
 %, allowing fast
@@
 %\cite{dcoeurjo_ChapDT} for an overview).
-In the following, we consider Voronoi map approach as defined in
-\cite{BreuEtAl95}: Let us first define hyper-rectangular image $I_X:
+In the following, we consider \emph{Voronoi Map} approach as defined in
+\cite{BreuEtAl95}: Let us first define an hyper-rectangular image $I_X:
      [1..N_1]\times\ldots\times[1..N_n] \rightarrow \{0,1\}$ such that
@@
   $S$ along the $i^{th}$ direction is a vector of $N_i$ points with
-  same coordinates except at $i$.}. In this process, metric information
+  same coordinates except at their $i^{th}$ one.}. In this process, metric information
 are embedded in the following  predicates (see
@@
 d(a,c)$. \textsc{HiddenBy}$(a, b, c, S)$, given three points
-$a,b,c\in\Z^n$ such that $a_i<b_i<c_i$ and a 1D image span
-$S$\footnote{Subscript $a_i$ denotes the $i^{th}$ coordinate of point
-  $a\in\Z^n$.}, this
+$a,b,c\in\Z^n$ such that $a_i<b_i<c_i$\footnote{Subscript $a_i$ denotes the $i^{th}$ coordinate of point
+  $a\in\Z^n$.} and a 1D image span
+$S$, this
 predicates returns true if there is no $s\in S$ such that
@@
   \caption{\small Geometrical predicates for Voronoi map construction:
-    \textsc{HiddenBy}($a,b,c,S)$ returns false in $(a)$ and true in
+    \textsc{HiddenBy}($a,b,c,S)$ returns true in $(a)$ and false in
     $(b)$ (straight segments correspond to Voronoi diagram
@@
 For $L_p$ norms Algorithm \ref{alg:voro} provides exact Voronoi map
-computation. Indeed, distance comparison predicate can be implemented
-error-free from integer number comparisons considering the $p$ power of
+computation. Indeed, distance comparison predicate can be error-free implemented
+ from integer number comparisons considering the $p$ power of
 the distance function $\left (d_{L_p}\right)^p$.
@@
 From \cite{BreuEtAl95,roerdnik}, $C=H=O(1)$ for $L_1,L_2$ and $L_\infty$
-norms.  For prescribed norm $d$, we first define generic
+norms.  For given norm $d$, we first define generic
 Algorithms~\ref{alg:genclosest}, \ref{alg:genedge} and
@@
   First, the generic \textsc{VoronoiEdge} is dichotomic with
-  $O(\log{N})$ steps and $O(C)$ for each one. \textsc{VoronoiEdge} is
+  $O(\log{N})$ steps and each step is in  $O(C)$. \textsc{VoronoiEdge} is
   in $O(C\cdot\log{N})$.  To prove the correctness of
@@
   are \emph{lower} than all pixels on $S$ closer to $b$ than to $a$
-  (if exist too). Thanks to test in line $4$, recursive call maintain
-  this invariant. Note that tests $2-5$ handle the fact that the edge
+  (if exist too). Thanks to the test in line $8$, recursive call maintain
+  this invariant. Note that tests on lines $2-5$ handle the fact that the edge
   may not belong to $S$.$\Box$
 \end{proof}
-If we consider a chamfer norm with $f$ facet rational ball, Eq.~(\ref{eq:1})
+If we consider a chamfer norm with a rational ball of $f$ facets, Eq.~(\ref{eq:1})
 suggests that $C=O(f)$. Hence, we have the following corollary:
@@
 of point $a$ can be obtained in two steps: First, we compute the wedge
-$(\vec{v}^k,\vec{v}^{k+1})$, $a$ belongs to. Then,
+$(\vec{v}^k,\vec{v}^{k+1})$ $a$ belongs to. Then,
 \begin{equation}
@@
 $e'_i>e_i$.
-Let us first suppose that we do not have $e$ but we know the two wedges
-$(\vec{v}^{k},\vec{v}^{k+1})$ (resp. $(\vec{v}^j,\vec{v}^{j+1})$) such
-that the vector $(e-a)^T$ (resp. $(e-b)^T$) belongs to (see
-Fig.~\ref{fig:algo}). In this situation, we know that $e$ is the
+Let us first suppose that we do not know $e$ but we know the  wedge
+$(\vec{v}^{k},\vec{v}^{k+1})$ (resp. $(\vec{v}^j,\vec{v}^{j+1})$) to which the vector $(e-a)^T$ (resp. $(e-b)^T$) belongs to (see
+Fig.~\ref{fig:algo}$-(c)$). In this situation, we know that $e$ is the
 solution of
@@
 the straight line $(a + \vec{v}^k)$ and $S$ is in the Voronoi cell of
-$a$ and such that the intersection between $(a + \vec{v}^k)$ and $S$
+$a$ and such that the intersection between $(a + \vec{v}^{k+1})$ and $S$
 is in the Voronoi cell of $b$ (see
 Fig.~\ref{fig:algo}$-(c)$). Algorithm~\ref{alg:chamedgew} thus first
-compute the intersection points associated with a wedge
+computes the intersection points associated with a wedge
 $(\vec{v}^{i+(j-i)/2}, \vec{v}^{i+(j-i)/2+1})$ (lines $5-6$);
-Evaluates the distances at these points (lines $7-8$) and then decides
+evaluates the distances at these points (lines $7-8$) and then decides
 which set $\{\vec{v}^i,\ldots,\vec{v}^{i+(j-i)/2}\}$ or
 $\{\vec{v}^{i+(j-i)/2},\ldots,\vec{v}^j\}$ has to be considered for
-the recursive call (lines $14-25$ and Fig.~\ref{fig:algo}$-(b)$).
+the recursive call (lines $14-20$ and Fig.~\ref{fig:algo}$-(b)$).
 
@@
   $(i)$ Algorithm     \ref{alg:chamedge} is in  $O(\log^2{m})$;
-  $(ii)$ Algorithm \ref{alg:voro} (with predicates from Algorithms
+  $(ii)$ Algorithm \ref{alg:voro} (with predicates from Algorithm
     \ref{alg:chamedge} and Lemma \ref{lem:log}), computes a Voronoi
@@
 automatically constructed. Please note that since all algorithms are
-separable, generic framework provided in \textsc{DGtal} allow us to
+separable, the generic framework provided in \textsc{DGtal} allow us to
 have a free multi-thread implementation \cite{dcoeurjo_ChapDTWADGMM}.
@@
     the first row corresponds to $\M_{5-7-11}$ and the second one to
-    $L_2$. $(b)$ Experimental evaluation of subquadratic chamfer norm
+    $L_2$. $(b)$ and zoom in $(c)$: Experimental evaluation of subquadratic chamfer norm
     Voronoi map computation.  \label{fig:2Dvoro}}
@@
 role in the computational analysis, we just use trivial ones that
-ensure that $\M$ is a norm with axis symmetric unit ball.
-In Fig.\ref{fig:2Dvoro}-$(b)$, we have considered a 2D domain $2048^2$
+ensure that $\M$ is a norm with axis symmetric unit ball.  In
+Fig.\ref{fig:2Dvoro}-$(b-c)$, we have considered a 2D domain $2048^2$
 with $2048$ random sites. First, we observe that fixing $N$, the
@@
 classical chamfer norm DT from raster scan (and sub-masks), the
-computational cost would have been in $O(m\cdot N^2)$ and thus would
-have a linear behavior in Fig.~\ref{fig:2Dvoro}-$(b)$. Since we have a
-separable algorithm, we can trivially implement it in a multi-thread
+computational cost is in $O(m\cdot N^2)$ and thus has a linear
+behavior in Fig.~\ref{fig:2Dvoro}-$(c)$. Since we have a separable
+algorithm, we can trivially implement it in a multi-thread
 environment. Hence, on a bi-processor and quad-core (hyper-threading)
 Intel(R) Xeon(R) cpu (16 threads can run in parallel), we observe a
-speed-up by a factor 10 (blue curve in Fig.~\ref{fig:2Dvoro}-$(b)$).  Please
-note that on this $2048^2$ domain with 2048 sites, Euclidean Voronoi
-Map ($L_2$) is obtained in 954.837 milliseconds on a single core and
-723.196 msec on 16 cores.
+speed-up by a factor 10 (blue curve in Fig.~\ref{fig:2Dvoro}-$(b)$).
+Please note that on this $2048^2$ domain with 2048 sites, Euclidean
+Voronoi Map ($L_2$) is obtained in 954.837 milliseconds on a single
+core and 723.196 msec on 16 cores.
 
@@
 norm with some properties) a first generic separable algorithm can be
-used. Focusing to chamfer norms, geometrical interpretation of this
+used. Focusing on chamfer norms, geometrical interpretation of this
 generic approach allows us to design a first subquadratic algorithm in

### 2014-05-14 latex/dgci2014/data/trace.py

@@ -15,6 +15,7 @@ mylog2 = np.log(myx)*np.log(myx)
 
 fig = plt.figure()
 axes = fig.add_subplot( 1, 1, 1 )
+#axes.set_yscale('log')
 
 datalist = pylab.loadtxt( "statVoronoi-mono.txt" )
 datalist2 = pylab.loadtxt( "statVoronoi-openmp.txt" )
@@ -26,13 +27,13 @@ plt.ylabel( 'Time in sec' )
 
 p1,=plt.plot( datalist[:,0],datalist[:,1]/1000, 'g',label="Voronoi Map (single thread)",alpha=1 )
 p2,=plt.plot( datalist2[:,0],datalist2[:,1]/1000, 'r',label="Voronoi Map (multi-thread)",alpha=1 )
-p2b,=plt.plot( datalist3[:,0],datalist3[:,1]/1000, 'b',label="Raster scan",alpha=1 )
+p2b,=plt.plot( datalist3[0:120,0],2.0*datalist3[0:120,1]/1000, 'b',label="Raster scan",alpha=1 )
 p3,=plt.plot( myx, 0.04*mylog2, '.r',label="$0.04\log^2{m}$",alpha=0.5 )
 p4,=plt.plot( myx, 0.4*mylog2, '.g',label="$0.4\log^2{m}$",alpha=0.5 )
 
 lines=[p1,p2,p2b,p3,p4]
 ##plt.legend( loc=2 )
-plt.legend(lines, [l.get_label() for l in lines], loc=7,frameon=False)
+plt.legend(lines, [l.get_label() for l in lines],loc=1,prop={'size':16},frameon=False)
 
 
 ##plt.show()
@@ -49,19 +50,20 @@ myylog2 = np.log(myxx)*np.log(myxx)
 
 fig2 = plt.figure()
 axes2 = fig2.add_subplot( 1, 1, 1 )
+#axes2.set_yscale('log')
 
 plt.xlabel( "Mask size $m$" )
 plt.ylabel( 'Time in sec' )
 
 p1,=plt.plot( datalistt[:,0],datalistt[:,1]/1000, 'g',label="Voronoi Map (single thread)",alpha=1 )
 p2,=plt.plot( datalistt2[:,0],datalistt2[:,1]/1000, 'r',label="Voronoi Map (multi-thread)",alpha=1 )
[…]

### 2014-09-05 latex/dgci2014/data/TMP/trace.py
tmp

@@ -1,0 +1,75 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import pylab
+import glob
+import os
+
+with plt.xkcd():
+
+    from matplotlib import rc
+    rc('font',**{'size': 18})
+    rc('text', usetex=True)
+    
+    current_path=os.getcwd()
+    
+    myx = np.linspace(0.01, 300000)
+    mylog2 = np.log(myx)*np.log(myx)
+    
+    fig = plt.figure()
+    axes = fig.add_subplot( 1, 1, 1 )
+    #axes.set_yscale('log')
+
+    datalist = pylab.loadtxt( "statVoronoi-mono.txt" )
+    datalist2 = pylab.loadtxt( "statVoronoi-openmp.txt" )
+    datalist3 = pylab.loadtxt( "result-raster.txt" )
+    
+    #plt.legend( loc=2 )
+    plt.xlabel( "Mask size $m$" )
+    plt.ylabel( 'Time in sec' )
+    
+    p1,=plt.plot( datalist[:,0],datalist[:,1]/1000, 'g',label="Voronoi Map (single thread)",alpha=1 )
+    p2,=plt.plot( datalist2[:,0],datalist2[:,1]/1000, 'r',label="Voronoi Map (multi-thread)",alpha=1 )
+    p2b,=plt.plot( datalist3[0:120,0],2.0*datalist3[0:120,1]/1000, 'b',label="Raster scan",alpha=1 )
+    p3,=plt.plot( myx, 0.04*mylog2, '.r',label="$0.04\log^2{m}$",alpha=0.5 )
+    p4,=plt.plot( myx, 0.4*mylog2, '.g',label="$0.4\log^2{m}$",alpha=0.5 )
+    
+    lines=[p1,p2,p2b,p3,p4]
+    ##plt.legend( loc=2 )
+    plt.legend(lines, [l.get_label() for l in lines],loc=1,prop={'size':16},frameon=False)
+
+
+    ##plt.show()
+    plt.savefig( 'result.pdf', format='PDF' )
+
+
+    datalistt = pylab.loadtxt( "statVoronoi-mono-short.txt" )
+    datalistt2 = pylab.loadtxt( "statVoronoi-openmp-short.txt" )
+    datalistt3 = pylab.loadtxt( "result-raster-short.txt" )
+    
+    
[…]

### 2014-09-05 latex/dgci2014/data/TMP/trace.py
tmp

@@ -6,9 +6,9 @@ import os
 
 with plt.xkcd():
 
-    from matplotlib import rc
-    rc('font',**{'size': 18})
-    rc('text', usetex=True)
+    #from matplotlib import rc
+    #rc('font',**{'size': 18})
+    #rc('text', usetex=True)
     
     current_path=os.getcwd()
     

### 2014-09-05 src/statVoronoi-raster.cpp
code fix

@@ -87,6 +87,7 @@ void rasterScan(const  Domain &aDomain,
   }
 }
 
+using namespace experimental;
 
 int main(int argc, char **argv)
 {

### 2014-09-05 src/statVoronoi.cpp

@@ -41,6 +41,7 @@ void constructPredicate(Predicate &mySet, const unsigned int nbSeeds, const unsi
     mySet.erase (*it);
 }
 
+using namespace experimental;
 
 int main(int argc, char **argv)
 {

### 2014-09-05 src/statVoronoi-raster.cpp
ok

@@ -90,7 +90,7 @@ void rasterScan(const  Domain &aDomain,
 
 int main(int argc, char **argv)
 {
-  unsigned int maxN = 50;
+  unsigned int maxN = 500;
   unsigned int domSize = 2048;
   unsigned int nbSeeds = domSize;
   

### 2014-09-05 src/statVoronoiMP.cpp
mp

@@ -55,9 +55,8 @@ int main(int argc, char **argv)
   DigitalSetBySTLSet<Z2i::Domain> mySet(domain);
   constructPredicate<DigitalSetBySTLSet<Z2i::Domain> >(mySet,nbSeeds, domSize);
   
+  unsigned int N = maxN;
   
-  for(unsigned int N = 2 ; N < maxN; )
-  {
     ChamferNorm2D<Z2i::Space> mask(N);
     trace.info() << mask<<std::endl;
     Z2i::Point origin(0,0);
@@ -101,7 +100,7 @@ int main(int argc, char **argv)
     
 #endif
     
-  }
+  
   
   return 0;
 }

### 2014-09-05 latex/dgci2014/data/TMP/trace.py
scaleup

@@ -67,9 +67,22 @@ with plt.xkcd():
     ##plt.legend( loc=2 )
     plt.legend(liness, [l.get_label() for l in lines], loc=2,prop={'size':16},frameon=False)
 
+    plt.savefig( 'result-zoom.pdf', format='PDF' )
+
+
+    scaleup = pylab.loadtxt( "scaleup.txt" )
+    
+    fig3 = plt.figure()
+    axes3 = fig3.add_subplot( 1, 1, 1 )
+    plt.xlabel( "Number of threads" )
+    plt.ylabel( 'Speedup' )
+
+   
+    p1,=plt.plot( scaleup[:,0],35633/scaleup[:,1], 'g',label="Separable Voronoi Map",alpha=1 )
+
 
 ##plt.show()
-plt.savefig( 'result-zoom.pdf', format='PDF' )
+plt.savefig( 'result-mp.pdf', format='PDF' )
 
 
 

### 2014-09-05 latex/dgci2014/data/TMP/trace.py
ok

@@ -78,7 +78,10 @@ with plt.xkcd():
     plt.ylabel( 'Speedup' )
 
    
-    p1,=plt.plot( scaleup[:,0],35633/scaleup[:,1], 'g',label="Separable Voronoi Map",alpha=1 )
+    pmp,=plt.plot( scaleup[:,0],35633/scaleup[:,1], '-+g',label="Separable Voronoi Map",alpha=1 )
+    liness2=[pmp]#,p3,p4]
+    ##plt.legend( loc=2 )
+    plt.legend(liness2, [l.get_label() for l in lines], loc=2,prop={'size':16},frameon=False)
 
 
 ##plt.show()

### 2014-09-05 latex/dgci2014/data/TMP/trace.py
ok

@@ -78,7 +78,7 @@ with plt.xkcd():
     plt.ylabel( 'Speedup' )
 
    
-    p1,=plt.plot( scaleup[:,0],35633/scaleup[:,1], 'g',label="Separable Voronoi Map",alpha=1 )
+    p1,=plt.plot( scaleup[:,0],35633/scaleup[:,1],'-g',label="Separable Voronoi Map",alpha=1 )
 
 
 ##plt.show()
